### 2015-10-28 contents/title.tex
Initial ShareLaTeX Import

\title{Human Body Outline Annotation}

\author{Author\\
Imperial College London\\
180 Queen’s Gate, SW7 2AZ, London, U.K.\\
{\tt\small \{email\}@imperial.ac.uk}}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both

### 2015-10-28 contents/abstract.tex
initial changes, by modifying ICCV submission

% Uses Abstract from Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder with some modification.
% Deformable objects are everywhere. Faces, ears, bodies,
% bottles etc. Recently, there has been a wealth of research
% on training deformable models for object detection,
% part localization and recognition using annotated data. In
% order to train deformable models with good generalization
% ability, a large amount of carefully annotated data is required,
% which is a highly time consuming and costly task.

% We propose the first - to the best of our knowledge - method
% for construction of dense deformable models using images
% captured in totally unconstrained conditions, recently
% referred to as “in-the-wild”. The only requirements of the
% method are drawings of image features. The object detector can be as simple as the
% Viola-Jones algorithm (e.g. even the cheapest digital camera
% features a robust face detector). The 2D shape model
% can be created by using only a few shape examples with deformations.
% In our experiments on facial deformable models,
% we show that the proposed automatically built model
% not only performs well, but also outperforms discriminative
% models trained on carefully annotated data. To the best of
% our knowledge, this is the first time it is shown that an automatically
% constructed model can perform as well as methods
% trained directly on annotated data.

% Building and training deformable models of objects (e.g. faces, ears, bottles and cars) has  recently been widely researched for object detection, part localisation, fitting, recognition and tracking using manual annotated data. To train deformable models with satisfiable generalisation, large amount of carefully manual annotation is required. However, landmark annotation is extremely time consuming, work intensive and, most importantly, number of landmarks have to stay consistent for all training data while it is challenging to maintain the consistency or to avoid bias when annotating objects that having reach features like ears. We propose framework to handle training data with inconsistent annotation, build dense shape model and introduce effective curve annotation methods. In our experiment, we show building dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data.

%The past few years we have witnessed the development of many techniques for constructing and fitting statistical models of deformable objects. The construction of Statistical Deformable Models (SDMs) typically requires careful annotation of images with regards to a set of landmarks describing the object's shape. Annotation of images with landmarks is a tedious, expensive and labor intensive procedure. Furthermore, for some deformable objects it is difficult to find a consistent set of landmarks find and annotate with regards to. Nevertheless, for the majority of objects it is possible to extract the shape by object segmentation or even by shape drawing. In this paper, we show for the first time, to the best of our knowledge, that it is possible to construct SDMs by putting object shapes in dense correspondence. Such SDMs can be build with much less efforts and can generalize so as to describe a larger battery of objects.

The past few years we have witnessed the development of many methodologies for constructing and fitting statistical deformable models. The construction of Statistical Deformable Models (SDMs) usually requires careful annotation of images with regards to a set of landmarks. Annotation of images with landmarks is a tedious, laborious, expensive and labor intensive procedure. Furthermore, for some deformable objects it is not possible to find and annotate with regards to a consistent set of landmarks. Nevertheless, for the majority of objects, it is possible to extract the shape by object segmentation or even by shape drawing. In this paper, we show for the first time, to the best of our knowledge, that it is possible to construct SDMs by putting object shapes in dense correspondence. Such SDMs can be build with much less efforts and can generalize so as to describe a larger battery of objects.

### 2015-10-28 contents/implementation.tex
initial changes, by modifying ICCV submission

\begin{figure*}[t!]
    \centering
        \includegraphics[width=\textwidth]{resources/architecture3}
    \caption{Schematic description of the proposed pipeline. Figure best viewed by zooming in.}
    \label{fig:archi}
\end{figure*}

\section{Constructing Deformable Models with Shape Flow}

% Deformable models are widely used for object detection, localization, recognition and tracking while training a deformable model with good generalisation requires tremendous amount of carefully annotated data, which is extremely time consuming. Even more, annotated data of a specific object category typically requires same numbers of landmarks for every training sample, making the annotation procedure significantly complex where corrext menual annotation of landmarks is impossible in various object classes e.g. ears.

% Despite the fact that that vast majority of existing methods are based on a sparse shape representation, dense shape representation reveals more nuanced structure in terms of [todo: explain].

We propose a novel framework for building deformable models that does not require any consistent set of annotated landmarks and is based on a dense shape representation. Our method only requires a set of point or curve line annotations that does not need to be consistent over different training samples. It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.

The proposed pipeline is depicted in Figure~\ref{fig:archi}. It takes as input a set of training images of a particular object class, along with inconsistent point and/or curve line annotations.
As a first step, all the shape annotations are consistently represented using multichannel SVS.
The next step is the application of Iterative Closest Point (ICP) algorithm \cite{Besl1992} to achieve an initial simple alignment of the SVS images.
The multichannel similarity-aligned SVS images are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all the shapes in the training set. In order for the flow estimation to be accurate and exploit the correlation among all training shapes, it utilises a correspondence basis built from sparse correspondences obtained by applying Nonrigid ICP on the annotated data. Finally, the dense correspondences yield by optical flow serve as automatically generated dense landmark annotations and are used to define a novel dense version of Active Appearance Models. The upcoming sections discuss each of the previous stages in further detail.

%two major modules. The first module handles inconsistent annotation set by converting to landmark independent shape discriminator. While the other module produces shape flow on object discriminators to generate dense flow transformations in shape space following by robust PCA\cite{?} to generate deformable model. In this section, we present the entire architectures, design decision and algorithms.
\subsection{Shape Representation Without Consistent Annotations}
\label{sec:svs}
%Ordinarily, construction of deformable model requires training data set having consistent number of landmarks. But unavoidable changes has to be made before applying same algorithm on diverse annotated data set.

In order to fully capture the variability among most deformable object shapes annotations, we use a representation based on Support Vector Shapes (SVS) \cite{Nguyen2013}. A SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with Radial Basis Function (RBF) kernels. In this way, a shape is represented as a classifier function, which has several advantages: (a) the representation is completely general, \eg it can be applied to sparse landmark points, curves lines or a combination of the two and (b) it fuses inconsistent landmarks into consistent and directly comparable decision functions. Furthermore, this representations is also robust against noise, missing data and outliers \cite{Nguyen2013}.

In practice, we assume that all the training images correspond to the same object category and contain a set of inconsistent points and curve line annotations. All annotations are densely sampled to yield a set of annotated landmarks per image, with this set being different for every training image. Initially, negative points get randomly sampled around sparse landmarks while annotated landmarks are positive points. Since the number of positive points is far smaller that the number of negative ones, landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are the number of positive/negative samples and $W_p, W_n$ are their corresponding weights.

SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object. Note that the decision function for SVMs can be mathematically expressed as:
\begin{equation} \label{eq:decisionfunc}
    d(\bm{x})=\sum_i\alpha_i \, k(\bm{x}_i^*,\bm{x})
\end{equation}
where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel .

Figure \ref{fig:build_svs} shows an exemplar shape representation using SVS. As it can be observed, the final result does not drastically depend on the original number of annotated landmarks.

% \begin{figure}[b!]
%     \centering
%     \begin{subfigure}[b]{0.2\textwidth}
%             \includegraphics[width=\textwidth]{resources/landmark}
%         \caption{Spare landmarks}
%     \end{subfigure}
%     \qquad
%     \begin{subfigure}[b]{0.2\textwidth}
%             \includegraphics[width=\textwidth]{resources/svs}
%         \caption{Decision function}
%         \label{fig:svs}
%     \end{subfigure}
%     \caption{Exemplar SVS shape representation. The decision function is trained on the set of sparse landmarks. In (b), brighter colour represents higher probability of a pixels belonging to the original shape.}
%     \label{fig:build_svs}
% \end{figure}

\begin{figure}[b!]
    \centering
    \includegraphics[width=0.4\textwidth]{resources/svs2}
    \caption{Exemplar SVS shape representation. A similar SVS image is obtained from different annotations of the same shape.}
    \label{fig:build_svs}
\end{figure}

After constructing the SVS representation for all images, the next step is to apply a simple similarity alignment over them. This is done because the goal here is to build a model capable of effectively representing non-rigid local shape deformations rather than global rotation, translation and scaling. The alignment is performed by using the Iterative Closest Point (ICP) algorithm \cite{Besl1992} on the annotated landmarks point cloud of the training images.

\subsection{Shape Correspondence Basis}

We consider the problem of dense correspondences across SVS images as a joint estimation of optical flow fields between a reference SVS image and every SVS image of the training dataset. The estimation of such a ``shape flow'' defines for every training SVS image a warping function that registers it with the reference SVS image. To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu}.

Instead of the \emph{motion} basis used in multiframe optical flow formulation of \cite{Garg:2013hu}, we build a \emph{correspondence} basis that introduces constraints on how points of different shapes are matched to each other. Every pixel of the reference SVS image is matched to its corresponding position at every training SVS image and in this way defines a \emph{correspondence vector}. This vector consists of the 2D locations of the specific point in all SVS images. To form this vector, the training images are arranged in an arbitrary order. Similarly to the order of training samples when Principal Component Analysis (PCA) is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.

Formally, let $F$ be the number of training SVS images and $n=1,\ldots,F$ be the training image index. Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
\{1,\ldots,F\} \rightarrow \R^2$ be the $R$ orthonormal elements of the correspondence basis, where $\boldsymbol{q}_i(n)$ is the displacement vector that matches the points of the reference SVS image with the points of the $n$-th training SVS image, according to the variation described from the $i$-th correspondence basis element. Note that the basis elements $\boldsymbol{q}_i(n)$ are independent from the point location. Note also that the number of basis elements is typically much smaller than the full dimensionality ($2 F$) of correspondence vectors, therefore this basis plays a role of dimensionality reduction.

In addition, let $\Omega \subset \R^2$ be the image domain of the SVS images and $\bx$ denote the point location. We denote the shape flow result as $\bm{u}_n(\bx):\Omega\times \{1,\ldots,F\}
\rightarrow \R^2$,  where $\bm{u}_n(\bx)$ is the displacement vector that matches the point $\bx$ of the reference SVS image with its corresponding location at the $n$-th training SVS image.

Using the constructed correspondence basis, the shape flow can be approximated as:
\begin{equation}\label{eq:LinTrajModel}
    \bm{u}_n(\bx) \approx
    \sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
\end{equation}
where $\bm{v}_i(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$. In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v}_i(\bm{x})$.
The values of the $i$-th coefficient for all the points $\bm{v}_i(\bm{x})$ can be interpreted as an image defined on $\Omega$. Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v}_i(\bm{x})$. The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.

The next section describes the methodology of constructing the correspondence basis and estimating the shape flow robustly.

% For all dense transformations $\bm{u}_n(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
% \begin{equation}
%     \begin{bmatrix}
%         \bm{u_1}(\bm{x}) \\
%         \vdots \\
%         \bm{u_F}(\bm{x})
%     \end{bmatrix}
%     =
%     \begin{bmatrix}
%         \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
%         \vdots      & \ddots & \vdots  \\
%         \bm{q_1}(F) & \cdots & \bm{q_R}(F)
%     \end{bmatrix}
%     \times
%     \begin{bmatrix}
%         \bm{v_1}(x) \\
%         \vdots \\
%         \bm{v_R}(x)
%     \end{bmatrix}
% \end{equation}
% where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
% \begin{equation}
%     \bm{u}_n(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)+\bm{\varepsilon_n}(\bm{x})
% \end{equation}

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/5}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/6}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/7}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.1\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Flows/8}
    \end{subfigure}
    \caption{Exemplar deformation fields obtained using the proposed pipeline. Figure best viewed by zooming in.}
    \label{fig:deformationfield}
\end{figure}

% ---------------------------------------------------------------------------------------------------------------------------------------------------

\subsection{Shape Flow}
\label{sec:shapeflow}

Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions. We propose to perform this estimation simultaneously for all training data, by using the correspondence basis. This procedure, which we call \emph{shape flow}, builds upon robust methods for multiframe optical flow estimation \cite{Garg:2013hu}. However, optical flow estimation typically works based on the assumptions of brightness or colour constancy and motion smoothness, whereas in our setting the input training data correspond to shapes. For this reason, we propose to modify the formulation of \cite{Garg:2013hu} by using the correspondence basis that we introduced in conjunction with the SVS representation of shapes.

%
%In order to learn the such a subspace, we first transform the original annotation to point clouds. Then, we use NICP to align the previous point clouds with respect to a reference point cloud template. NICP iteratively deforms each point cloud until its points match the ones on the shape template and correspondences are established. However, because optical flow is a pixel-wise frame registration technique, we need to establish correspondences for all pixels on the reference frame rather than for sparse point clouds. To achieve this, we apply Thin Plate Spline (TPS) \cite{Bookstein1989} to find correspondences for all pixels in the reference frame given the point cloud correspondences provided by the previous NICP stage. Once dense correspondences have been established among all pixels, the so-called correspondence subspace is obtained by performing PCA the trajectory of all pixels. Note that incorporating the previous subspace as a low rank constrained in optical flow is consistent with its assumption of smooth motion.

\subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}

To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds. Then, we apply Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set. NICP iteratively deforms the cloud of points of every shape to match the points of the reference shape. This yields an initial estimation of the correspondence vectors on the sparse locations of annotated landmarks on the reference shape. To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference SVS image), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation. Finally, the correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.

%
%
%Since optical flow pixel-wise frame registration, the trajectory basis build should also match the dimension, which is dense on shapes with trajectory length depends on number of training data. With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{Bookstein1989} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering. For all dense transformations $\bm{u}_n(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
%\begin{equation}
%    \begin{bmatrix}
%        \bm{u_1}(\bm{x}) \\
%        \vdots \\
%        \bm{u_F}(\bm{x})
%    \end{bmatrix}
%    =
%    \begin{bmatrix}
%        \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
%        \vdots      & \ddots & \vdots  \\
%        \bm{q_1}(F) & \cdots & \bm{q_R}(F)
%    \end{bmatrix}
%    \times
%    \begin{bmatrix}
%        \bm{v_1}(x) \\
%        \vdots \\
%        \bm{v_R}(x)
%    \end{bmatrix}
%\end{equation}
%where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
%\begin{equation}
%    \bm{u}_n(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bm{x})+\bm{\varepsilon_n}(\bm{x})
%\end{equation}
%Although optical flow on shapes made under the assumption that objects motion are smooth, the low rank constrain on trajectory basis recovered the hypothesis.

\subsubsection{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
\label{varshapeflow}

Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d}_n(\bx)$ by minimizing the following energy:
\begin{align}
E_{sf} & =\alpha
\int_{\Omega}\sum_{n=1}^F \|\bm{d}_n(\bx+\bm{u}_n(x))-\bm{d}_0(x)\| \ud \bx \label{eq:costfunc}\\
    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
    &+
\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
\end{align}
This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v}_i(\bx)$ that are spatially regularised and enforce a low-rank prior. We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$. The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.

The \textbf{first term} of the above energy \eqref{eq:costfunc} is a data attachment term
that uses the robust $\Lone$-norm.  It is based on the assumption that the values of the reference SVS image $\bm{d}_0(\bx)$ at every pixel $\bx$ are preserved at its corresponding locations on all training SVS images $\bm{d}_n(\bx)$. The use of an $\Lone$-norm improves the robustness of the method since it allows deviations from this assumption, which might occur in practice.
The \textbf{second term} of the energy \eqref{eq:lowrank} penalizes the difference between the two sets  of shape flows and acts as a coupling term between them.
The \textbf{third term} of the energy \eqref{eq:TVterm} corresponds to the spatial Total Variation regularization \cite{rudin92} of
the correspondence basis coefficients $\bm{v}_i(\bx)$.
This term penalizes spatial oscillations of each coefficient caused by distortions of the SVS images but not strong discontinuities that are desirable in the borders of different object regions. In addition, this term allows to fill in information into regions where the shape information in the SVS images is missing, due to e.g.~regions with no annotations.

We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}. In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with the shape flow result of the TPS interpolation described in Sec.~\ref{sec:trabasis}. We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization. After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$. The minimization w.r.t.~
$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}. The minimization w.r.t.~
$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.

Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method. These results correspond to exemplar training shapes in the case of a face dataset.

%
%
%To register all decision functions to temp`late shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm. The objective cost function we would like to minimise is:
%\begin{align}
%    \operatorname*{arg\,min}_{\bm{u}_n(\bm{x}), \bm{v}}&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u}_n(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
%    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
%    &+ \sum[\bm{TV}(Qv)]
%\end{align}
%where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$. $TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
%
%Term~\eqref{eq:costfunc} state the shape constancy where points having similar classification probability are from same object.
%Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
%The objective cost function has two free parameters $u$ and $v$, so we perform alternating minimisation. The equation can be solved using a thresholding scheme after linearisation of image functions. The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in \{1,...F\}$ independently.
%
%
%
%
%
%
%After solving the equation, $\bm{u}_n(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g. $\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame. Figure~\ref{fig:deformationfield} demonstrates deformation fields that warps from reference frame where there is no deformation.

% \begin{figure}[h!]
%     \centering
%         \includegraphics[width=0.5\textwidth]{resources/df}
%     \caption{Deformation field built}
%     \label{fig:deformationfield}
% \end{figure}

% Applying PCA on deformations trains dense deformable shape model:
% \begin{equation*}
%     \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
% \end{equation*}
% where $\bm{s_p}$ is deformed shape instance. $\bm{\bar{s}}$ is mean shape and $\bm{U}_s\bm{p}$ are eigenvectors with corresponding parameters $p$. Figure~\ref{fig:models} shows an instance of deformed shape and appearance model.
% \begin{figure}[h!]
%     \centering
%     \begin{subfigure}[b]{0.22\textwidth}
%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_shape}
%     \end{subfigure}
%   	\hfill
%     \begin{subfigure}[b]{0.22\textwidth}
%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_app}
%     \end{subfigure}
%     \caption{Dense Deformable Model}
%     \label{fig:models}
% \end{figure}

% \begin{figure}[h!]
%     \centering
%     \begin{subfigure}[b]{0.22\textwidth}
%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_shape}
%     \end{subfigure}
%   	\hfill
%     \begin{subfigure}[b]{0.22\textwidth}
%             \includegraphics[width=\textwidth]{resources/Fig_dAAM/of_app}
%     \end{subfigure}
%     \caption{Dense Deformable Model}
%     \label{fig:models}
% \end{figure}

\subsection{Dense Active Appearance Models}

The deformation fields obtained from section \ref{sec:shapeflow} can be effectively used to learn a naturally dense version of Active Appearance Models \cite{Cootes2001, Matthews2004}. Because all deformation fields contain the same number of pixels (the same as on the reference frame) the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation field themselves as dense annotations of the object's shape. Consequently, building a dense shape model reduces to normalizing these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying Principal Component Analysis (PCA). The resulting shape model can be mathematically expressed as:
\begin{equation}
    \begin{aligned}
        \bm{s} & = \bm{\bar{s}} + \bm{S} \bm{p}
    \end{aligned}
    \label{eq:shape_model}
\end{equation}
where $\bm{\bar{s}}$ is mean shape and $\bm{S}$ and $\bm{p}$ are the shape bases and shape parameters respectively.

On the other hand, the texture model associated to the previous set of densified shapes can be easily obtained by warping all image onto the reference frame, making explicit use of the one-to-one correspondence between pixels on the reference frame and on the deformation fields. Once the images have been warped, the texture model is obtained by applying PCA on the warped images. The texture model is mathematically defined by the following expression:
\begin{equation}
    \begin{aligned}
        \bm{t} = \bm{\bar{t}} + \bm{T} \bm{c}
    \end{aligned}
	\label{eq:tex_model}
\end{equation}
where $\bm{t}$ is the mean texture, and $\bm{T}$ and $\bm{c}$ are the texture bases and texture parameters respectively.

Note that, both shape and texture models are directly related through the existent one-to-one correspondence between dense landmarks and pixels on the reference
frame. Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, in our dense formulation no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models . As noted by other authors \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.

%\subsubsection{Drawing Annotation}
%The purpose of the shape descriptor $\bm{d_i}(x)$ generates probabilities for arbitrary points. If we sample points that are exactly pixel-wise integers, and normalise classification value, we can visualise a SVS as an image for example in figure~\ref{fig:svs}. In other words, our architecture will also works for images with landmarks similar to SVS visualisations like drawing. Assuming the intensity of a gray-scale image simulate the decision function, named $\bm{I_i}(x), x \in \Omega, i \in \{1,...F\}$. But in this situation, pixels at image space are discontinued, so $x$ is constrained to be integer and within the view window of size $N\times M$.

\subsection{Outline-based Deformable Modeling}

The

\subsection{Part-based AAMs}

### 2015-10-28 contents/introduction.tex
initial changes, by modifying ICCV submission

% Building and training deformable models of objects (e.g. faces, ears, bodies, bottles, vehicles etc.) has recently been widely researched for object detection, part localisation, fitting, recognition and tracking using manual annotated data. Shapes and appearances of majority of objects vary significantly from object instance. To illustrate, ears have complicated inner structures (e.g. helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears and highly sensitive to intensity changes. Recently, we have witnessed a great progress in object detection, alignment and recognition.

% To train deformable models with satisfiable generalisation, large amount of careful manual annotation is required. However, landmark annotation is extremely time consuming, work intensive and, most importantly, number of landmarks have to stay consistent for all training data while it is challenging to maintain the consistency or to avoid bias when annotating objects that having reach features. In ears, for example, large amount of landmarks required as the inner structure of ears are complex. To annotate an ear with clear contour, helix and cavum conchae, more than 50 landmarks are required. The inconsistency of ear features enhanced the difficulty of accurate annotation (e.g. Fossa Triangularies and Crus Helicis are optional feature of an ear also their visibility is highly sensitive to pose and illumination variation).
% To illustrate how much time consuming careful ear annotation is, according to our experience, a trained annotator may need an average of (TODO: experiment) minutes per image for the manual annotation of 55 landmarks. This means that the annotation of 1000 images requires a total of about (TODO: experiment). Furthermore, personal issue, prior knowledge and circumstances can heavily bias the annotation accuracy thus second round correction might desired.

% We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs with shape flow.

% %(1)
% Annotated data of same objects can have various number of landmarks, \cite{?} shown faces have landmarks different in range 10+ to 70+. Building SDMs (e.g. Active Appearance Models), however, require training data are annotated consistently, for example, all faces have 68 landmarks, 6 landmarks for an eye and 9 for a nose \cite{?}. Such property of SDMs largely limited their application area like combining different dataset as one. We propose the pipeline with non-rigid alignment and support vector shape to blend landmarks into relatively consistent shape discriminator before building models.

% %(2)
% Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised and semi supervised learning of models for the tasks of alignment, landmark localization, tracking and recognition has attracted considerable attention \cite{?}. As our proposed framework are available to handle landmarks with inconsistency, it leads to a more efficient, convenient, unbiased and simple annotation methods - curve annotation.

% %(3)
% To build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow. Optical flow is originally applied to video sequences that several assumptions holds, illumination consistency and motion smoothness, while shapes having no motion smoothness completely as all training data are independent. Low rank constrain plays important role to simulate motion smoothness assumption.

% % Back Ground, uses Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
% The two most closely related works to the proposed
% method are the automatic construction of Active Appearance
% Models (AAMs) in \cite{?} and the so-called RASL
% methodology in \cite{?} for person-specific face alignment.
% There are two main differences between our framework
% and \cite{?}. (1) We use a predefined statistical shape model
% instead of trying to find both the shape and appearance models.
% We believe that with the current available optimization
% techniques, it is extremely difficult to simultaneously optimize
% for both the texture and shape parameters. (2) We
% employ the robust component analysis of \cite{?} for the appearance
% which deals with outliers. Thus, even though
% our method is similar in concept to \cite{?}, these two differences
% make the problem feasible to solve. In particular, the
% methodology in \cite{?} fails to create a generic model even in
% controlled recording conditions, due to extremely high dimensionality
% of the parameters to be found and to the sensitivity
% of the subspace method to outliers. This was probably
% one of the reasons why the authors demonstrate very
% limited and only person-specific experiments. Furthermore,
% our methodology bypasses some of the limitations of \cite{?},
% which requires the presence of only one low-rank subspace,
% hence it has been shown to work only for the case of congealing
% images of a single person. Finally, we argue that
% in order for an automatically constructed AAM methodology
% to be robust to both within-class and out-of-class outliers4,
% which cannot be avoided in totally unsupervised setting
% statistical component analysis techniques should be
% employed \cite{?}.

% We summarize our contributions as follows:
% \begin{itemize}
%   \item Constructing SDMs using training data with inconsistent annotation.
%   \item Introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
%   \item Building dense correspondent SDMs with shape flow
% \end{itemize}

% In our experiment, we show that building robust dense models trained with inconsistent annotation and trained with curve annotation improves performance of discriminative models trained on carefully annotated data including ears, faces, bottles, (cars ?) and bodies. Evaluation methods and choices are described in details.

% \clearpage
\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.145\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.145\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.145\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.07\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.07\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.07\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_5}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.06\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_5}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_0}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_1}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_2}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_3}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_4}
    \end{subfigure}
   	\hfill
    \begin{subfigure}[b]{0.075\textwidth}
            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_5}
    \end{subfigure}
    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
    \label{fig:intro}
\end{figure}

Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}. Recently, we have witnessed tremendous developments in building and fitting models of human faces and bodies using images captured in unconstrained recording environments, usually referred to as "in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}. This is attributed to:
\begin{itemize}

\item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images. The latter has led to the development of large databases of "in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}. Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013}.

\item The development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) \cite{lowe1999object}, Histogram of Oriented Gradients (HoGs) \cite{Dalal2005} and recently Deep Convolutional Neural Networks \cite{sermanet2013overfeat}), as well as generative and discriminative methodologies for learning deformable models.

\end{itemize}

There are two drawbacks on building deformable models that rely on landmarks:
\begin{itemize}

\item Annotating with regards to consistent landmark annotation is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person. Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks. For example human ears have very complicated inner structures (e.g. helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears. Moreover, certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.

\item The nature of many deformable objects does not allow them to be consistently annotated with regards to a consistent set of landmarks (e.g. bottles, fruits etc.). Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently, Figure \ref{fig:intro}. That is why many state-of-the-art methods opt to leave the boundary out for comparison \cite{Tzimiropoulos2014, Asthana2014}. The majority of the state-of-the-art methods for model-based landmark localisation \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable for objects with inconsistent sets of landmarks.

\end{itemize}

To illustrate how time consuming careful annotation of the human ear is we lay down our own experience. A trained annotator needs an average of 4 minutes per image for the manual annotation of 55 landmarks. This means that the annotation of 1000 images requires a total of about 67 hours. Furthermore,  training and fatigue largely influence the annotation accuracy. Hence, a second pass on the annotated data is, in many cases, necessary. Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}. However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected "in-the-wild". On the other hand, the method of \cite{antonakos2014automatic}, which can deal with "in-the-wild" images, requires a set of consistently annotated sparse shapes to perform deformable face congealing.

In this paper, we provide a solution for annotating an object with regards to its deformations that requires considerable less effort and in the same time can be used to define statistical deformations for objects without consistent set of landmarks. That is, we argue that it is better to annotate an object with regards to a set of continuous lines that describe the shape of the object. An example is provided in Figure \ref{fig:intro} where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks. Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes 42, 38 and 43 secs per image for faces, ears and bottles correspondingly. Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.

Furthermore, we show that flow methods have mature enough so that it can be used to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods \cite{Garg:2013hu,Nguyen2013}.  In particular, to build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow. Optical flow is originally applied to video sequences that several assumptions holds, illumination consistency and motion smoothness, while shapes having no motion smoothness completely as all training data are independent. Low rank constrain plays important role to simulate motion smoothness assumption.

We show that this way dense correspondences between images can be established and dense Active Appearance Models (AAMs) can be build on top of that. We show that the proposed methodology even though not tailored to landmark localization can be applied for landmark localization achieving very good performance. Finally, we demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks. To the best of our knowledge this is the first methodology which can create a dense statistical model for AAM which can operate in "in-the-wild".

%[..]. There are methods such as [..] and [..] but ...

Summarizing, the contributions proposed in this paper are:
\begin{itemize}
  \item Constructing SDMs using training data with inconsistent annotation.
  \item Introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
  \item Building dense correspondent SDMs with shape flow
\end{itemize}

%In our experiment, we show that building robust dense models trained with inconsistent annotation and %trained with curve annotation improves performance of discriminative models trained on carefully %annotated data including ears, faces, bottles, (cars ?) and bodies. Evaluation methods and choices are %described in details.

%We propose a framework to (1) construct SDMs using training data with inconsistent annotation, (2) %introduce highly effective curve annotation which tremendously reduces manual work overload but %maintains same performance level against state-of-the-art SDMs and (3) build dense correspondent SDMs %with shape flow.

%(1)
%Annotated data of same objects can have various number of landmarks, \cite{?} shown faces have %landmarks different in range 10+ to 70+. Building SDMs (e.g. Active Appearance Models), however, %%require training data are annotated consistently, for example, all faces have 68 landmarks, 6 landmarks %for an eye and 9 for a nose \cite{?}. Such property of SDMs largely limited their application area like %combining different dataset as one. We propose the pipeline with non-rigid alignment and support vector %shape to blend landmarks into relatively consistent shape discriminator before building models.

%(2)

%(3)

% Back Ground, uses Nondas' paper "Automatic Construction of Deformable Models In-The-Wild" as place holder
%The two most closely related works to the proposed
%method are the automatic construction of Active Appearance
%Models (AAMs) in \cite{?} and the so-called RASL
%methodology in \cite{?} for person-specific face alignment.
%There are two main differences between our framework
%and \cite{?}. (1) We use a predefined statistical shape model
%instead of trying to find both the shape and appearance models.
%We believe that with the current available optimization
%techniques, it is extremely difficult to simultaneously optimize
%for both the texture and shape parameters. (2) We
%employ the robust component analysis of \cite{?} for the appearance
%which deals with outliers. Thus, even though
%our method is similar in concept to \cite{?}, these two differences
%make the problem feasible to solve. In particular, the
%methodology in \cite{?} fails to create a generic model even in
%controlled recording conditions, due to extremely high dimensionality
%of the parameters to be found and to the sensitivity
%of the subspace method to outliers. This was probably
%one of the reasons why the authors demonstrate very
%limited and only person-specific experiments. Furthermore,
%our methodology bypasses some of the limitations of \cite{?},
%which requires the presence of only one low-rank subspace,
%hence it has been shown to work only for the case of congealing
%images of a single person. Finally, we argue that
%in order for an automatically constructed AAM methodology
%to be robust to both within-class and out-of-class outliers4,
%which cannot be avoided in totally unsupervised setting
%statistical component analysis techniques should be
%employed \cite{?}.

### 2015-10-30 contents/implementation.tex
updated text,deformation fig, added paragraphs for additional steps for the system

@@
         \centering
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/0}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/1}
-    \end{subfigure}
-   	\hfill
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/2}
-    \end{subfigure}
+        \begin{tabular}{ccc}
+        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/1}
+        &
+        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/2}
+        &
+        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/3}
         \\
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/4}
-    \end{subfigure}
-   	\hfill
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/5}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/6}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/7}
-    \end{subfigure}
-   	\hfill
-    \begin{subfigure}[b]{0.1\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Flows/8}
-    \end{subfigure}
-    \caption{Exemplar deformation fields obtained using the proposed pipeline. Figure best viewed by zooming in.}
+        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/4}
+        &
+        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/5}
+        &
+        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/6}
+        \end{tabular}
+    \caption{Exemplar deformation fields for the left forearm, obtained using the proposed pipeline. Figure best viewed by zooming in.}
     \label{fig:deformationfield}
@@
 
-Note that, both shape and texture models are directly related through the existent one-to-one correspondence between dense landmarks and pixels on the reference
-frame.
+Note that, both shape and texture models are directly related through the established one-to-one correspondence between dense landmarks and pixels on the reference frame.
 Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, in our dense formulation no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models .
-As noted by other authors \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.
+As noted in other works \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.
 
-%\subsubsection{Drawing Annotation}
-%The purpose of the shape descriptor $\bm{d_i}(x)$ generates probabilities for arbitrary points.
-If we sample points that are exactly pixel-wise integers, and normalise classification value, we can visualise a SVS as an image for example in figure~\ref{fig:svs}.
-In other words, our architecture will also works for images with landmarks similar to SVS visualisations like drawing.
-Assuming the intensity of a gray-scale image simulate the decision function, named $\bm{I_i}(x), x \in \Omega, i \in \{1,...F\}$.
-But in this situation, pixels at image space are discontinued, so $x$ is constrained to be integer and within the view window of size $N\times M$.
+This shape flow-based dense AAM formulation provides an exceptionally effective modeling and fitting for various objects, such as ears and faces, whose appearance has characteristic structures spread all over the object region (even if these structures cannot be consistently annotated).
+Therefore, what has been described so far completes our proposed approach in training and fitting deformable models of this type of objects.
+
+However, there exist other challenging object types, such as forearms, legs and full body, that not only cannot be consistently annotated with landmarks, but also whose appearance is informative almost entirely on the object outline and not in the interior object region.
+This is due to the hugely varying texture of these objects (e.g.~colors and patterns of clothes) that is typically totally unrelated to their shape.
+For these cases, we propose to add some additional steps on our methodology.
+More specifically, we propose to focus on the dense correspondences solely on the object outline, utilize them to automatically estimate highly-accurate object skeleton landmarks and then adopt a parts-based deformable modeling.
+These steps will be described in the next section.
 
@@
 
-The
+As already mentioned, for estimating body pose and modeling other object types with similar challenges, we propose to only consider the established correspondences on the object outline.
 
-\subsection{Part-based AAMs}
+Based on the proposed shape flow framework, we develop a methodology for robust automatic landmarking of the object outline.
+This allows a small initial training set that is manually annotated without consistent landmarks to be expanded to a much larger training set in an automatic way.
+In more detail, regarding the manually annotated images, for which SVS functions have been constructed, the outline correspondences are yielded by evaluating the estimated shape flow on the object outline of the reference image.
+To expand the training set to images without any annotations, we fit the trained dense AAM on these images and then only consider the deformed positions of the dense landmarks that correspond to the object outline on the mean shape.
+
+Having reliable object outline annotations on a large training set, we appropriately fuse their information to infer consistent landmarks on the object skeleton.
+This procedure equips deformable model training with consistent landmark annotations.
+This is particularly valuable, since it automates the training process and overcomes the limitations of inconsistent and inaccurate manual annotations on challenging objects such as forearms and legs.
+
+Based on these skeleton landmarks, we then train an parts-based deformable model. More specifically, ...

### 2015-10-30 contents/abstract.tex
Updates from ShareLaTeX

@@
 Annotation of images with landmarks is a tedious, laborious, expensive and labor intensive procedure.
-Furthermore, for some deformable objects it is not possible to find and annotate with regards to a consistent set of landmarks.
+Furthermore, for some deformable objects, e.g.
+human body, it is very  difficult to find a consistent set of landmarks or for other objects it is not possible at all to guide humans in order to annotate a collection of object images with regards to a consistent set of landmarks.
 Nevertheless, for the majority of objects, it is possible to extract the shape by object segmentation or even by shape drawing.
@@
 Such SDMs can be build with much less efforts and can generalize so as to describe a larger battery of objects.
+Furthermore, we show that by sampling on the dense model a part-based SDM can be learned with its parts being in correspondence.
+We apply our framework for developing an SDM of human arm and legs which can be used for the segmentation of the outline of the human body, as well as to provide better and more consistent annotations for body joints.

### 2015-11-03 contents/introduction.tex
Updates from ShareLaTeX

@@
 % \clearpage
+
 \begin{figure}[t!]
     \centering
-    \begin{subfigure}[b]{0.145\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.145\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-2}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.145\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-4}
     \end{subfigure}
     \\
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-2}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-3}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.07\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_3}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-4}
+    \end{subfigure}
+    \\
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.07\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_4}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-2}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.07\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_5}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-4}
     \end{subfigure}
     \\
-    \begin{subfigure}[b]{0.06\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_0}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.06\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_1}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-2}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.06\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_2}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-3}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.06\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_3}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-4}
     \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.06\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_4}
-    \end{subfigure}
-   	\hfill
-    \begin{subfigure}[b]{0.06\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_2_5}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_0}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_1}
-    \end{subfigure}
-   	\hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_4}
-    \end{subfigure}
-   	\hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_3_5}
-    \end{subfigure}
+
     \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}

### 2015-11-03 contents/evaluation.tex

\subsection{Databases}

\subsection{Error Metrics}

\begin{figure}[t!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist}
    \end{subfigure}
    \caption{Hand Benchmark.}
    \label{fig:variance}
\end{figure}

### 2015-11-03 contents/evaluation.tex
Updates from ShareLaTeX

@@
-\subsection{Databases}
+This sections evaluates the performance of proposed methodology in estimating correspondences of human poses in-the-wild.
+Results for quantitative an qualitative experiments are reported.
+Experiments \ref{exp:internal} investigate the accuracy of estimating dense correspondences of non-rigid deformable objects, and the impact of annotating outlines of human poses instead of annotating skeletons.
+Experiments \ref{exp:benchmark} compare the joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild.
+Note that all results reported in this section were obtained by fitting Patch AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
+For further experimental results and visualisations please refer to our supplementary material.
 
-\subsection{Error Metrics}
+\subsection{Databases \& Error Metrics}
+
+\subsection{Internal Evaluation}
+\label{exp:internal}
+
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.23\textwidth}
+            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow_joints}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.23\textwidth}
+            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist_joints}
+    \end{subfigure}
+    \caption{Hand Benchmark.}
+    \label{fig:internal_benchmark}
+\end{figure}
+
+\subsection{Benchmark Against State-if-the-art}
+\label{exp:benchmark}
 
@@
     \caption{Hand Benchmark.}
-    \label{fig:variance}
+    \label{fig:hand_benchmark}
 \end{figure}
+
+\subsection{Qualitative Results}
+\label{exp:qualitative}

### 2015-11-03 contents/introduction.tex

@@
 
-\item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
+\item The abundance of complex visual data, spread mostly through the Internet via web services such as Youtube, Flickr and Google Images.
 The latter has led to the development of large databases of "in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
-Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013}.
 
@@
 
+\item Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.
+
 \end{itemize}
 
-There are two drawbacks on building deformable models that rely on landmarks:
+There are two drawbacks on building deformable models that directly rely on landmarks:
 \begin{itemize}
 
-\item Annotating with regards to consistent landmark annotation is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person.
+\item Annotating with regards to consistent landmark annotation is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person .
 Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
@@
 Moreover, certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
+Another example is human body which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints.
+The task of annotation was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
+Unfortunately, these annotations are, in many cases, not consistent\footnote{From personal experience the quality of annotations that have been produced from AMT in case of faces are extremely inaccurate and cannot by any means compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:intro}).
+As it was also pointed out recently, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant \cite{tompson2015efficient}.
 
@@
 bottles, fruits etc.).
-Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently, Figure \ref{fig:intro}.
+Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently.
 That is why many state-of-the-art methods opt to leave the boundary out for comparison \cite{Tzimiropoulos2014, Asthana2014}.
@@
 In this paper, we provide a solution for annotating an object with regards to its deformations that requires considerable less effort and in the same time can be used to define statistical deformations for objects without consistent set of landmarks.
-That is, we argue that it is better to annotate an object with regards to a set of continuous lines that describe the shape of the object.
-An example is provided in Figure \ref{fig:intro} where the shape of the facial parts is annotated with continuous lines instead of a number of discrete landmarks.
-Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes 42, 38 and 43 secs per image for faces, ears and bottles correspondingly.
+We apply the proposed method to construct deformable models of the outline of  human body parts (e.g., arms and legs).
+To the best of our knowledge this is the first SDM of the outline of human body parts.
+The proposed SDM can be also used to provide accurate and consistent annotations of several of the body joints (such as wrist etc.).
+
+To this end, we argue and empirically demonstrate that it is better to annotate an object with regards to a set of continuous lines that describe the shape of the object.
+An example is provided in Figure \ref{fig:intro} where the shape of the human arm is annotated with continuous lines instead of a number of discrete landmarks.
+Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes 42, 38 and 43 secs per image for arm, faces, ears and bottles correspondingly.
 Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.
@@
 We show that the proposed methodology even though not tailored to landmark localization can be applied for landmark localization achieving very good performance.
-Finally, we demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
-To the best of our knowledge this is the first methodology which can create a dense statistical model for AAM which can operate in "in-the-wild".
+We demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
+Furthermore, We show that by sampling the shape of the dense AAM a part-based AAM can be trained with its parts being in correspondence.
+We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging database, outperforming state-of-the-art methods [..].
+Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for certain body parts.
+
+%To the best of our knowledge this is the first methodology which can %create a dense statistical model for AAM which can operate in %"in-the-wild".
 
@@
 \begin{itemize}
-  \item Constructing SDMs using training data with inconsistent annotation.
-  \item Introduce highly effective curve annotation which tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
-  \item Building dense correspondent SDMs with shape flow
+
+  \item We propose one of the first methodologies that construct SDMs from a set of training data with inconsistent annotation.
+We show that the proposed methodology, since it uses highly effective curve annotation, tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
+We show that by sampling the dense shape of SDM very powerful part-based SDMs can
+
+  \item We propose the first SDMs of the outline of human parts, such as human arms, which can be applied for both highly accurate body part segmentation and pose estimation, as well as for providing accurate annotations for body joints.
+
 \end{itemize}

### 2015-11-03 contents/introduction.tex
Updates from ShareLaTeX

@@
     \centering
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-1}
+    \begin{subfigure}[b]{0.115\textheight}
+            \includegraphics[height=2cm]{resources/MotivativeAnnotation/MPII}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-2}
+    \begin{subfigure}[b]{0.115\textheight}
+            \includegraphics[height=2cm]{resources/MotivativeAnnotation/FashionPose}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-3}
+    \begin{subfigure}[b]{0.115\textheight}
+            \includegraphics[height=2cm]{resources/MotivativeAnnotation/FLIC}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/BBCPose/bad_anno-4}
+    \begin{subfigure}[b]{0.115\textheight}
+            \includegraphics[height=2cm]{resources/MotivativeAnnotation/BBCPose}
     \end{subfigure}
     \\
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-1}
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-2}
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-3}
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FashionPose/bad_anno-4}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-1}
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-2}
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/FLIC/bad_anno-4}
-    \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-2}
-    \end{subfigure}
-  	\hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[width=\textwidth]{resources/MotivativeAnnotation/MPII/bad_anno-4}
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
     \end{subfigure}

### 2015-11-03 contents/introduction.tex
Updates from ShareLaTeX

@@
     \centering
-    \begin{subfigure}[b]{0.115\textheight}
-            \includegraphics[height=2cm]{resources/MotivativeAnnotation/MPII}
+    \begin{subfigure}[b]{0.09125\textwidth}
+            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/MPII}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textheight}
-            \includegraphics[height=2cm]{resources/MotivativeAnnotation/FashionPose}
+    \begin{subfigure}[b]{0.1125\textwidth}
+            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FashionPose}
     \end{subfigure}
   	\hfill
-    \begin{subfigure}[b]{0.115\textheight}
-            \includegraphics[height=2cm]{resources/MotivativeAnnotation/FLIC}
+    \begin{subfigure}[b]{0.125\textwidth}
+            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FLIC}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.115\textheight}
-            \includegraphics[height=2cm]{resources/MotivativeAnnotation/BBCPose}
+    \begin{subfigure}[b]{0.125\textwidth}
+            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/BBCPose}
+    \end{subfigure}
+    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
+    \label{fig:wrong_anno}
+\end{figure}
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.156\textwidth}
+            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.156\textwidth}
+            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_1}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.156\textwidth}
+            \includegraphics[height=2.8cm]{resources/Fig_Intro/intro_0_2}
     \end{subfigure}
     \\
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_0}
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_1_0}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_1}
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_1_1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_0_2}
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_1_2}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_0}
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_2_0}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_1}
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_2_1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Intro/intro_1_2}
+    \begin{subfigure}[b]{0.075\textwidth}
+            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_2_2}
     \end{subfigure}
@@
 Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
-Recently, we have witnessed tremendous developments in building and fitting models of human faces and bodies using images captured in unconstrained recording environments, usually referred to as "in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
+Recently, we have witnessed tremendous developments in building and fitting models of human faces and bodies using images captured in unconstrained recording environments, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
 This is attributed to:
@@
 \item The abundance of complex visual data, spread mostly through the Internet via web services such as Youtube, Flickr and Google Images.
-The latter has led to the development of large databases of "in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
+The latter has led to the development of large databases of ``in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
 
@@
 Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}.
-However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected "in-the-wild".
-On the other hand, the method of \cite{antonakos2014automatic}, which can deal with "in-the-wild" images, requires a set of consistently annotated sparse shapes to perform deformable face congealing.
+However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected ``in-the-wild".
+On the other hand, the method of \cite{antonakos2014automatic}, which can deal with ``in-the-wild" images, requires a set of consistently annotated sparse shapes to perform deformable face congealing.
 

### 2015-11-04 contents/evaluation.tex
git ignore added, annotation figure added
Updates from ShareLaTeX

@@
 \subsection{Databases \& Error Metrics}
+There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{}, BBC Pose\cite{}, Fashion Pose\cite{} and MPII\cite{} attracted most public attention.
+In our work, we reported our performance comparison on BBC Pose Dataset\cite{}, which has relatively most consistent skeleton annotation among the others.
+
+The training of dense Active Appearance Models (dAAMs) for upper body involves manual outline annotation from a combination of datasets, including H3D\cite{}, Microsoft COCO\cite{}, MPII\cite{}, Fashion Pose\cite{}, FLIC\cite{} and BBC Poses\cite{}.
+The training set contains 891 training images from where 500 are annotated with outline manually.
+A dAAMs is built from 500 training images thereby produces dense correspondences for generating sparse outline annotation.
+A Patch AAM is build from sparse annotations before fitting to 391 images.
+Manual minor correction are required for putting those fitted image to training set.
+The final Patch AAM is built from 891 images and validated on validation set given by BBC Pose.
 
@@
 
-\subsection{Benchmark Against State-if-the-art}
+\subsection{Benchmark Against State-of-the-art}
 \label{exp:benchmark}

### 2015-11-04 contents/introduction.tex
Updates from ShareLaTeX

@@
             \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/MPII}
+            \caption{MPII}
     \end{subfigure}
@@
             \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FashionPose}
+            \caption{Fashion}
     \end{subfigure}
@@
             \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FLIC}
+            \caption{FLIC}
     \end{subfigure}
@@
             \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/BBCPose}
+            \caption{BBC Pose}
     \end{subfigure}
-    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
+    \caption{Visualisation of inconsistent and inaccurate annotations of human pose among different datasets. Original annotation are shown in yellow dots while better annotations shown in blue dots.}
     \label{fig:wrong_anno}
@@
     \\
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_1_0}
+    \begin{subfigure}[b]{0.085\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_0}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_1_1}
+    \begin{subfigure}[b]{0.085\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_1_2}
+    \begin{subfigure}[b]{0.085\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_2}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_2_0}
+    \begin{subfigure}[b]{0.065\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_0}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_2_1}
+    \begin{subfigure}[b]{0.065\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_1}
     \end{subfigure}
     \hfill
-    \begin{subfigure}[b]{0.075\textwidth}
-            \includegraphics[height=2.35cm]{resources/Fig_Intro/intro_2_2}
+    \begin{subfigure}[b]{0.065\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_2}
     \end{subfigure}
 
-    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears, bottles and human actions.}
+    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears and hands.}
     \label{fig:intro}

### 2015-11-04 contents/evaluation.tex
Evaluation Edit

--- 2015-11-03 contents/evaluation.tex
@@
 \subsection{Databases \& Error Metrics}
+There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
+In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
+
+The training of dense Active Appearance Models (dAAMs) for upper body involves manual outline annotation from a combination of datasets, including H3D\cite{PoseletsICCV09}, Microsoft COCO\cite{lin2014microsoft}, MPII\cite{andriluka14cvpr}, Fashion Pose\cite{dantone2013human}, FLIC\cite{sapp2013modec} and BBC Poses\cite{pfister2015flowing}.
+The training set contains 891 training images from where 500 are annotated with outline manually.
+A dAAMs is built from 500 training images thereby produces dense correspondences for generating sparse outline annotation (29 landmarks).
+A Patch AAM is build from sparse annotations before fitting to 391 images.
+Manual minor correction are required for putting those fitted image to training set.
+The final Patch AAM is built from 891 images and validated on validation set given by BBC Pose.
+
+In order to compare with current state-of-the-art human pose estimation on BBC Pose, we uses same error metric as BBC Poses does, which normalises testing images to have height of 256 pixels.
+Performance measure of experiments in this paper are plot with Cumulative Error Distribution (CED) curve, where graph shows accuracy against distance from ground truth in pixels on normalised images.
+
+\subsection{Benchmark Against State-of-the-art}
+\label{exp:benchmark}
+This experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting.
+We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
+Dense scale-invariant feature transform (DSIFT)\cite{PoseletsICCV09} feature is used from image representation for our model.
+Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset.
+Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton.
+For our model, joints are projected from the dense correspondence generated from our proposed method.
+
+Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are reported in Table \ref{tab:hand_benchmark}.
+Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms.
+In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error \leq 6pt) on wrist, as well as marginal improvement on elbow estimation.
+
+\begin{figure}[b!]
+    \centering
+    \begin{subfigure}[b]{0.23\textwidth}
+            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.23\textwidth}
+            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow}
+    \end{subfigure}
+    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
+    \label{fig:hand_benchmark}
+\end{figure}
+
+\begin{table}[b!]
+    \small
+    \centering
+    \begin{tabular}{|l|c|c|c||c|c|c|}
+        \hline
+                            & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
+        \hline
+        \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
+        \hline\hline
+        Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
+        Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
+        Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
+        Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
+        Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
+        Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
+        \hline\hline
+        Ours                & \textbf{6.791}& \textbf{10.910}   & \textbf{63.1\%}       & \textbf{8.250}     &  \textbf{10.564}        & 52.1\%\\
+        \hline
+    \end{tabular}
+    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
+    \label{tab:hand_benchmark}
+\end{table}
 
@@
 
-\subsection{Benchmark Against State-if-the-art}
-\label{exp:benchmark}
-
-\begin{figure}[t!]
-    \centering
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist}
-    \end{subfigure}
-    \caption{Hand Benchmark.}
-    \label{fig:hand_benchmark}
-\end{figure}
-
 \subsection{Qualitative Results}

### 2015-11-05 contents/introduction.tex
updates on technical parts

@@
 % %(2)
-% Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised and semi supervised learning of models for the tasks of alignment, landmark localization, tracking and recognition has attracted considerable attention \cite{?}.
+% Due to the fact that manual annotation is a rather costly and labour-intensive procedure, unsupervised and semi supervised learning of models for the tasks of alignment, landmark localisation, tracking and recognition has attracted considerable attention \cite{?}.
 As our proposed framework are available to handle landmarks with inconsistency, it leads to a more efficient, convenient, unbiased and simple annotation methods - curve annotation.
@@
     \centering
+    \begin{subfigure}[b]{0.065\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.065\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.065\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.085\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.085\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_1}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.085\textwidth}
+            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_2}
+    \end{subfigure}
+    \\
     \begin{subfigure}[b]{0.156\textwidth}
@@
     \end{subfigure}
-    \\
-    \begin{subfigure}[b]{0.085\textwidth}
-            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_0}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.085\textwidth}
-            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.085\textwidth}
-            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_1_2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.065\textwidth}
-            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_0}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.065\textwidth}
-            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_1}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.065\textwidth}
-            \includegraphics[height=2.55cm]{resources/Fig_Intro/intro_2_2}
-    \end{subfigure}
-
-    \caption{Demonstration of classical landmark annotation and curve annotation of faces, ears and hands.}
+    \caption{Comparison of the classical landmark annotation (red dots) with the curve annotation (blue lines) of hands, ears and faces.}
     \label{fig:intro}
@@
 
-\item Annotating with regards to consistent landmark annotation is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person .
+\item Annotating with regards to consistent landmarks is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person.
 Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
 For example human ears have very complicated inner structures (e.g.
-helix, crus antihelicis, scapha, tragus, lobe etc.) which differs remarkably between ears.
-Moreover, certain ear parts, such as  Fossa Triangularies and Crus Helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
+helix, crus antihelicis, scapha, tragus, lobe etc.) which differ remarkably between ears.
+Moreover, certain ear parts, such as  fossa triangularies and crus helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
 Another example is human body which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints.
 The task of annotation was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
-Unfortunately, these annotations are, in many cases, not consistent\footnote{From personal experience the quality of annotations that have been produced from AMT in case of faces are extremely inaccurate and cannot by any means compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:intro}).
-As it was also pointed out recently, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant \cite{tompson2015efficient}.
+Unfortunately, these annotations are, in many cases, not consistent\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot by any means be compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:intro}).
+As it was also pointed out recently \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.
 
-\item The nature of many deformable objects does not allow them to be consistently annotated with regards to a consistent set of landmarks (e.g.
-bottles, fruits etc.).
+\item The nature of many deformable objects does not allow them to be annotated with regards to a consistent set of landmarks (e.g.~bottles, fruits etc.).
 Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently.
-That is why many state-of-the-art methods opt to leave the boundary out for comparison \cite{Tzimiropoulos2014, Asthana2014}.
+That is why many state-of-the-art methods opt to leave the boundary out from the comparisons \cite{Tzimiropoulos2014, Asthana2014}.
 The majority of the state-of-the-art methods for model-based landmark localisation \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable for objects with inconsistent sets of landmarks.
@@
 
+\section{Contributions}
+
 In this paper, we provide a solution for annotating an object with regards to its deformations that requires considerable less effort and in the same time can be used to define statistical deformations for objects without consistent set of landmarks.
 We apply the proposed method to construct deformable models of the outline of  human body parts (e.g., arms and legs).
-To the best of our knowledge this is the first SDM of the outline of human body parts.
+To the best of our knowledge, this is the first SDM of the outline of human body parts.
 The proposed SDM can be also used to provide accurate and consistent annotations of several of the body joints (such as wrist etc.).
@@
 To this end, we argue and empirically demonstrate that it is better to annotate an object with regards to a set of continuous lines that describe the shape of the object.
-An example is provided in Figure \ref{fig:intro} where the shape of the human arm is annotated with continuous lines instead of a number of discrete landmarks.
-Similarly, the shape annotations for the ear, a bottle and human body is shown in Figure \ref{fig:intro} Annotating facial images by following this procedure takes 42, 38 and 43 secs per image for arm, faces, ears and bottles correspondingly.
-Furthermore, these shapes can be automatically produced by recent methods that perform discriminative segmentation of objects.
+An example is provided in Figure \ref{fig:intro}, where classical landmark annotations are compared with the proposed curve annotations for hands, ears and faces.
+It is evident that curve annotations avoid the inherent ambiguity of placing sparse landmarks and offer a richer description of the object shape.
+%
+%where the shape of the human arm is annotated with continuous lines instead of a number of discrete landmarks.
+Similarly, the shape annotations for an ear and a face are shown in the same figure.
+Annotating images by following this procedure takes 42, 38 and 43 secs per image for arm, faces, ears correspondingly.
+Furthermore, these curves can be automatically produced by recent methods that perform discriminative segmentation of objects.
 
-Furthermore, we show that flow methods have mature enough so that it can be used to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods \cite{Garg:2013hu,Nguyen2013}.
-In particular, to build dense correspondence between independent shapes, we apply optical flow on shapes with low rank constrains, so we name it shape flow.
-Optical flow is originally applied to video sequences that several assumptions holds, illumination consistency and motion smoothness, while shapes having no motion smoothness completely as all training data are independent.
-Low rank constrain plays important role to simulate motion smoothness assumption.
+In addition, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods \cite{Nguyen2013}.
+In particular, to build dense correspondences between different shapes of the same object type, we estimate the optical flow among all shapes jointly by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.
+Multiframe optical flow is originally applied on video sequences, relying on the assumptions of color constancy and motion smoothness.
+However, these assumptions do not hold in our case, where we have a collection of shapes, therefore we introduce appropriate modifications of the multiframe optical flow formulation, based on consistency of the image-based shape representation and low rank priors.
+%
+%On the other hand,  while shapes having no motion smoothness completely as all training data are independent. Low rank constrain plays important role to simulate motion smoothness assumption.
 
-We show that this way dense correspondences between images can be established and dense Active Appearance Models (AAMs) can be build on top of that.
-We show that the proposed methodology even though not tailored to landmark localization can be applied for landmark localization achieving very good performance.
+After establishing dense shape correspondences, we describe how dense Active Appearance Models (AAMs) can be built on top of that.
+We show that the proposed methodology can be applied for landmark localisation, even though not tailored for that task, achieving particularly good performance.
 We demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
-Furthermore, We show that by sampling the shape of the dense AAM a part-based AAM can be trained with its parts being in correspondence.
-We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging database, outperforming state-of-the-art methods [..].
-Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for certain body parts.
+Furthermore, We show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence.
+We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods [..].
+Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for different body parts.
 
@@
 
-Summarizing, the contributions proposed in this paper are:
+Summarizing, the contributions proposed in this paper are the following:
 \begin{itemize}
 
-  \item We propose one of the first methodologies that construct SDMs from a set of training data with inconsistent annotation.
+  \item We propose one of the first methodologies that construct SDMs from a set of training data with inconsistent annotations.
 We show that the proposed methodology, since it uses highly effective curve annotation, tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.

### 2015-11-05 contents/evaluation.tex
New Figures

@@
 Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms.
-In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error \leq 6pt) on wrist, as well as marginal improvement on elbow estimation.
+In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
 

### 2015-11-05 contents/implementation.tex
Updates from ShareLaTeX

@@
 
-We propose a novel framework for building deformable models that does not require any consistent set of annotated landmarks and is based on a dense shape representation.
+This section presents the proposed method for establishing dense correspondences among training shapes 
+by only using curve annotations. Our pipeline is depicted in Figure~\ref{fig:archi}. 
+%
+%We propose a novel framework for building deformable models that does not require any consistent set of annotated landmarks and is based on a dense shape representation.
 Our method only requires a set of point or curve line annotations that does not need to be consistent over different training samples.
-It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.
-
-The proposed pipeline is depicted in Figure~\ref{fig:archi}. It takes as input a set of training images of a particular object class, along with inconsistent point and/or curve line annotations.
-As a first step, all the shape annotations are consistently represented using multichannel SVS.
+%
+%It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.
+%
+It takes as input a set of training images of a particular object class, along with curve annotations.
+As a first step, all the curve annotations are consistently represented using a multichannel extension of the Support Vector Shape (SVS) representation \cite{Nguyen2013}.
 The next step is the application of Iterative Closest Point (ICP) algorithm \cite{Besl1992} to achieve an initial simple alignment of the SVS images.
@@
 Finally, the dense correspondences yield by optical flow serve as automatically generated dense landmark annotations and are used to define a novel dense version of Active Appearance Models.
-The upcoming sections discuss each of the previous stages in further detail.
+The upcoming sections discuss each of the aforementioned steps in further detail.
 
@@
 In this section, we present the entire architectures, design decision and algorithms.
-\subsection{Shape Representation Without Consistent Annotations}
+\subsection{Shape Representation Based on Support Vector Shapes}
 \label{sec:svs}
@@
 
-In practice, we assume that all the training images correspond to the same object category and contain a set of inconsistent points and curve line annotations.
-All annotations are densely sampled to yield a set of annotated landmarks per image, with this set being different for every training image.
-Initially, negative points get randomly sampled around sparse landmarks while annotated landmarks are positive points.
-Since the number of positive points is far smaller that the number of negative ones, landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are the number of positive/negative samples and $W_p, W_n$ are their corresponding weights.
+%In practice, we assume that all the training images correspond to the same object category and contain a set of inconsistent points and curve line annotations. 
+The curve annotations for all training images are densely sampled to yield a set of landmarks per image, with this set being different for every training image.
+To train the SVM, these landmarks are assigned as belonging to the class with label `+1', whereas randomly sampled points around them are assigned as belonging to the class with label `-1'.
+Since the class `+1' has far less points than the class `-1', landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of points of the class `+1' and `-1' respectively and $W_p, W_n$ are their corresponding weights.
 
@@
 \end{equation}
-where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel .
+where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel.
+The decision function $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret is as an image and we call it \emph{SVS image}.
 
@@
 
+We extend the SVS representation to support also the case where multiple curves with different labels are annotated.
+This is useful when annotating different structures of the same object, such as the curve of the left eyebrow and the curve of the right eyebrow on faces.
+Even though not absolutely necessary in our framework, it can provide further guidance on the estimation of dense shape correspondences.
+In more detail, we create a multi-channel SVS image $\bm{d}(\bm{x})=[d_1(\bm{x}) \cdots d_i(\bm{x}) \cdots d_{N_c}(\bm{x})]$, where $d_i(\bm{x})$ is the SVS image that corresponds to the curve annotation of the $i$-th structure and $N_c$ is the total number of structures (a single curve annotation is the special case where $N_c=1$).
+Note that we do not necessarily require that all structures are annotated in all the object images: in the case that a structure is not annotated, the corresponding channel of the SVS image simply takes a zero value for all pixels.
+The shape flow estimation can deal with such missing information thanks to the spatial regularisation and the low-rank constraint that it adopts, c.f.~Section \ref{sec:shapeflow}.
+
 After constructing the SVS representation for all images, the next step is to apply a simple similarity alignment over them.
@@
 
-\subsection{Shape Correspondence Basis}
+\subsection{Correspondence Basis for Shape Flow Estimation}
 
-We consider the problem of dense correspondences across SVS images as a joint estimation of optical flow fields between a reference SVS image and every SVS image of the training dataset.
-The estimation of such a ``shape flow'' defines for every training SVS image a warping function that registers it with the reference SVS image.
+We define the problem of shape flow as the joint estimation of optical flow fields between a reference SVS image and every SVS image of the training dataset, which yields dense correspondences across SVS images.
+This also defines for every training SVS image a warping function that registers it with the reference SVS image.
 To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu}.
@@
 
-Formally, let $F$ be the number of training SVS images and $n=1,\ldots,F$ be the training image index. Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
-\{1,\ldots,F\} \rightarrow \R^2$ be the $R$ orthonormal elements of the correspondence basis, where $\boldsymbol{q}_i(n)$ is the displacement vector that matches the points of the reference SVS image with the points of the $n$-th training SVS image, according to the variation described from the $i$-th correspondence basis element.
+Formally, let $N_t$ be the number of training SVS images and $n=1,\ldots,N_t$ be the training image index. Also, let $\boldsymbol{q}_1(n),\ldots,\boldsymbol{q}_R(n):
+\{1,\ldots,N_t\} \rightarrow \R^2$ be the $R$ orthonormal elements of the correspondence basis, where $\boldsymbol{q}_i(n)$ is the displacement vector that matches the points of the reference SVS image with the points of the $n$-th training SVS image, according to the variation described from the $i$-th correspondence basis element.
 Note that the basis elements $\boldsymbol{q}_i(n)$ are independent from the point location.
-Note also that the number of basis elements is typically much smaller than the full dimensionality ($2 F$) of correspondence vectors, therefore this basis plays a role of dimensionality reduction.
+Note also that the number of basis elements is typically much smaller than the full dimensionality ($2 N_t$) of correspondence vectors, therefore this basis plays a role of dimensionality reduction.
 
-In addition, let $\Omega \subset \R^2$ be the image domain of the SVS images and $\bx$ denote the point location. We denote the shape flow result as $\bm{u}_n(\bx):\Omega\times \{1,\ldots,F\}
+In addition, let $\Omega \subset \R^2$ be the image domain of the SVS images and $\bx$ denote the point location. We denote the shape flow result as $\bm{u}_n(\bx):\Omega\times \{1,\ldots,N_t\}
 \rightarrow \R^2$,  where $\bm{u}_n(\bx)$ is the displacement vector that matches the point $\bx$ of the reference SVS image with its corresponding location at the $n$-th training SVS image.
@@
 
-\subsection{Shape Flow}
+\subsection{Shape Flow Estimation}
 \label{sec:shapeflow}
 
-Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
+%Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
 We propose to perform this estimation simultaneously for all training data, by using the correspondence basis.
-This procedure, which we call \emph{shape flow}, builds upon robust methods for multiframe optical flow estimation \cite{Garg:2013hu}.
+
+As already mentioned, our shape flow estimation builds upon robust methods for multiframe optical flow estimation \cite{Garg:2013hu}.
 However, optical flow estimation typically works based on the assumptions of brightness or colour constancy and motion smoothness, whereas in our setting the input training data correspond to shapes.
@@
 This yields an initial estimation of the correspondence vectors on the sparse locations of annotated landmarks on the reference shape.
-To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference SVS image), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation.
+Finally, the correspondence basis is found by applying PCA on these  correspondence vectors and keeping only the first $R$ principal components.
+
+%To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference SVS image), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation.
 Finally, the correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.
@@
 
+% \begin{figure}[t!]
+%         \centering
+%         \begin{tabular}{cccccccc}
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_0}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_1}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_2}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_3}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_4}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_5}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_6}
+%         &
+%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/variances}
+%         \end{tabular}
+%     \caption{Variances}
+%     \label{fig:variances}
+% \end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_1}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_4}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_6}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/variances}
+    \end{subfigure}
+    \caption{Variance.}
+    \label{fig:variance}
+\end{figure}
+
 \subsubsection{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
@@
 
-Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training SVS images $\bm{d}_n(\bx)$ by minimizing the following energy:
+Let $\bm{d}(\bx;n)$, $\bm{d}(\bx;0):\Omega\rightarrow \R^{N_c}$ be the $n$-th training SVS image and the reference SVS image respectively.
+Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training images by minimizing the following energy:
 \begin{align}
 E_{sf} & =\alpha
-\int_{\Omega}\sum_{n=1}^F \|\bm{d}_n(\bx+\bm{u}_n(x))-\bm{d}_0(x)\| \ud \bx \label{eq:costfunc}\\
-    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
+\int_{\Omega}\sum_{n=1}^{N_t} \|\bm{d}(\bx+\bm{u}_n(x);n)-\bm{d}(x;0)\| \ud \bx \label{eq:costfunc}\\
+    &+ \beta \int_{\Omega}\sum_{n=1}^{N_t}\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
     &+

### 2015-11-05 contents/abstract.tex
Updates from ShareLaTeX

--- 2015-10-28 contents/abstract.tex
@@
 
-The past few years we have witnessed the development of many methodologies for constructing and fitting statistical deformable models.
-The construction of Statistical Deformable Models (SDMs) usually requires careful annotation of images with regards to a set of landmarks.
-Annotation of images with landmarks is a tedious, laborious, expensive and labor intensive procedure.
-Furthermore, for some deformable objects it is not possible to find and annotate with regards to a consistent set of landmarks.
+During the past few years we have witnessed the development of many methodologies for constructing and fitting Statistical Deformable Models (SDMs).
+The construction of accurate SDMs requires careful annotation of images with regards to a consistent set of landmarks.
+However, the manual annotation of a large amount of images is a tedious, laborious and expensive procedure.
+Furthermore, for several deformable objects, e.g.
+human body, it is difficult to define a consistent set of landmarks, and, thus, it becomes impossible to train humans in order to accurately annotate a collection of images.
 Nevertheless, for the majority of objects, it is possible to extract the shape by object segmentation or even by shape drawing.
 In this paper, we show for the first time, to the best of our knowledge, that it is possible to construct SDMs by putting object shapes in dense correspondence.
-Such SDMs can be build with much less efforts and can generalize so as to describe a larger battery of objects.
+Such SDMs can be built with much less effort and can generalise so as to describe a larger battery of objects.
+Additionally, we show that by sampling the dense model a part-based SDM can be learned with its parts being in correspondence.
+We apply our framework for developing an SDM of human arm and legs which can be used for the segmentation of the outline of the human body, as well as to provide better and more consistent annotations for body joints.

### 2015-11-05 contents/introduction.tex

@@
 The task of annotation was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
-Unfortunately, these annotations are, in many cases, not consistent\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot by any means be compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:intro}).
+Unfortunately, these annotations are, in many cases, not consistent\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot by any means be compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:wrong_anno}).
 As it was also pointed out recently \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.
@@
 Furthermore, We show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence.
-We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods [..].
+We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods \cite{pfister2015flowing}.
 Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for different body parts.

### 2015-11-05 contents/abstract.tex
Updates from ShareLaTeX

@@
 Such SDMs can be built with much less effort and can generalise so as to describe a larger battery of objects.
-Additionally, we show that by sampling the dense model a part-based SDM can be learned with its parts being in correspondence.
-We apply our framework for developing an SDM of human arm and legs which can be used for the segmentation of the outline of the human body, as well as to provide better and more consistent annotations for body joints.
+Additionally, we show that, by sampling the dense model, a part-based SDM can be learned with its parts being in correspondence.
+We employ our framework to develop SDMs of human arms and legs, which can be used for the segmentation of the outline of the human body, as well as to provide better and more consistent annotations for body joints.

### 2015-11-05 contents/evaluation.tex
Updates from ShareLaTeX

@@
 In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
+
+\begin{figure}[t!]
+    \centering
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_1}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_3}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_4}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.05\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_6}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[width=\textwidth]{resources/Fig_Variance/variances}
+    \end{subfigure}
+    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
+    \label{fig:variance}
+\end{figure}
 
@@
 We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
-Dense scale-invariant feature transform (DSIFT)\cite{PoseletsICCV09} feature is used from image representation for our model.
+Dense Scale-Invariant Feature Transform (SIFT)\cite{PoseletsICCV09} feature is used from image representation for our model.
 Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset.
@@
         \hline\hline
-        Ours                & \textbf{6.791}& \textbf{10.910}   & \textbf{63.1\%}       & \textbf{8.250}     &  \textbf{10.564}        & 52.1\%\\
+        Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
         \hline

### 2015-11-05 contents/introduction.tex

@@
     \end{subfigure}
-    \caption{Visualisation of inconsistent and inaccurate annotations of human pose among different datasets. Original annotation are shown in yellow dots while better annotations shown in blue dots.}
+    \caption{Visualisation of inconsistent and inaccurate annotations of human pose among different datasets.
+\emph{Blue} dots denote the original annotations.
+The arrows and \emph{green} dots show the correct location at which the points should be.
+    %Original annotations are shown in blue dots while better annotations shown in green dots.
+    }
     \label{fig:wrong_anno}
@@
     \end{subfigure}
-    \caption{Comparison of the classical landmark annotation (red dots) with the curve annotation (blue lines) of hands, ears and faces.}
+    \caption{Comparison of the standard landmark annotation (\emph{red} dots) with the curve annotation (\emph{blue} lines) on hands, ears and faces.}
     \label{fig:intro}
@@
 
-Building and fitting statistical deformable models of objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
-Recently, we have witnessed tremendous developments in building and fitting models of human faces and bodies using images captured in unconstrained recording environments, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
+Building and fitting Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
+Recently, we have witnessed tremendous developments in building and fitting SDMs of human faces and bodies using images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
 This is attributed to:
 \begin{itemize}
-
-\item The abundance of complex visual data, spread mostly through the Internet via web services such as Youtube, Flickr and Google Images.
-The latter has led to the development of large databases of ``in-the-wild" images of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
+\item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
+The latter has led to the development of large ``in-the-wild" databases of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
 
@@
 \item Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.
-
 \end{itemize}

### 2015-11-05 contents/abstract.tex

@@
 
-During the past few years we have witnessed the development of many methodologies for constructing and fitting Statistical Deformable Models (SDMs).
+During the past few years we have witnessed the development of many methodologies for building and fitting Statistical Deformable Models (SDMs).
 The construction of accurate SDMs requires careful annotation of images with regards to a consistent set of landmarks.
@@
 In this paper, we show for the first time, to the best of our knowledge, that it is possible to construct SDMs by putting object shapes in dense correspondence.
-Such SDMs can be built with much less effort and can generalise so as to describe a larger battery of objects.
+Such SDMs can be built with much less effort for a large battery of objects.
 Additionally, we show that, by sampling the dense model, a part-based SDM can be learned with its parts being in correspondence.

### 2015-11-05 contents/introduction.tex

@@
     \end{subfigure}
-    \caption{Visualisation of inconsistent and inaccurate annotations of human pose among different datasets.
+    \caption{Examples of inconsistent and inaccurate annotations of human pose among different datasets.
 \emph{Blue} dots denote the original annotations.
@@
     \end{subfigure}
-    \caption{Comparison of the standard landmark annotation (\emph{red} dots) with the curve annotation (\emph{blue} lines) on hands, ears and faces.}
+    \caption{Comparison of the standard landmark annotation (\emph{red} dots) with the curve annotation (\emph{blue} lines) on arms, ears and faces.
+It is evident that the curve annotations surpass the inevitable inconsistency of sparse annotations.}
     \label{fig:intro}
@@
 
-Building and fitting Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
-Recently, we have witnessed tremendous developments in building and fitting SDMs of human faces and bodies using images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
+Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
+Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
 This is attributed to:
 \begin{itemize}
-\item The abundance of complex visual data, spread mostly through the internet via web services such as Youtube, Flickr and Google Images.
-The latter has led to the development of large ``in-the-wild" databases of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
+\item The abundance of complex visual data, spread through web services (e.g.
+Youtube, Flickr, Google Images), which has led to the development of ``in-the-wild" databases of human faces and bodies \cite{Belhumeur2011, Le2012, Zhu2012, Burgos2013}.
 
-\item The development of powerful visual features, able to describe objects and its parts in a robust manner (e.g., Scale Invariant Feature Transforms (SIFT) \cite{lowe1999object}, Histogram of Oriented Gradients (HoGs) \cite{Dalal2005} and recently Deep Convolutional Neural Networks \cite{sermanet2013overfeat}), as well as generative and discriminative methodologies for learning deformable models.
+\item The manual annotation of such databases that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.
 
-\item Equally important is the task of manual annotation of images with regards to face and body parts and that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.
+\item The development of powerful visual features that are able to describe objects and their parts in a robust manner (e.g., SIFT \cite{lowe1999object}, HoGs \cite{Dalal2005}
+%and Deep Convolutional Neural Networks \cite{sermanet2013overfeat}
+), as well as generative and discriminative methodologies for learning SDMs.
 \end{itemize}
 
-There are two drawbacks on building deformable models that directly rely on landmarks:
+However, there are two main drawbacks when building SDMs directly on manually annotated landmarks:
 \begin{itemize}
@@
 \item Annotating with regards to consistent landmarks is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person.
-Furthermore, for many objects it requires a highly skilled person to identify and annotate a set of images with regards to a consistent set of landmarks.
-For example human ears have very complicated inner structures (e.g.
-helix, crus antihelicis, scapha, tragus, lobe etc.) which differ remarkably between ears.
-Moreover, certain ear parts, such as  fossa triangularies and crus helicis, do not appear in all ears and  their visibility is highly sensitive to pose and illumination variation.
-Another example is human body which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints.
-The task of annotation was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
-Unfortunately, these annotations are, in many cases, not consistent\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot by any means be compared with the ones provided by the recent competition \cite{sagonas_iccv_300w_2013}} (please see Figure \ref{fig:wrong_anno}).
-As it was also pointed out recently \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.
+Furthermore, for various object classes, it requires a highly skilled person in order to identify and annotate landmarks in a consistent manner.
+For example, the human ear has very complicated inner structures (helix, crus antihelicis, scapha, tragus, lobe etc.) which remarkably differ between different ears.
+Moreover, certain ear parts, such as fossa triangularies and crus helicis, do not appear in all ears and their visibility is highly sensitive to the head pose and illumination variation.
+Another such example is the human body, which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints.
+For most body pose databases, annotation task was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
+Unfortunately, this resulted in acquiring inconsistent and inaccurate annotations, in many cases\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot, by any means, be compared with the ones provided by the recent 300W competition \cite{sagonas_iccv_300w_2013}.} (please see Figure \ref{fig:wrong_anno}).
+As it was also recently pointed out \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.
 
-\item The nature of many deformable objects does not allow them to be annotated with regards to a consistent set of landmarks (e.g.~bottles, fruits etc.).
-Also the boundary/outline of objects, such as faces, ears, body can be very difficultly annotated consistently.
-That is why many state-of-the-art methods opt to leave the boundary out from the comparisons \cite{Tzimiropoulos2014, Asthana2014}.
-The majority of the state-of-the-art methods for model-based landmark localisation \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable for objects with inconsistent sets of landmarks.
+\item The nature of many deformable objects does not allow them to be annotated with regards to a consistent set of landmarks (e.g., bottles, fruits etc.).
+Additionally, it is very difficult to consistently annotate the boundary/outline of certain objects such as faces, ears, body, since these landmarks do not have any semantic meaning.
+That is why many state-of-the-art methods opt to leave the boundary out when reporting results \cite{Tzimiropoulos2014, Asthana2014}.
+The majority of the state-of-the-art methods for model-based landmark localisation \cite{Cao2012, Zhu2012, Xiong2013, Tzimiropoulos2014, Asthana2014} are not applicable to objects with inconsistent sets of landmarks.
 
@@
 
-To illustrate how time consuming careful annotation of the human ear is we lay down our own experience.
+To illustrate how time consuming careful annotation of a complex deformable object is, we lay down our own experience based on the human ear.
 A trained annotator needs an average of 4 minutes per image for the manual annotation of 55 landmarks.
 This means that the annotation of 1000 images requires a total of about 67 hours.
-Furthermore,  training and fatigue largely influence the annotation accuracy.
+Furthermore, the quality of training as well as fatigue largely influence the annotation accuracy.
 Hence, a second pass on the annotated data is, in many cases, necessary.
-Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the tasks of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}.
-However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed the limited number of methods that have been applied to the task cannot be directly applied to arbitrary collection of images collected ``in-the-wild".
+Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the task of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}.
+However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed, the limited number of methods that have been proposed for the task cannot be directly applied to arbitrary collection of ``in-the-wild" images.
 On the other hand, the method of \cite{antonakos2014automatic}, which can deal with ``in-the-wild" images, requires a set of consistently annotated sparse shapes to perform deformable face congealing.
@@
 
-In this paper, we provide a solution for annotating an object with regards to its deformations that requires considerable less effort and in the same time can be used to define statistical deformations for objects without consistent set of landmarks.
-We apply the proposed method to construct deformable models of the outline of  human body parts (e.g., arms and legs).
-To the best of our knowledge, this is the first SDM of the outline of human body parts.
-The proposed SDM can be also used to provide accurate and consistent annotations of several of the body joints (such as wrist etc.).
+In this paper, we propose a solution for annotating an object with regards to its deformations that requires considerably less effort compared to manual annotation and, at the same time, can be used to define statistical deformations for objects without a consistent set of landmarks.
+We employ the proposed method in order to construct SDMs based on the outline of human body parts (i.e., arms and legs).
+To the best of our knowledge, this is the first time that an SDM is proposed to be trained on the outline of human body parts and not on their skeleton joints.
+The proposed SDM can also be used to provide accurate and consistent annotations for several of the body joints (such as wrist, elbow etc.).
 
-To this end, we argue and empirically demonstrate that it is better to annotate an object with regards to a set of continuous lines that describe the shape of the object.
-An example is provided in Figure \ref{fig:intro}, where classical landmark annotations are compared with the proposed curve annotations for hands, ears and faces.
-It is evident that curve annotations avoid the inherent ambiguity of placing sparse landmarks and offer a richer description of the object shape.
+To this end, we argue and empirically demonstrate that it is better to annotate an object with regards to a set of continuous lines that describe its shape.
+An example is provided in Figure \ref{fig:intro}, which compares the standard landmark annotations that are employed in the current literature with the proposed curve annotations for arms, ears and faces.
+It becomes evident that the curve annotations avoid the inherent ambiguity of placing sparse landmarks and offer a richer description of the object's shape.
 %
@@
 Annotating images by following this procedure takes 42, 38 and 43 secs per image for arm, faces, ears correspondingly.
-Furthermore, these curves can be automatically produced by recent methods that perform discriminative segmentation of objects.
+Furthermore, these curves can be automatically generated by recently proposed methods that perform discriminative segmentation of objects \cite{luo2013pedestrian,liu2015matching}.
 
-In addition, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using simple, as well as more recent and robust shape representations methods \cite{Nguyen2013}.
-In particular, to build dense correspondences between different shapes of the same object type, we estimate the optical flow among all shapes jointly by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.
-Multiframe optical flow is originally applied on video sequences, relying on the assumptions of color constancy and motion smoothness.
-However, these assumptions do not hold in our case, where we have a collection of shapes, therefore we introduce appropriate modifications of the multiframe optical flow formulation, based on consistency of the image-based shape representation and low rank priors.
+Furthermore, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using either simplistic or more even sophisticated and robust shape representation methods \cite{Nguyen2013}.
+In particular, to build dense correspondences between different shape instances of the same object class, we jointly estimate the optical flow among all the instances by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.
+Multiframe optical flow has originally been applied on video sequences, relying on the assumptions of color consistency and motion smoothness \cite{Garg:2013hu}.
+However, these assumptions do not hold in our case, where we have a collection of shapes.
+Therefore, we introduce appropriate modifications based on the consistency of image-based shape representation, as well as low rank priors.
 %
@@
 
-After establishing dense shape correspondences, we describe how dense Active Appearance Models (AAMs) can be built on top of that.
-We show that the proposed methodology can be applied for landmark localisation, even though not tailored for that task, achieving particularly good performance.
-We demonstrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
-Furthermore, We show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence.
+In addition, we demonstrate how dense Active Appearance Models (AAMs) can be built after establishing dense shape correspondences.
+We show that the proposed methodology can be applied for landmark localisation, even though it is not tailored for that task, achieving particularly good performance.
+We also illustrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
+We report state-of-the-art
+
+Furthermore, we show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence.
 We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods \cite{pfister2015flowing}.

### 2015-11-05 contents/introduction.tex

@@
     \centering
-    \begin{subfigure}[b]{0.09125\textwidth}
-            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/MPII}
+    \begin{subfigure}[b]{0.105\textwidth}
+            \includegraphics[height=5.5cm]{resources/MotivativeAnnotation/MPII}
             \caption{MPII}
@@
     \hfill
-    \begin{subfigure}[b]{0.1125\textwidth}
-            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FashionPose}
+    \begin{subfigure}[b]{0.115\textwidth}
+            \includegraphics[height=5.5cm]{resources/MotivativeAnnotation/FashionPose}
             \caption{Fashion}
@@
   	\hfill
-    \begin{subfigure}[b]{0.125\textwidth}
-            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/FLIC}
+    \begin{subfigure}[b]{0.22\textwidth}
+            \includegraphics[height=5.5cm]{resources/MotivativeAnnotation/FLIC}
             \caption{FLIC}
     \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.125\textwidth}
-            \includegraphics[height=3.25cm]{resources/MotivativeAnnotation/BBCPose}
-            \caption{BBC Pose}
-    \end{subfigure}
+    % \hfill
+    % \begin{subfigure}[b]{0.145\textwidth}
+    %         \includegraphics[height=4cm]{resources/MotivativeAnnotation/BBCPose}
+    %         \caption{BBC Pose}
+    % \end{subfigure}
     \caption{Examples of inconsistent and inaccurate annotations of human pose among different datasets.
@@
 
-Furthermore, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using either simplistic or more even sophisticated and robust shape representation methods \cite{Nguyen2013}.
-In particular, to build dense correspondences between different shape instances of the same object class, we jointly estimate the optical flow among all the instances by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.
+Furthermore, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using either simplistic or even more sophisticated and robust shape representation methods \cite{Nguyen2013}.
+In particular, in order to build dense correspondences between different shape instances of the same object class, we jointly estimate the optical flow among all the instances by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.
 Multiframe optical flow has originally been applied on video sequences, relying on the assumptions of color consistency and motion smoothness \cite{Garg:2013hu}.
@@
 In addition, we demonstrate how dense Active Appearance Models (AAMs) can be built after establishing dense shape correspondences.
-We show that the proposed methodology can be applied for landmark localisation, even though it is not tailored for that task, achieving particularly good performance.
+We show that the proposed methodology can be applied on landmark localisation, even though it is not tailored for that task, achieving particularly good performance.
 We also illustrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
-We report state-of-the-art
-
-Furthermore, we show that by sampling the shape of the dense AAM, a part-based AAM can be trained with its parts being in correspondence.
-We show that such a part-based AAM can used to produce state-of-the-art results in localisation of human body parts in challenging databases, outperforming state-of-the-art methods \cite{pfister2015flowing}.
+Furthermore, we show how to build a powerful part-based AAM on the sparse outline landmarks that are obtained by sampling the shape of the dense AAM.
+Using the resulting outline part-based AAM, we report state-of-the-art performance on the task of human body parts localisation on challenging databases.
 Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for different body parts.
@@
 
-Summarizing, the contributions proposed in this paper are the following:
+In summary, the contributions of this paper are the following:
 \begin{itemize}

### 2015-11-05 contents/introduction.tex
Updates from ShareLaTeX

@@
 
-  \item We propose one of the first methodologies that construct SDMs from a set of training data with inconsistent annotations.
-We show that the proposed methodology, since it uses highly effective curve annotation, tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
+  \item We propose one of the first methodologies that build accurate SDMs from a set of training data with inconsistent annotations.
+We show that the proposed methodology, thanks to the highly effective curve annotations, tremendously reduces manual workload but maintains same performance level against state-of-the-art SDMs.
 We show that by sampling the dense shape of SDM very powerful part-based SDMs can

### 2015-11-05 contents/implementation.tex
Updates from ShareLaTeX

@@
 This section presents the proposed method for establishing dense correspondences among training shapes 
-by only using curve annotations. Our pipeline is depicted in Figure~\ref{fig:archi}. 
+by only using curve annotations.
 %
@@
 %
-It takes as input a set of training images of a particular object class, along with curve annotations.
-As a first step, all the curve annotations are consistently represented using a multichannel extension of the Support Vector Shape (SVS) representation \cite{Nguyen2013}.
-The next step is the application of Iterative Closest Point (ICP) algorithm \cite{Besl1992} to achieve an initial simple alignment of the SVS images.
-The multichannel similarity-aligned SVS images are then fed into a multi-image subspace flow estimation that establishes dense correspondences between all the shapes in the training set.
-In order for the flow estimation to be accurate and exploit the correlation among all training shapes, it utilises a correspondence basis built from sparse correspondences obtained by applying Nonrigid ICP on the annotated data.
-Finally, the dense correspondences yield by optical flow serve as automatically generated dense landmark annotations and are used to define a novel dense version of Active Appearance Models.
+It takes as input a set of training images of a particular object class, along with the corresponding curve annotations.
+The steps of our pipeline, which are also depicted in Figure~\ref{fig:archi}, are the following:
+
+\noindent\textbf{Step 1:} Represent the curve annotations in a consistent way using a multichannel extension of the Support Vector Shape (SVS) representation \cite{Nguyen2013}.
+Apply the Iterative Closest Point (ICP) algorithm \cite{Besl1992} to achieve an initial alignment of the SVS images.
+
+\noindent\textbf{Step 2:} Construct a correspondence basis for the training SVS images.
+This is acquired by applying Non-rigid ICP on the densely sampled annotated curves, followed by Principal Component Analysis (PCA).
+
+\noindent\textbf{Step 3:} Establish dense correspondences between all the shapes in the training set by feeding the multichannel similarity-aligned SVS images into a multi-image subspace flow estimation.
+
+\noindent\textbf{Step 4:} Utilise the dense correspondences acquired by the optical flow in order to automatically generate dense and sparse (on the outline) landmark annotations and build a dense \cite{ramnath2008increasing, Amberg2009, anderson2014using} and part-based \cite{Tzimiropoulos2014} AAM, respectively.
+
 The upcoming sections discuss each of the aforementioned steps in further detail.
@@
 In this section, we present the entire architectures, design decision and algorithms.
-\subsection{Shape Representation Based on Support Vector Shapes}
-\label{sec:svs}
+\newcounter{steps}
+{\refstepcounter{steps}\label{sec:step1}\subsection*{Step 1: Shape Representation Based on Support Vector Shapes}}
+% \subsection{Shape Representation Based on Support Vector Shapes}
+% \label{sec:step1}
 %Ordinarily, construction of deformable model requires training data set having consistent number of landmarks.
@@
 
-In order to fully capture the variability among most deformable object shapes annotations, we use a representation based on Support Vector Shapes (SVS) \cite{Nguyen2013}.
-A SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with Radial Basis Function (RBF) kernels.
-In this way, a shape is represented as a classifier function, which has several advantages: (a) the representation is completely general, \eg it can be applied to sparse landmark points, curves lines or a combination of the two and (b) it fuses inconsistent landmarks into consistent and directly comparable decision functions.
+In order to fully capture the variability among most deformable objects' shapes annotations, we use a representation based on Support Vector Shapes (SVS) \cite{Nguyen2013}.
+An SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with Radial Basis Function (RBF) kernels.
+In this way, a shape is represented as a classifier function, which has several advantages: (a)~the representation is completely generic, e.g.
+it can be applied to sparse landmark points, curves lines or a combination of the two, and~(b) it fuses inconsistent landmarks into consistent and directly comparable decision functions.
 Furthermore, this representations is also robust against noise, missing data and outliers \cite{Nguyen2013}.
@@
 
-Figure \ref{fig:build_svs} shows an exemplar shape representation using SVS. As it can be observed, the final result does not drastically depend on the original number of annotated landmarks.
+Figure \ref{fig:build_svs} shows an exemplar shape representation of the human ear using SVS.
+As it can be observed, the final result does not drastically depend on the original number of annotated landmarks.
 
@@
 This is useful when annotating different structures of the same object, such as the curve of the left eyebrow and the curve of the right eyebrow on faces.
-Even though not absolutely necessary in our framework, it can provide further guidance on the estimation of dense shape correspondences.
+Even though not absolutely necessary in our framework, it can provide further guidance on the estimation of dense shape correspondences for various object classes.
 In more detail, we create a multi-channel SVS image $\bm{d}(\bm{x})=[d_1(\bm{x}) \cdots d_i(\bm{x}) \cdots d_{N_c}(\bm{x})]$, where $d_i(\bm{x})$ is the SVS image that corresponds to the curve annotation of the $i$-th structure and $N_c$ is the total number of structures (a single curve annotation is the special case where $N_c=1$).
 Note that we do not necessarily require that all structures are annotated in all the object images: in the case that a structure is not annotated, the corresponding channel of the SVS image simply takes a zero value for all pixels.
-The shape flow estimation can deal with such missing information thanks to the spatial regularisation and the low-rank constraint that it adopts, c.f.~Section \ref{sec:shapeflow}.
+The shape flow estimation can deal with such missing information thanks to the spatial regularisation and the low-rank constraint that it adopts, c.f.~Step~\ref{sec:step3}.
 
@@
 
-\subsection{Correspondence Basis for Shape Flow Estimation}
+%\subsection{Correspondence Basis for Shape Flow Estimation}
+{\refstepcounter{steps}\label{sec:step2}\subsection*{Step 2: Correspondence Basis for Shape Flow Estimation}}
 
@@
 
-\subsection{Shape Flow Estimation}
-\label{sec:shapeflow}
+{\refstepcounter{steps}\label{sec:step3}\subsection*{Step 3: Shape Flow Estimation}}
+% \subsection{Shape Flow Estimation}
+% \label{sec:step3}
 
@@
 % \end{figure}
-
-\begin{figure}[t!]
-    \centering
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_1}
-    \end{subfigure}
-  	\hfill
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_3}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_4}
-    \end{subfigure}
-  	\hfill
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.05\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/image_6}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[width=\textwidth]{resources/Fig_Variance/variances}
-    \end{subfigure}
-    \caption{Variance.}
-    \label{fig:variance}
-\end{figure}
 
@@
 
-\subsection{Dense Active Appearance Models}
+{\refstepcounter{steps}\label{sec:step4}\subsection*{Step 4: Dense and Part-Based Active Appearance Models}}
+% \subsection{Dense and Part-Based Active Appearance Models}
 
-The deformation fields obtained from section \ref{sec:shapeflow} can be effectively used to learn a naturally dense version of Active Appearance Models \cite{Cootes2001, Matthews2004}.
-Because all deformation fields contain the same number of pixels (the same as on the reference frame) the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation field themselves as dense annotations of the object's shape.
-Consequently, building a dense shape model reduces to normalizing these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying Principal Component Analysis (PCA).
-The resulting shape model can be mathematically expressed as:
+The deformation fields obtained from Step~\ref{sec:step3} can be used to naturally build two different kinds of effective AAMs \cite{Cootes2001, Matthews2004}: \emph{dense} \cite{ramnath2008increasing, Amberg2009, anderson2014using} and \emph{part-based} \cite{Tzimiropoulos2014}.
+The only difference between these two AAM formulations is on the way that the shape is represented and, thus, the manner in which the texture is sampled.
+Each one of them is suitable for object classes with specific properties.
+The dense AAM provides an exceptionally effective modeling and fitting for non-articulated objects, such as ears and faces, whose appearance has characteristic structures that spread all over their region (even if these structures cannot be consistently annotated).
+On the other hand, there exist other challenging object classes, such as arms and legs, that not only cannot be consistently annotated with landmarks, but their appearance is distinctive only on the object's outline and not in its interior region.
+Especially in the case of human body parts, they are almost always covered by clothes, which makes it impossible to construct robust texture models.
+
+\paragraph{Dense Active Appearance Model} Since all the deformation fields acquired by Step~\ref{sec:step3} contain the same number of pixels, which are the same as in the reference frame, the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation fields as dense annotations of the object's shape.
+Consequently, building a dense shape model reduces to normalising these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying PCA.
+A shape instance can be generated by the resulting shape model as:
 \begin{equation}
-    \begin{aligned}
-        \bm{s} & = \bm{\bar{s}} + \bm{S} \bm{p}
-    \end{aligned}
+    \bm{s}(\bm{p}) = \bm{\bar{s}} + \bm{S} \bm{p}
     \label{eq:shape_model}
 \end{equation}
-where $\bm{\bar{s}}$ is mean shape and $\bm{S}$ and $\bm{p}$ are the shape bases and shape parameters respectively.
+where $\bm{\bar{s}}$ is mean shape, and $\bm{S}$ and $\bm{p}$ are the shape bases and shape parameters, respectively.
 
-On the other hand, the texture model associated to the previous set of densified shapes can be easily obtained by warping all image onto the reference frame, making explicit use of the one-to-one correspondence between pixels on the reference frame and on the deformation fields.
-Once the images have been warped, the texture model is obtained by applying PCA on the warped images.
-The texture model is mathematically defined by the following expression:
+By making explicit use of the one-to-one correspondence between pixels on the reference frame and on the deformation fields, the motion model of sparse holistic AAMs \cite{Cootes2001, Matthews2004} (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is replaced by sampling all pixel values onto the reference frame.
+Let us define this sampling function, given a shape instance $\bm{s}(\bm{p})$, as $\mathcal{W}(\bm{s}(\bm{p}))$.
+Once the images have been warped, the texture model is obtained by applying PCA on them.
+A texture instance can be generated as:
 \begin{equation}
-    \begin{aligned}
-        \bm{t} = \bm{\bar{t}} + \bm{T} \bm{c}
-    \end{aligned}
+    \bm{t}(\bm{c}) = \bm{\bar{t}} + \bm{T} \bm{c}
 	\label{eq:tex_model}
 \end{equation}
-where $\bm{t}$ is the mean texture, and $\bm{T}$ and $\bm{c}$ are the texture bases and texture parameters respectively.
+where $\bm{t}$ is the mean texture, and $\bm{T}$ and $\bm{c}$ are the texture bases and texture parameters, respectively.
 
-Note that, both shape and texture models are directly related through the established one-to-one correspondence between dense landmarks and pixels on the reference frame.
-Therefore, in clear contrast to classic AAMs formulations \cite{Cootes2001, Matthews2004}, in our dense formulation no motion model (piece-wise affine, thin-plates splines \cite{Bookstein1989}) is required to relate the previous shape and texture models .
-As noted in other works \cite{Amberg2009, Tzimiropoulos2014}, this has the advantage that all efficient compositional gradient descent algorithms for fitting AAMs \cite{Papandreou2008, Matthews2004, Amberg2009, Tzimiropoulos2013, Alabort2014} become exact under our formulation.
+Given a test image $\mathbf{I}$, the fitting process involves the minimisation of the following cost function:
+\begin{equation}
+    \arg\min_{\bm{p}, \bm{c}}\|\bm{I}(\mathcal{W}(\bm{s}(\bm{p}))) - \bm{t}(\bm{c})\|_2^2
+	\label{eq:aam_cost}
+\end{equation}
+This optimisation problem is typically solved using the inverse-compositional Gauss-Newton algorithm, for which different variations have been proposed \cite{Matthews2004, Papandreou2008, Amberg2009, Tzimiropoulos2013, Alabort2014}.
+Note that the existence of the sampling function $\mathcal{W}()$ instead of a non-linear warping function has the advantage that all existing efficient gradient descent algorithms become exact.
 
-This shape flow-based dense AAM formulation provides an exceptionally effective modeling and fitting for various objects, such as ears and faces, whose appearance has characteristic structures spread all over the object region (even if these structures cannot be consistently annotated).
-Therefore, what has been described so far completes our proposed approach in training and fitting deformable models of this type of objects.
-
-However, there exist other challenging object types, such as forearms, legs and full body, that not only cannot be consistently annotated with landmarks, but also whose appearance is informative almost entirely on the object outline and not in the interior object region.
-This is due to the hugely varying texture of these objects (e.g.~colors and patterns of clothes) that is typically totally unrelated to their shape.
-For these cases, we propose to add some additional steps on our methodology.
-More specifically, we propose to focus on the dense correspondences solely on the object outline, utilize them to automatically estimate highly-accurate object skeleton landmarks and then adopt a parts-based deformable modeling.
-These steps will be described in the next section.
-
-\subsection{Outline-based Deformable Modeling}
+\paragraph{Outline Part-Based Active Appearance Model}
+For
 

### 2015-11-05 contents/introduction.tex

--- 2015-11-05 contents/introduction.tex
@@
 
+\setlength{\tabcolsep}{1pt}        
 \begin{figure}[t!]
-    \centering
-    \begin{subfigure}[b]{0.105\textwidth}
-            \includegraphics[height=5.5cm]{resources/MotivativeAnnotation/MPII}
-            \caption{MPII}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.115\textwidth}
-            \includegraphics[height=5.5cm]{resources/MotivativeAnnotation/FashionPose}
-            \caption{Fashion}
-    \end{subfigure}
-  	\hfill
-    \begin{subfigure}[b]{0.22\textwidth}
-            \includegraphics[height=5.5cm]{resources/MotivativeAnnotation/FLIC}
-            \caption{FLIC}
-    \end{subfigure}
-    % \hfill
-    % \begin{subfigure}[b]{0.145\textwidth}
-    %         \includegraphics[height=4cm]{resources/MotivativeAnnotation/BBCPose}
-    %         \caption{BBC Pose}
-    % \end{subfigure}
-    \caption{Examples of inconsistent and inaccurate annotations of human pose among different datasets.
-\emph{Blue} dots denote the original annotations.
-The arrows and \emph{green} dots show the correct location at which the points should be.
-    %Original annotations are shown in blue dots while better annotations shown in green dots.
-    }
+        \begin{tabular}{ccc}
+        \includegraphics[height=.65\columnwidth]{resources/MotivativeAnnotation/MPII}
+        &
+        \includegraphics[height=.65\columnwidth]{resources/MotivativeAnnotation/FashionPose}
+        &
+        \includegraphics[trim=50 0 50 0,clip,height=.65\columnwidth]{resources/MotivativeAnnotation/FLIC}
+        \\
+        (a) MPII
+        &
+        (b) Fashion
+        &
+        (c) FLIC
+        \end{tabular}
+    \caption{Examples of inconsistent annotations of human pose among different datasets.
+\emph{Blue} markers denote the original annotations.
+The arrows and \emph{green} markers show the correct location at which the points should be annotated.}
     \label{fig:wrong_anno}
@@
 
-  \item We propose one of the first methodologies that construct SDMs from a set of training data with inconsistent annotations.
-We show that the proposed methodology, since it uses highly effective curve annotation, tremendously reduces manual work overload but maintains same performance level against state-of-the-art SDMs.
-We show that by sampling the dense shape of SDM very powerful part-based SDMs can
+  \item We propose one of the first, to the best of our knowledge, methodologies that constructs accurate SDMs from a set of training data with inconsistent annotations.
+We show that the proposed methodology tremendously reduces the manual workload thanks to the highly effective curve annotations.
 
-  \item We propose the first SDMs of the outline of human parts, such as human arms, which can be applied for both highly accurate body part segmentation and pose estimation, as well as for providing accurate annotations for body joints.
+  \item We illustrate the ability of the proposed method to generate consistent sparse landmark annotations for object classes which, by nature, make it impossible to be manually annotated in a consistent way.
+
+  \item We show that it is more advantageous to model the human body parts (e.g.
+arms) with a set of sparse landmarks on their outline, rather than on their skeleton joints.
+This is because the outline landmarks, which can be acquired by our method in a straightforward way, exhibit better consistency compared to the inevitable inconsistency of the joint landmarks.
+
+  \item We report state-of-the-art quantitative and qualitative results on the task of human body parts localisation by employing a part-based AAM trained on the outline landmarks that are sampled by the dense AAM.
+Our proposed model outperforms all current state-of-the-art techniques that are trained on skeleton joints
+
+  \item We show that the employed part-based AAM corrects the annotations that are currently provided for most major human body pose databases.
+Upon acceptance of the paper, we will make the corrected annotations publicly available.
 

### 2015-11-05 contents/implementation.tex

@@
 
-\noindent\textbf{Step 4:} Utilise the dense correspondences acquired by the optical flow in order to automatically generate dense and sparse (on the outline) landmark annotations and build a dense \cite{ramnath2008increasing, Amberg2009, anderson2014using} and part-based \cite{Tzimiropoulos2014} AAM, respectively.
+\noindent\textbf{Step 4:} Utilise the dense correspondences acquired by the optical flow in order to automatically generate dense and sparse (on the outline) landmark annotations and build a dense \cite{ramnath2008increasing, Amberg2009, anderson2014using} and patch-based \cite{Tzimiropoulos2014} AAM, respectively.
 
@@
 
-{\refstepcounter{steps}\label{sec:step4}\subsection*{Step 4: Dense and Part-Based Active Appearance Models}}
-% \subsection{Dense and Part-Based Active Appearance Models}
+{\refstepcounter{steps}\label{sec:step4}\subsection*{Step 4: Dense and Patch-Based Deformable Models}}
+% \subsection{Dense and Patch-Based Active Appearance Models}
 
-The deformation fields obtained from Step~\ref{sec:step3} can be used to naturally build two different kinds of effective AAMs \cite{Cootes2001, Matthews2004}: \emph{dense} \cite{ramnath2008increasing, Amberg2009, anderson2014using} and \emph{part-based} \cite{Tzimiropoulos2014}.
+The deformation fields obtained from Step~\ref{sec:step3} can be used to naturally build two different kinds of effective Active Appearance Models (AAMs) \cite{Cootes2001, Matthews2004}: \emph{dense} \cite{ramnath2008increasing, Amberg2009, anderson2014using} and \emph{patch-based} \cite{Tzimiropoulos2014}.
 The only difference between these two AAM formulations is on the way that the shape is represented and, thus, the manner in which the texture is sampled.
@@
 
-\paragraph{Outline Part-Based Active Appearance Model}
-For
+\paragraph{Outline Patch-Based Active Appearance Model}
+The object classes for which the interior appearance does not have specific structure are modeled using patch-based AAMs \cite{Tzimiropoulos2014} trained on a set of sparse landmarks.
+Especially for human body parts (arms, legs), we strongly believe that the points located to the outline of the object are more suitable compared to the internal ones that correspond to the skeleton joints, which are commonly used by current literature \cite{buehler2011upper,charles2013domain,pfister2015flowing,yang2013articulated}.
 
-As already mentioned, for estimating body pose and modeling other object types with similar challenges, we propose to only consider the established correspondences on the object outline.
-
-Based on the proposed shape flow framework, we develop a methodology for robust automatic landmarking of the object outline.
-This allows a small initial training set that is manually annotated without consistent landmarks to be expanded to a much larger training set in an automatic way.
-In more detail, regarding the manually annotated images, for which SVS functions have been constructed, the outline correspondences are yielded by evaluating the estimated shape flow on the object outline of the reference image.
-To expand the training set to images without any annotations, we fit the trained dense AAM on these images and then only consider the deformed positions of the dense landmarks that correspond to the object outline on the mean shape.
-
-Having reliable object outline annotations on a large training set, we appropriately fuse their information to infer consistent landmarks on the object skeleton.
-This procedure equips deformable model training with consistent landmark annotations.
-This is particularly valuable, since it automates the training process and overcomes the limitations of inconsistent and inaccurate manual annotations on challenging objects such as forearms and legs.
-
-Based on these skeleton landmarks, we then train an parts-based deformable model. More specifically, ...
+The main differences between the patch-based and dense AAMs are that (a)~the densified shape instances are sub-sampled to include only the outline points, and (b)~the texture representation involves the sampling a neighbourhood around each point instead of a single pixel.
+Specifically, in order to build the outline sparse shape model, we simply select the outline points on the SVS reference frame.
+Then, by taking advantage of the dense correspondences obtained by Step \ref{sec:step3}, the shape model is trained in a similar way as in the dense case.
+Moreover, similar to the dense case, the texture model is built by sampling the image values from the sparse shape locations, i.e.
+$\mathcal{W}(\bm{s}(\bm{p}))$.
+However, contrary to dense AAMs, we sample a patch that is centred around each landmark point.
+These patches are then vectorised and concatenated in a single texture vector.
+Note that the optimisation process remains exactly the same.

### 2015-11-05 contents/introduction.tex

@@
 In particular, in order to build dense correspondences between different shape instances of the same object class, we jointly estimate the optical flow among all the instances by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.
-Multiframe optical flow has originally been applied on video sequences, relying on the assumptions of color consistency and motion smoothness \cite{Garg:2013hu}.
+Multiframe optical flow has originally been applied on video sequences, relying on the assumptions of colour consistency and motion smoothness \cite{Garg:2013hu}.
 However, these assumptions do not hold in our case, where we have a collection of shapes.
@@
 
-In addition, we demonstrate how dense Active Appearance Models (AAMs) can be built after establishing dense shape correspondences.
-We show that the proposed methodology can be applied on landmark localisation, even though it is not tailored for that task, achieving particularly good performance.
-We also illustrate the performance of the proposed methodology for describing objects that do not have consistent landmarks.
-Furthermore, we show how to build a powerful part-based AAM on the sparse outline landmarks that are obtained by sampling the shape of the dense AAM.
-Using the resulting outline part-based AAM, we report state-of-the-art performance on the task of human body parts localisation on challenging databases.
-Finally, we show that the proposed part-based AAM can be used to provide consistent annotations for different body parts.
+Additionally, we show that the proposed methodology can be applied on landmark localisation, even though it is not tailored for that task, achieving particularly good performance.
+Specifically, we explain how to build powerful dense SDMs that are suitable for objects that have rich interior texture but lack landmarks consistency.
+Furthermore, we show how to build a powerful patch-based SDMs on the sparse outline landmarks of objects that do not have semantically meaningful interior textures.
+Using the resulting outline patch-based SDM, we report state-of-the-art performance on the task of human body parts localisation on challenging databases.
+Finally, we show that the proposed patch-based SDM can be used to provide consistent annotations for different body parts.
 
@@
 
-  \item We report state-of-the-art quantitative and qualitative results on the task of human body parts localisation by employing a part-based AAM trained on the outline landmarks that are sampled by the dense AAM.
+  \item We report state-of-the-art quantitative and qualitative results on the task of human body parts localisation by employing a patch-based SDM trained on the outline landmarks that are sampled by the dense correspondences.
 Our proposed model outperforms all current state-of-the-art techniques that are trained on skeleton joints
 
-  \item We show that the employed part-based AAM corrects the annotations that are currently provided for most major human body pose databases.
+  \item We show that the employed patch-based SDM corrects the annotations that are currently provided for most major human body pose databases.
 Upon acceptance of the paper, we will make the corrected annotations publicly available.

### 2015-11-05 contents/evaluation.tex
Updates from ShareLaTeX

--- 2015-11-05 contents/evaluation.tex
@@
 
+\begin{figure}[t!]
+    \centering
+    % \begin{subfigure}[b]{0.05\textwidth}
+    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
+    % \end{subfigure}
+    % \hfill
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_1}
+    \end{subfigure}
+  	\hfill
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_2}
+    \end{subfigure}
+    \hfill
+    % \begin{subfigure}[b]{0.07\textwidth}
+    %         \includegraphics[height=4.8cm]{resources/Fig_Variance/image_3}
+    % \end{subfigure}
+    % \hfill
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_4}
+    \end{subfigure}
+  	\hfill
+    % \begin{subfigure}[b]{0.05\textwidth}
+    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
+    % \end{subfigure}
+    % \hfill
+    \begin{subfigure}[b]{0.08\textwidth}
+            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_6}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.125\textwidth}
+            \includegraphics[height=5.5cm]{resources/Fig_Variance/variances}
+    \end{subfigure}
+    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
+    \label{fig:variance}
+\end{figure}
+
 The training of dense Active Appearance Models (dAAMs) for upper body involves manual outline annotation from a combination of datasets, including H3D\cite{PoseletsICCV09}, Microsoft COCO\cite{lin2014microsoft}, MPII\cite{andriluka14cvpr}, Fashion Pose\cite{dantone2013human}, FLIC\cite{sapp2013modec} and BBC Poses\cite{pfister2015flowing}.
@@
 
-\subsection{Benchmark Against State-of-the-art}
+\subsection{Arm Pose Estimation}
 \label{exp:benchmark}
@@
 In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
+Detailed statistical results please refer to supplementary material.
 
@@
 
-\begin{table}[b!]
-    \small
-    \centering
-    \begin{tabular}{|l|c|c|c||c|c|c|}
-        \hline
-                            & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
-        \hline
-        \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
-        \hline\hline
-        Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
-        Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
-        Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
-        Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
-        Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
-        Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
-        \hline\hline
-        Ours                & \textbf{6.791}& \textbf{10.910}   & \textbf{63.1\%}       & \textbf{8.250}     &  \textbf{10.564}        & 52.1\%\\
-        \hline
-    \end{tabular}
-    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
-    \label{tab:hand_benchmark}
-\end{table}
+% \begin{table}[b!]
+%     \small
+%     \centering
+%     \begin{tabular}{|l|c|c|c||c|c|c|}
+%         \hline
+%                             & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
+%         \hline
+%         \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
+%         \hline\hline
+%         Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
+%         Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
+%         Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
+%         Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
+%         Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
+%         Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
+%         \hline\hline
+%         Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
+%         \hline
+%     \end{tabular}
+%     \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
+%     \label{tab:hand_benchmark}
+% \end{table}
 
-\subsection{Internal Evaluation}
+\subsection{Non-rigid Object Alignment In-the-wild}
 \label{exp:internal}
 
-\begin{figure}[t!]
-    \centering
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow_joints}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist_joints}
-    \end{subfigure}
-    \caption{Hand Benchmark.}
-    \label{fig:internal_benchmark}
-\end{figure}
-
-\subsection{Qualitative Results}
+\subsection{Annotation Correct}
 \label{exp:qualitative}

### 2015-11-06 contents/evaluation.tex

@@
 
-Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are reported in Table \ref{tab:hand_benchmark}.
+Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are shown in supplementary material.
 Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms.
 In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
-Detailed statistical results please refer to supplementary material.
 
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/HandBenchmark/wrist}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/HandBenchmark/elbow}
-    \end{subfigure}
+    \includegraphics[width=\columnwidth]{resources/HandBenchmark/wrist}
+    \\
+    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/wrist}
+    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
     \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
@@
 \label{exp:internal}
+\begin{figure}[b!]
+    \centering
+    \begin{subfigure}[b]{0.23\textwidth}
+            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/face}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.23\textwidth}
+            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/ear}
+    \end{subfigure}
+    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
+    \label{fig:daam_benchmark}
+\end{figure}
 
-\subsection{Annotation Correct}
+This experiment compares the fitting accuracy of our dAAMs versus the one of classic AAM on the problem of nonrigid face and ear alignment in-the-wild.
+
+For face experiment, both models were built using the 811 training images of the Labelled
+Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
+Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
+Our dAAMs were built as the pipeline proposed.
+Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations.
+For this experiment, we report results using pixels intensities (INT) for both models.
+
+For ear experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear.
+To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper.
+Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
+We randomly split the previous database into two disjoint sets of training (500) and testing (105) images.
+Both models were built using the 500 images training set and their fitting accuracy evaluated on the 105 images of the testing set.
+Note here that we used the same procedures to build the models as for faces and same error metric for evaluation.
+
+CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
+We can readily observe that the accuracy achieved by ear models, in terms of the previous normalized point-to-point error measure, is lower than the one achieved by face models.
+This result is expected due to the more complex structure of the ear shape.
+Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
+Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.
+In fact, classic AAM fail to improve the accuracy of the original initialisation on ears.
+Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
+
+\subsection{Annotation Correction}
 \label{exp:qualitative}

### 2015-11-06 contents/evaluation.tex

@@
 
-The training of dense Active Appearance Models (dAAMs) for upper body involves manual outline annotation from a combination of datasets, including H3D\cite{PoseletsICCV09}, Microsoft COCO\cite{lin2014microsoft}, MPII\cite{andriluka14cvpr}, Fashion Pose\cite{dantone2013human}, FLIC\cite{sapp2013modec} and BBC Poses\cite{pfister2015flowing}.
+The training of dense Active Appearance Models (dAAMs) for upper body involves manual outline annotation from a combination of datasets, including H3D \cite{PoseletsICCV09}, Microsoft COCO \cite{lin2014microsoft}, MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
 The training set contains 891 training images from where 500 are annotated with outline manually.
@@
 \label{exp:benchmark}
-This experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting.
-We build Patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
-Dense Scale-Invariant Feature Transform (SIFT)\cite{PoseletsICCV09} feature is used from image representation for our model.
+Two experiments are undertaken in this section: 1) presenting training classic patch AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch AAM from joint annotation .
+
+First experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting.
+We build patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
+SIFT \cite{PoseletsICCV09} feature is used from image representation for our model.
 Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset.
@@
 
-Cumulative Error Distributions (CED) for this experiment are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are shown in supplementary material.
-Results show that, for this experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms.
+Second experiment investigates the disadvantages of using skeleton annotation.
+We build patch AAM on joints with same training data and with SIFT representation.
+Both models are fine-tuned on BBC Pose validation set.
+The fitting procedure is performed under exactly same condition, e.g.
+same testing set and initialisation position.
+
+CED Curves for both experiments are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are shown in supplementary material.
+Results show that, for first experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms.
 In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
+While for second experiment, patch AAM trained with outline significantly outperforms path AAM trained with joints as we expected.
+Note that path AMM trained with Joints still comparable even marginally better than recent algorithms.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{resources/HandBenchmark/wrist}
+    \includegraphics[width=\columnwidth]{resources/HandBenchmark/legend}
     \\
@@
 \subsection{Non-rigid Object Alignment In-the-wild}
-\label{exp:internal}
+\label{exp:daam_benchmark}
 \begin{figure}[b!]
@@
     \end{subfigure}
-    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
+    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:daam_benchmark}}
     \label{fig:daam_benchmark}

### 2015-11-06 contents/evaluation.tex
Backup
exp 4.4

@@
 \label{exp:benchmark}
+
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=\columnwidth]{resources/HandBenchmark/legend}
+    \\
+    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/wrist}
+    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
+    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
+    \label{fig:hand_benchmark}
+\end{figure}
+
 Two experiments are undertaken in this section: 1) presenting training classic patch AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch AAM from joint annotation .
@@
 Note that path AMM trained with Joints still comparable even marginally better than recent algorithms.
-
-\begin{figure}[b!]
-    \centering
-    \includegraphics[width=\columnwidth]{resources/HandBenchmark/legend}
-    \\
-    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/wrist}
-    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
-    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
-    \label{fig:hand_benchmark}
-\end{figure}
 
@@
 \label{exp:daam_benchmark}
+
 \begin{figure}[b!]
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/face}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.23\textwidth}
-            \includegraphics[width=\textwidth]{resources/DAAMBenchmark/ear}
-    \end{subfigure}
-    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:daam_benchmark}}
+    \includegraphics[width=0.25\columnwidth]{resources/DAAMBenchmark/legend}
+    \\
+    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/face}
+    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
+    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
     \label{fig:daam_benchmark}
@@
 \label{exp:qualitative}
+
+\begin{figure*}[t!]
+    \centering
+    \includegraphics[height=\fh]{resources/Fixing/fix_3}
+    \includegraphics[height=\fh]{resources/Fixing/fix_5}
+    \includegraphics[height=\fh]{resources/Fixing/fix_6}
+    \includegraphics[height=\fh]{resources/Fixing/fix_7}
+    \includegraphics[height=\fh]{resources/Fixing/fix_8}
+    \includegraphics[height=\fh]{resources/Fixing/fix_9}
+    \includegraphics[height=\fh]{resources/Fixing/fix_10}
+    \includegraphics[height=\fh]{resources/Fixing/fix_12}
+    \includegraphics[height=\fh]{resources/Fixing/fix_13}
+    \includegraphics[height=\fh]{resources/Fixing/fix_14}
+    \includegraphics[height=\fh]{resources/Fixing/fix_15}
+    \includegraphics[height=\fh]{resources/Fixing/fix_17}
+    \includegraphics[height=\fh]{resources/Fixing/fix_18}
+    \includegraphics[height=\fh]{resources/Fixing/fix_19}
+    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}}
+    \label{fig:qualitative}
+\end{figure*}

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

@@
     \centering
-    \includegraphics[width=0.25\columnwidth]{resources/DAAMBenchmark/legend}
+    \includegraphics[width=0.6\columnwidth]{resources/DAAMBenchmark/legend}
     \\
@@
 
+This experiment demonstrates inconsistency of joints annotation among MPII, Fashion Pose and FLIC, as well as investigate the inevitable variance of manual annotation.
+Three well trained annotators are used to annotate left arm using 120 test images from Fashion Pose dataset.
+Figure \ref{fig:variance} presents statistical results calculated using data annotated and officially provided with normalisation based on length of arms.
+Exemplar annotation visualisation also shows significant inconsistency of manual annotation on joints.
+
+Figure \ref{exp:qualitative} presents corrections of joint annotations using patch-based SDM trained as experiment \ref{exp:benchmark}.
+\textbf{Red dots} shows ``ground truth" points while \textbf{green dots} shows landmarks after correction using our methodology.
+There is no doubt that points after correction show more consistency among images.
+Images are croped to hand only for better visualisation.
+
 \begin{figure*}[t!]
+    \newcommand{\fh}{0.24\columnwidth}
     \centering
@@
 \end{figure*}
+
+\begin{figure*}[t!]
+    \newcommand{\ofh}{0.24\columnwidth}
+    \centering
+    \includegraphics[height=\ofh]{resources/Fixing/fix_3}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_5}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_6}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_7}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_8}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_9}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_10}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_12}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_13}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_14}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_15}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_17}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_18}
+    \includegraphics[height=\ofh]{resources/Fixing/fix_19}
+    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}}
+    \label{fig:outline_fitting}
+\end{figure*}

### 2015-11-06 contents/evaluation.tex
Temp Save

@@
     \centering
-    % \begin{subfigure}[b]{0.05\textwidth}
-    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_0}
-    % \end{subfigure}
-    % \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_1}
-    \end{subfigure}
-  	\hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_2}
-    \end{subfigure}
-    \hfill
-    % \begin{subfigure}[b]{0.07\textwidth}
-    %         \includegraphics[height=4.8cm]{resources/Fig_Variance/image_3}
-    % \end{subfigure}
-    % \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_4}
-    \end{subfigure}
-  	\hfill
-    % \begin{subfigure}[b]{0.05\textwidth}
-    %         \includegraphics[width=\textwidth]{resources/Fig_Variance/image_5}
-    % \end{subfigure}
-    % \hfill
-    \begin{subfigure}[b]{0.08\textwidth}
-            \includegraphics[height=5.5cm]{resources/Fig_Variance/image_6}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.125\textwidth}
-            \includegraphics[height=5.5cm]{resources/Fig_Variance/variances}
-    \end{subfigure}
+    \newcommand{\vfh}{4cm}
+    \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
+    \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
+    \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
+    \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
+    \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
     \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
@@
     \centering
-    \includegraphics[height=\ofh]{resources/Fixing/fix_3}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_5}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_6}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_7}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_8}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_9}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_10}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_12}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_13}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_14}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_15}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_17}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_18}
-    \includegraphics[height=\ofh]{resources/Fixing/fix_19}
-    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}}
+    \includegraphics[height=\ofh]{resources/Fittings/1.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/3.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/4.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/6.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/7.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/8.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/13.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/15.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/17.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/19.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/21.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/23.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/25.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/27.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/29.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/31.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/33.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/35.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/36.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/37.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/38.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/39.eps}
+    \caption{Demonstration of outline fitting of patch AAM}
     \label{fig:outline_fitting}

### 2015-11-06 contents/title.tex
Updates from ShareLaTeX
git ignore added, annotation figure added

@@
-\title{Human Body Outline Annotation}
+\title{Estimating Correspondences of Deformable Objects ``In-the-wild"}
 
-\author{Author\\
+\author{Yuxiang Zhou, Epameinondas Antonakos, Anastasios Roussos, Stefanos Zafeiriou\\
 Imperial College London\\
 180 Queen’s Gate, SW7 2AZ, London, U.K.\\
-{\tt\small \{email\}@imperial.ac.uk}}
+{\tt\small \{yuxiang.zhou10, e.antonakos, troussos, s.zafeiriou\}@imperial.ac.uk}}
 % For a paper whose authors are all at the same institution,

### 2015-11-06 contents/implementation.tex
Updates from ShareLaTeX

@@
 where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel.
-The decision function $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret is as an image and we call it \emph{SVS image}.
+The decision function $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret it as an image and we call it \emph{SVS image}.
 
@@
 
-\subsubsection{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
+\subsubsection*{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
 
@@
 
-\subsubsection{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
+\subsubsection*{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
 \label{varshapeflow}
@@
 Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method.
-These results correspond to exemplar training shapes in the case of a face dataset.
+These results correspond to exemplar training shapes in the case of an arm dataset.
 
@@
 
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=0.45\textwidth]{resources/models}
+    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
+    \label{fig:dense_models}
+\end{figure}
+
 The deformation fields obtained from Step~\ref{sec:step3} can be used to naturally build two different kinds of effective Active Appearance Models (AAMs) \cite{Cootes2001, Matthews2004}: \emph{dense} \cite{ramnath2008increasing, Amberg2009, anderson2014using} and \emph{patch-based} \cite{Tzimiropoulos2014}.

### 2015-11-06 contents/evaluation.tex

@@
 Results for quantitative an qualitative experiments are reported.
-Experiments \ref{exp:internal} investigate the accuracy of estimating dense correspondences of non-rigid deformable objects, and the impact of annotating outlines of human poses instead of annotating skeletons.
+Experiments \ref{exp:daam_benchmark} show performance of fitting dense SDMs built to non-rigid objects having rich interior textures e.g.
+faces and ears.
 Experiments \ref{exp:benchmark} compare the joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild.
-Note that all results reported in this section were obtained by fitting Patch AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
+In addition, this experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons.
+Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
 For further experimental results and visualisations please refer to our supplementary material.
-
-\subsection{Databases \& Error Metrics}
-There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
-In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
 
@@
     \centering
-    \newcommand{\vfh}{4cm}
-    \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
-    \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
-    \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
-    \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
-    \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
+    \includegraphics[width=\columnwidth]{resources/Fig_Variance/final}
+    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
+    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
+    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
+    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
+    % \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
     \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
@@
 
-The training of dense Active Appearance Models (dAAMs) for upper body involves manual outline annotation from a combination of datasets, including H3D \cite{PoseletsICCV09}, Microsoft COCO \cite{lin2014microsoft}, MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
+\subsection{Non-rigid Object Alignment In-the-wild}
+\label{exp:daam_benchmark}
+
+This experiment compares the fitting accuracy of our dense Active Appearance Models (dAAMs) versus the one of classic AAM on the problem of nonrigid face and ear alignment in-the-wild.
+
+\subsubsection{Databases \& Error Metrics}
+For face experiment, both models were built using the 811 training images of the Labelled
+Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
+Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
+Our dAAMs were built as the pipeline proposed.
+Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations.
+For this experiment, we report results using pixels intensities (INT) for both models.
+
+For ear experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear.
+To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper.
+Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
+We randomly split the previous database into two disjoint sets of training (500) and testing (105) images.
+Both models were built using the 500 images training set and their fitting accuracy evaluated on the 105 images of the testing set.
+Note here that we used the same procedures to build the models as for faces and same error metric for evaluation.
+
+\subsubsection{Experiments}
+
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=0.6\columnwidth]{resources/DAAMBenchmark/legend}
+    \\
+    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/face}
+    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
+    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
+    \label{fig:daam_benchmark}
+\end{figure}
+
+CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
+We can readily observe that the accuracy achieved by ear models, in terms of the previous normalized point-to-point error measure, is lower than the one achieved by face models.
+This result is expected due to the more complex structure of the ear shape.
+Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
+Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.
+In fact, classic AAM fail to improve the accuracy of the original initialisation on ears.
+Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
+
+\subsection{Arm Pose Estimation}
+\label{exp:benchmark}
+This section provides experiments showing that training patch-based AAM from outline annotation provides remarkable joints estimation.
+
+\subsubsection{Dataset \& Error Metric}
+There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
+In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
+
+The training of patch-based AAM for arms involves manual outline annotation from a combination of datasets, including H3D \cite{PoseletsICCV09}, Microsoft COCO \cite{lin2014microsoft}, MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
 The training set contains 891 training images from where 500 are annotated with outline manually.
 A dAAMs is built from 500 training images thereby produces dense correspondences for generating sparse outline annotation (29 landmarks).
-A Patch AAM is build from sparse annotations before fitting to 391 images.
+A patch-based AAM is build from sparse annotations before fitting to 391 images.
 Manual minor correction are required for putting those fitted image to training set.
-The final Patch AAM is built from 891 images and validated on validation set given by BBC Pose.
+The final patch-based AAM is built from 891 images and validated on validation set given by BBC Pose.
 
@@
 
-\subsection{Arm Pose Estimation}
-\label{exp:benchmark}
+\subsubsection{Experiments}
 
@@
 
-Two experiments are undertaken in this section: 1) presenting training classic patch AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch AAM from joint annotation .
+Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
 
 First experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting.
-We build patch AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
+We build patch-based AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
 SIFT \cite{PoseletsICCV09} feature is used from image representation for our model.
@@
 Second experiment investigates the disadvantages of using skeleton annotation.
-We build patch AAM on joints with same training data and with SIFT representation.
+We build patch-based AAM on joints with same training data and with SIFT representation.
 Both models are fine-tuned on BBC Pose validation set.
@@
 In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
-While for second experiment, patch AAM trained with outline significantly outperforms path AAM trained with joints as we expected.
+While for second experiment, patch-based AAM trained with outline significantly outperforms path AAM trained with joints as we expected.
 Note that path AMM trained with Joints still comparable even marginally better than recent algorithms.
@@
 
-\subsection{Non-rigid Object Alignment In-the-wild}
-\label{exp:daam_benchmark}
-
-\begin{figure}[b!]
-    \centering
-    \includegraphics[width=0.6\columnwidth]{resources/DAAMBenchmark/legend}
-    \\
-    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/face}
-    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
-    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
-    \label{fig:daam_benchmark}
-\end{figure}
-
-This experiment compares the fitting accuracy of our dAAMs versus the one of classic AAM on the problem of nonrigid face and ear alignment in-the-wild.
-
-For face experiment, both models were built using the 811 training images of the Labelled
-Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
-Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
-Our dAAMs were built as the pipeline proposed.
-Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations.
-For this experiment, we report results using pixels intensities (INT) for both models.
-
-For ear experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear.
-To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper.
-Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
-We randomly split the previous database into two disjoint sets of training (500) and testing (105) images.
-Both models were built using the 500 images training set and their fitting accuracy evaluated on the 105 images of the testing set.
-Note here that we used the same procedures to build the models as for faces and same error metric for evaluation.
-
-CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
-We can readily observe that the accuracy achieved by ear models, in terms of the previous normalized point-to-point error measure, is lower than the one achieved by face models.
-This result is expected due to the more complex structure of the ear shape.
-Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
-Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.
-In fact, classic AAM fail to improve the accuracy of the original initialisation on ears.
-Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
-
-\subsection{Annotation Correction}
-\label{exp:qualitative}
-
-This experiment demonstrates inconsistency of joints annotation among MPII, Fashion Pose and FLIC, as well as investigate the inevitable variance of manual annotation.
-Three well trained annotators are used to annotate left arm using 120 test images from Fashion Pose dataset.
-Figure \ref{fig:variance} presents statistical results calculated using data annotated and officially provided with normalisation based on length of arms.
-Exemplar annotation visualisation also shows significant inconsistency of manual annotation on joints.
-
-Figure \ref{exp:qualitative} presents corrections of joint annotations using patch-based SDM trained as experiment \ref{exp:benchmark}.
-\textbf{Red dots} shows ``ground truth" points while \textbf{green dots} shows landmarks after correction using our methodology.
-There is no doubt that points after correction show more consistency among images.
-Images are croped to hand only for better visualisation.
-
-\begin{figure*}[t!]
+\begin{figure*}[!t]
     \newcommand{\fh}{0.24\columnwidth}
@@
     \includegraphics[height=\fh]{resources/Fixing/fix_19}
-    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}}
+    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}.
+\emph{Red} dots refer to officially provided landmarks, and \emph{green} dots are corrected position.}
     \label{fig:qualitative}
@@
 
-\begin{figure*}[t!]
+\begin{figure*}[!t]
     \newcommand{\ofh}{0.24\columnwidth}
@@
     \includegraphics[height=\ofh]{resources/Fittings/3.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/19.eps}
     \includegraphics[height=\ofh]{resources/Fittings/4.eps}
     \includegraphics[height=\ofh]{resources/Fittings/6.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/15.eps}
     \includegraphics[height=\ofh]{resources/Fittings/7.eps}
@@
     \includegraphics[height=\ofh]{resources/Fittings/13.eps}
-    \includegraphics[height=\ofh]{resources/Fittings/15.eps}
     \includegraphics[height=\ofh]{resources/Fittings/17.eps}
-    \includegraphics[height=\ofh]{resources/Fittings/19.eps}
+    \\
     \includegraphics[height=\ofh]{resources/Fittings/21.eps}
@@
     \includegraphics[height=\ofh]{resources/Fittings/39.eps}
-    \caption{Demonstration of outline fitting of patch AAM}
+    \caption{Demonstration of outline fitting of patch-based AAM on arms.}
     \label{fig:outline_fitting}
 \end{figure*}
+
+\subsection{Annotation Correction}
+\label{exp:qualitative}
+
+This experiment demonstrates inconsistency of joints annotation among MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human} and FLIC \cite{sapp2013modec}, as well as investigate the inevitable variance of manual annotation.
+Three well trained annotators are used to annotate left arm using 120 test images from Fashion Pose \cite{dantone2013human} dataset.
+Figure \ref{fig:variance} presents statistical results calculated using data annotated and officially provided with normalisation based on length of arms.
+Exemplar annotation visualisation also shows significant inconsistency of manual annotation on joints.
+
+Figure \ref{exp:qualitative} presents corrections of joint annotations using patch-based SDM trained as experiment \ref{exp:benchmark}.
+\emph{Red} dots shows ``ground truth" points while \emph{green} dots shows landmarks after correction using our methodology.
+There is no doubt that points after correction show more consistency among images.
+Images are croped to hand only for better visualisation.

### 2015-11-06 contents/implementation.tex

@@
 
-\begin{figure}[b!]
-    \centering
-    \includegraphics[width=0.4\textwidth]{resources/svs2}
-    \caption{Exemplar SVS shape representation. A similar SVS image is obtained from different annotations of the same shape.}
-    \label{fig:build_svs}
-\end{figure}
+% \begin{figure}[b!]
+%     \centering
+%     \includegraphics[width=0.4\textwidth]{resources/svs2}
+%     \caption{Exemplar SVS shape representation. A similar SVS image is obtained from different annotations of the same shape.}
+%     \label{fig:build_svs}
+% \end{figure}
 
@@
     \centering
-        \begin{tabular}{ccc}
-        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/1}
-        &
-        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/2}
-        &
-        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/3}
-        \\
-        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/4}
-        &
-        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/5}
-        &
-        \includegraphics[trim=200 150 200 50,clip,width=.25\columnwidth]{resources/Fig_Flows/6}
-        \end{tabular}
+    \newcommand{\flowh}{0.25\columnwidth}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/1}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/2}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/3}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/4}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/5}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/6}
     \caption{Exemplar deformation fields for the left forearm, obtained using the proposed pipeline. Figure best viewed by zooming in.}

### 2015-11-06 contents/evaluation.tex
Save

@@
 
-\subsubsection{Databases \& Error Metrics}
+\textbf{Databases \& Error Metrics}
 For face experiment, both models were built using the 811 training images of the Labelled
@@
 
-\subsubsection{Experiments}
-
 \begin{figure}[b!]
@@
 
+\textbf{Experiments}
 CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
-We can readily observe that the accuracy achieved by ear models, in terms of the previous normalized point-to-point error measure, is lower than the one achieved by face models.
+We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models.
 This result is expected due to the more complex structure of the ear shape.
@@
 
-\subsubsection{Dataset \& Error Metric}
+\textbf{Dataset \& Error Metric}
 There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
@@
 
+\textbf{Experiments} 
 Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
@@
 SIFT \cite{PoseletsICCV09} feature is used from image representation for our model.
-Model fitting is initialised based on current state-of-the-art human pose estimation algorithms on BBC Pose dataset.
+Model fitting is initialised based on current state-of-the-art human pose estimation algorithms (including Buehler \cite{buehler2011upper}, Charles14 \cite{charles2014upper}, Charles13 \cite{charles2013domain}, Pfister14 \cite{pfister2015deep}, Ramanan \cite{yang2013articulated} and Pfister15 \cite{pfister2015flowing}) on BBC Pose \cite{pfister2015flowing} dataset.
 Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton.
@@
     \centering
+    \includegraphics[height=\fh]{resources/Fixing/fix_1}
+    \includegraphics[height=\fh]{resources/Fixing/fix_2}
     \includegraphics[height=\fh]{resources/Fixing/fix_3}
@@
     \includegraphics[height=\fh]{resources/Fixing/fix_10}
+    \includegraphics[height=\fh]{resources/Fixing/fix_20}
     \includegraphics[height=\fh]{resources/Fixing/fix_12}
@@
     \includegraphics[height=\fh]{resources/Fixing/fix_18}
-    \includegraphics[height=\fh]{resources/Fixing/fix_19}
+    % \includegraphics[height=\fh]{resources/Fixing/fix_19}
     \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}.
@@
     \centering
-    \includegraphics[height=\ofh]{resources/Fittings/1.eps}
+    \includegraphics[height=\ofh]{resources/Fittings/20.eps}
     \includegraphics[height=\ofh]{resources/Fittings/3.eps}
@@
 There is no doubt that points after correction show more consistency among images.
-Images are croped to hand only for better visualisation.
+Images are cropped to hand only for better visualisation.

### 2015-11-06 contents/implementation.tex
Save

@@
 
-In order to fully capture the variability among most deformable objects' shapes annotations, we use a representation based on Support Vector Shapes (SVS) \cite{Nguyen2013}.
+In order to fully capture the variability among most deformable objects' shapes annotations, we use a representation based on SVS \cite{Nguyen2013}.
 An SVS is a decision function trained on shapes using Support Vector Machines (SVMs) with Radial Basis Function (RBF) kernels.
@@
 This is done because the goal here is to build a model capable of effectively representing non-rigid local shape deformations rather than global rotation, translation and scaling.
-The alignment is performed by using the Iterative Closest Point (ICP) algorithm \cite{Besl1992} on the annotated landmarks point cloud of the training images.
+The alignment is performed by using the ICP algorithm \cite{Besl1992} on the annotated landmarks point cloud of the training images.
 
@@
 To form this vector, the training images are arranged in an arbitrary order.
-Similarly to the order of training samples when Principal Component Analysis (PCA) is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
+Similarly to the order of training samples when PCA is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
 
@@
 To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
-Then, we apply Non-rigid Iterative Closest Point (NICP)\cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
+Then, we apply NICP \cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
 NICP iteratively deforms the cloud of points of every shape to match the points of the reference shape.

### 2015-11-06 contents/implementation.tex
Updates from ShareLaTeX
updates on describing steps, shortened a lot

@@
 
-\noindent\textbf{Step 4:} Utilise the dense correspondences acquired by the optical flow in order to automatically generate dense and sparse (on the outline) landmark annotations and build a dense \cite{ramnath2008increasing, Amberg2009, anderson2014using} and patch-based \cite{Tzimiropoulos2014} AAM, respectively.
+\noindent\textbf{Step 4:} Utilise the dense correspondences acquired by the optical flow in order to automatically generate either dense or sparse (on the outline) landmark annotations, depending on the object class type.
+Then, build either a dense \cite{ramnath2008increasing, Amberg2009, anderson2014using} or a patch-based \cite{Tzimiropoulos2014} AAM, respectively.
 
@@
 The curve annotations for all training images are densely sampled to yield a set of landmarks per image, with this set being different for every training image.
-To train the SVM, these landmarks are assigned as belonging to the class with label `+1', whereas randomly sampled points around them are assigned as belonging to the class with label `-1'.
-Since the class `+1' has far less points than the class `-1', landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of points of the class `+1' and `-1' respectively and $W_p, W_n$ are their corresponding weights.
+To train the SVM, these landmarks are assigned as belonging to the `positive' class, whereas randomly sampled points around them are assigned as belonging to the `negative' class.
+Since the positive class has far less points than the negative class, landmarks are assigned considerably larger weights so that $N_p \times W_p=N_n \times W_n$ where $N_p, N_n$ are number of points of the positive and negative class respectively and $W_p, W_n$ are their corresponding weights.
 
-SVMs with RBF kernel function map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on 2D space represents the actual shape of the object.
-Note that the decision function for SVMs can be mathematically expressed as:
-\begin{equation} \label{eq:decisionfunc}
-    d(\bm{x})=\sum_i\alpha_i \, k(\bm{x}_i^*,\bm{x})
-\end{equation}
-where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp\left(-\frac{\|\bm{x} -\bm{y}\|^2}{2 \sigma^2}\right)$} is the RBF kernel.
-The decision function $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret it as an image and we call it \emph{SVS image}.
+SVMs with RBF kernel functions map any number of data points onto an infinite-dimensional space where positive and negative points are linearly separable, hence the classification boundary on the 2D space represents the actual shape of the object.
+%Note that the decision function for SVMs can be mathematically expressed as:
+%\begin{equation} \label{eq:decisionfunc}
+%    d(\bm{x})=\sum_i\alpha_i \, k(\bm{x}_i^*,\bm{x})
+%\end{equation}
+%where $\bm{x}_i^*$ are the so-called support vectors and \mbox{$k(\bm{x}, \bm{y}) = \exp(-{\|\bm{x} -\bm{y}\|^2}/{2 \sigma^2})$} is the RBF kernel.
+Let $d(\bm{x})$ be the decision function for SVMs.
+In our formulation, $d(\bm{x})$ can be defined for every pixel $\bm{x}$ of the corresponding object image, therefore we interpret it as an image and we call it \emph{SVS image}.
 
-Figure \ref{fig:build_svs} shows an exemplar shape representation of the human ear using SVS.
+%Figure~\ref{fig:archi} includes some exemplar SVS representations of arm shapes (Step 1 box)
+
+%Figure \ref{fig:build_svs} shows an exemplar shape representation of the human ear using SVS.
 As it can be observed, the final result does not drastically depend on the original number of annotated landmarks.
@@
 We extend the SVS representation to support also the case where multiple curves with different labels are annotated.
-This is useful when annotating different structures of the same object, such as the curve of the left eyebrow and the curve of the right eyebrow on faces.
+This is useful when annotating different structures of the same object, such as the left and right eyebrows on faces.
 Even though not absolutely necessary in our framework, it can provide further guidance on the estimation of dense shape correspondences for various object classes.
@@
 This also defines for every training SVS image a warping function that registers it with the reference SVS image.
-To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu}.
+To establish the dense correspondences robustly, we are inspired by the idea of subspace constraints in the estimation of multiframe optical flow \cite{Garg:2013hu,tomasi2012dense,snape15faceflow}.
 
@@
 
-The next section describes the methodology of constructing the correspondence basis and estimating the shape flow robustly.
+To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
+Then, we apply Nonrigid Iterative Closest Point (NICP) \cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
+NICP iteratively deforms the cloud of points of every shape to match the points of the reference shape.
+This yields an initial estimation of the correspondence vectors on the sparse locations of annotated landmarks on the reference shape.
+Finally, the correspondence basis is found by applying PCA on these correspondence vectors and keeping only the first $R$ principal components.
 
@@
     \includegraphics[height=\flowh]{resources/Fig_Flows/6}
-    \caption{Exemplar deformation fields for the left forearm, obtained using the proposed pipeline. Figure best viewed by zooming in.}
+    \caption{Exemplar deformation fields for the left arm, obtained using the proposed pipeline. Figure best viewed by zooming in.}
     \label{fig:deformationfield}
@@
 
-\subsubsection*{Non-rigid ICP and Correspondence Basis Creation} \label{sec:trabasis}
-
-To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
-Then, we apply NICP \cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
-NICP iteratively deforms the cloud of points of every shape to match the points of the reference shape.
-This yields an initial estimation of the correspondence vectors on the sparse locations of annotated landmarks on the reference shape.
-Finally, the correspondence basis is found by applying PCA on these  correspondence vectors and keeping only the first $R$ principal components.
-
-%To make this correspondence vectors estimation dense (i.e.~for every pixel of the reference SVS image), we apply Thin-Plate Splines (TPS)\cite{Bookstein1989} interpolation.
-Finally, the correspondence basis is found by applying PCA on the result of TPS interpolation and keeping only the first $R$ principal components.
-
-%
-%
-%Since optical flow pixel-wise frame registration, the trajectory basis build should also match the dimension, which is dense on shapes with trajectory length depends on number of training data.
-With correspondences produced after applying NICP, Thin-Plate Spline (TPS)\cite{Bookstein1989} transformations are utilized to warp every shape planes to template plane thereby generates an implicit dense shape registering.
-For all dense transformations $\bm{u}_n(\bm{x}), n \in \{1,...,F\}$, where $F$ is number of data and $\bm{x}$ is vector of pixels, Principle Component Analysis (PCA) is performed on trajectory to obtain low rank trajectory basis:
-%\begin{equation}
-%    \begin{bmatrix}
-%        \bm{u_1}(\bm{x}) \\
-%        \vdots \\
-%        \bm{u_F}(\bm{x})
-%    \end{bmatrix}
-%    =
-%    \begin{bmatrix}
-%        \bm{q_1}(1) & \cdots & \bm{q_R}(1) \\
-%        \vdots      & \ddots & \vdots  \\
-%        \bm{q_1}(F) & \cdots & \bm{q_R}(F)
-%    \end{bmatrix}
-%    \times
-%    \begin{bmatrix}
-%        \bm{v_1}(x) \\
-%        \vdots \\
-%        \bm{v_R}(x)
-%    \end{bmatrix}
-%\end{equation}
-%where $\bm{q_i}(n)$ are low rank components with $R \ll 2F$ and $\bm{v_i}(x)$ weighted each component with dependencies on $x$. Simpler expression shown below:
-%\begin{equation}
-%    \bm{u}_n(\bm{x})=\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(\bm{x})+\bm{\varepsilon_n}(\bm{x})
-%\end{equation}
-%Although optical flow on shapes made under the assumption that objects motion are smooth, the low rank constrain on trajectory basis recovered the hypothesis.
-
-% \begin{figure}[t!]
-%         \centering
-%         \begin{tabular}{cccccccc}
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_0}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_1}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_2}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_3}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_4}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_5}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/image_6}
-%         &
-%         \includegraphics[trim=200 150 200 50,clip,width=.1\columnwidth]{resources/Fig_Variance/variances}
-%         \end{tabular}
-%     \caption{Variances}
-%     \label{fig:variances}
-% \end{figure}
-
-\subsubsection*{Variational Shape Flow Estimation}%{Multi-image Subspace Flow}
-\label{varshapeflow}
-
 Let $\bm{d}(\bx;n)$, $\bm{d}(\bx;0):\Omega\rightarrow \R^{N_c}$ be the $n$-th training SVS image and the reference SVS image respectively.
@@
 
-We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}.
-In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with the shape flow result of the TPS interpolation described in Sec.~\ref{sec:trabasis}.
+We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu} \footnote{We used the publicly available code at \url{http://bitbucket.org/troussos/mfsf/}}.
+We slightly modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Step~\ref{sec:step2}.
+This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed. 
+% 
+Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method.
+These results correspond to exemplar training shapes in the case of an arm dataset.
+We observe that the shape flow estimation captures the shape and deformations of the human arm in a plausible way.
+
+%In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with a Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Sec.~\ref{sec:step2}.
 We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization.
@@
 The minimization w.r.t.~
-$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+%$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
 The minimization w.r.t.~
-$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
-
-Figure~\ref{fig:deformationfield} shows some examples of deformation fields derived from the estimated shape flow computed by the aforementioned method.
-These results correspond to exemplar training shapes in the case of an arm dataset.
+%$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
 

### 2015-11-06 contents/introduction.tex
updates on describing steps, shortened a lot

@@
 
-Furthermore, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using either simplistic or even more sophisticated and robust shape representation methods \cite{Nguyen2013}.
+Furthermore, we capitalise on recent advances on multiframe optical flow estimation \cite{Garg:2013hu,tomasi2012dense,snape15faceflow} and show that the relevant methodologies have matured enough to densely annotate the proposed shapes using either simplistic or even more sophisticated and robust shape representation methods \cite{Nguyen2013}.
 In particular, in order to build dense correspondences between different shape instances of the same object class, we jointly estimate the optical flow among all the instances by imposing low-rank constrains, an approach that we call \emph{Shape Flow}.

### 2015-11-06 contents/evaluation.tex

@@
 
-\textbf{Databases \& Error Metrics}
-For face experiment, both models were built using the 811 training images of the Labelled
-Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
+\paragraph{Databases \& Error Metrics} For face experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
 Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
@@
 
-\textbf{Experiments}
-CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
+\paragraph{Experiments} CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
 We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models.
@@
 
-\textbf{Dataset \& Error Metric}
-There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
+\paragraph{Dataset \& Error Metric} There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
 In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
@@
 
-\textbf{Experiments} 
-Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
+\paragraph{Experiments} Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
 

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

@@
-This sections evaluates the performance of proposed methodology in estimating correspondences of human poses in-the-wild.
-Results for quantitative an qualitative experiments are reported.
-Experiments \ref{exp:daam_benchmark} show performance of fitting dense SDMs built to non-rigid objects having rich interior textures e.g.
-faces and ears.
-Experiments \ref{exp:benchmark} compare the joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild.
-In addition, this experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons.
-Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
+We evaluate the performance of the proposed methodology in experiments of estimating correspondences of human poses in-the-wild and in non-rigid object alignment in-the-wild.
 For further experimental results and visualisations please refer to our supplementary material.
+
+%Results of quantitative and qualitative evaluations are reported.
 
@@
 
-This experiment compares the fitting accuracy of our dense Active Appearance Models (dAAMs) versus the one of classic AAM on the problem of nonrigid face and ear alignment in-the-wild.
+This experiment compares the fitting accuracy of dense Active Appearance Models (dAAMs) trained with the proposed framework, as compared to classic AAMs.
+We here consider two object classes that have rich interior textures: faces and ears.
+The comparisons are for the problem of non-rigid face and ear alignment in-the-wild.
 
@@
 This section provides experiments showing that training patch-based AAM from outline annotation provides remarkable joints estimation.
+
+Experiments \ref{exp:benchmark} compare joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild.
+In addition, the experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons.
+Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
 

### 2015-11-06 contents/implementation.tex
Updates from ShareLaTeX

@@
     \bm{u}_n(\bx) \approx
-    \sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
+    \textstyle \, \sum_{i=1}^R \, \bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
 \end{equation}
@@
 
-\paragraph{Dense Active Appearance Model} Since all the deformation fields acquired by Step~\ref{sec:step3} contain the same number of pixels, which are the same as in the reference frame, the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation fields as dense annotations of the object's shape.
+\paragraph{Dense Active Appearance Model} Since all the deformation fields acquired by Step~\ref{sec:step3} are defined for the pixels of the reference SVS image, the spatial positions $\bm{x}_i=(x_i, y_i)$ of these pixels can be treated as point landmarks and the deformation fields as dense annotations of the object's shape.
 Consequently, building a dense shape model reduces to normalising these dense annotations with respect to a global similarity transform (typically using Procrustes Analysis) and applying PCA.
@@
 
-\paragraph{Outline Patch-Based Active Appearance Model}
-The object classes for which the interior appearance does not have specific structure are modeled using patch-based AAMs \cite{Tzimiropoulos2014} trained on a set of sparse landmarks.
+\paragraph{Outline Patch-Based Active Appearance Model} The object classes for which the interior appearance does not have specific structure are modeled using patch-based AAMs \cite{Tzimiropoulos2014} trained on a set of sparse landmarks.
 Especially for human body parts (arms, legs), we strongly believe that the points located to the outline of the object are more suitable compared to the internal ones that correspond to the skeleton joints, which are commonly used by current literature \cite{buehler2011upper,charles2013domain,pfister2015flowing,yang2013articulated}.

### 2015-11-06 contents/evaluation.tex
citation fix, label fix

@@
 
-\paragraph{Databases \& Error Metrics} For face experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
+\textbf{Databases \& Error Metrics} For face experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
 Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
@@
 
-\paragraph{Experiments} CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
+\textbf{Experiments} CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
 We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models.
@@
 
-\paragraph{Dataset \& Error Metric} There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
-In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
+\textbf{Dataset \& Error Metric} There are significant numbers of datasets exist for human pose estimation, where FLIC \cite{sapp2013modec}, BBC Pose \cite{pfister2015flowing}, Fashion Pose \cite{dantone2013human} and MPII \cite{andriluka14cvpr} attracted most public attention.
+In our work, we reported our performance comparison on BBC Pose Dataset \cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
 
@@
 
-\paragraph{Experiments} Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
+\textbf{Experiments} Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
 

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

--- 2015-11-06 contents/evaluation.tex
@@
-We evaluate the performance of the proposed methodology in experiments of estimating correspondences of human poses in-the-wild and in non-rigid object alignment in-the-wild.
-For further experimental results and visualisations please refer to our supplementary material.
+We evaluate the performance of the proposed methodology for the task of human body pose correspondence estimation, as well as non-rigid alignment ``in-the-wild''.
+For further experimental results, please refer to the supplementary material.
 
@@
 \label{exp:daam_benchmark}
+Herein, we compare the fitting accuracy of the dAAMs that are trained with our proposed framework with holistic sparse AAMs~\cite{Cootes2001,Matthews2004}.
+We consider two object classes that demonstrate rich texture: face and ear.
 
-This experiment compares the fitting accuracy of dense Active Appearance Models (dAAMs) trained with the proposed framework, as compared to classic AAMs.
-We here consider two object classes that have rich interior textures: faces and ears.
-The comparisons are for the problem of non-rigid face and ear alignment in-the-wild.
-
-\paragraph{Databases \& Error Metrics} For face experiment, both models were built using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{Asthana2014} database.
-Classic AAM were built from 68 point landmark annotations using the standard procedure described in \cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
+\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}.
+Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}.
+We use the standard formulation described in~\cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
 Our dAAMs were built as the pipeline proposed.
@@
 \label{exp:benchmark}
-This section provides experiments showing that training patch-based AAM from outline annotation provides remarkable joints estimation.
 
-Experiments \ref{exp:benchmark} compare joints localisation accuracy of our skeleton prediction from outline fitting with respect to that of state-of-the-art human pose estimation algorithms in-the-wild.
+This experiment evaluates the localisation of arm joints using our skeleton prediction from outline fitting and compares it to state-of-the-art human pose estimation algorithms in-the-wild. 
+% We show here that training a patch-based AAM from our automatic outline annotations provides remarkable joints estimation.
 In addition, the experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons.
@@
 
-\paragraph{Dataset \& Error Metric} There are significant numbers of datasets exist for human pose estimation, where FLIC\cite{sapp2013modec}, BBC Pose\cite{pfister2015flowing}, Fashion Pose\cite{dantone2013human} and MPII\cite{andriluka14cvpr} attracted most public attention.
-In our work, we reported our performance comparison on BBC Pose Dataset\cite{pfister2015flowing}, which has relatively most consistent skeleton annotation among the others.
+\paragraph{Dataset \& Error Metric} There exist several datasets for human pose estimation, with FLIC \cite{sapp2013modec}, BBC Pose \cite{pfister2015flowing}, Fashion Pose \cite{dantone2013human} and MPII \cite{andriluka14cvpr} being some of the most commonly-used ones.
+In this work, we report quantitative evaluation on BBC Pose, which contains the most consistent skeleton annotations among the relevant datasets.
 

### 2015-11-06 contents/implementation.tex
citation fix, label fix
Updates from ShareLaTeX

@@
 
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=0.4\textwidth]{resources/models}
+    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
+    \label{fig:dense_models}
+\end{figure}
+
+\begin{figure*}[t!]
+\begin{center}
+ \begin{tabular}{ccc}
+\subfigure[]{
+    \newcommand{\flowh}{0.12\columnwidth}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/1}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/2}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/3}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/4}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/5}
+    \includegraphics[height=\flowh]{resources/Fig_Flows/6}
+} &
+\subfigure[]{
+    \includegraphics[width=0.2\textwidth]{resources/models}
+}
+ \end{tabular}
+\end{center}
+\caption{(a) . (b) }
+\label{REC}
+\end{figure*}
+
 % ---------------------------------------------------------------------------------------------------------------------------------------------------
@@
 This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v}_i(\bx)$ that are spatially regularised and enforce a low-rank prior.
-We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$.
+%We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$. 
 The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
@@
 
-We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu} \footnote{We used the publicly available code at \url{http://bitbucket.org/troussos/mfsf/}}.
-We slightly modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Step~\ref{sec:step2}.
-This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed.
+We implement the minimization of the energy $E_{sf}$ by using the optimization algorithm described in \cite{Garg:2013hu}. For more details, please refer to the Supplementary Material.
+%We slightly modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate %Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Step~\ref{sec:step2}.
+%This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed.
 %
@@
 
-\begin{figure}[b!]
-    \centering
-    \includegraphics[width=0.45\textwidth]{resources/models}
-    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
-    \label{fig:dense_models}
-\end{figure}
-
 The deformation fields obtained from Step~\ref{sec:step3} can be used to naturally build two different kinds of effective Active Appearance Models (AAMs) \cite{Cootes2001, Matthews2004}: \emph{dense} \cite{ramnath2008increasing, Amberg2009, anderson2014using} and \emph{patch-based} \cite{Tzimiropoulos2014}.

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

--- 2015-11-06 contents/evaluation.tex
@@
     % \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
-    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
+    \caption{Example of human pose annotation for left arm among 4 annotators. The large variance shows the difficulties of having consistent landmarks. Figure best viewed by zooming in.}
     \label{fig:variance}
@@
 Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}.
-We use the standard formulation described in~\cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model.
-Our dAAMs were built as the pipeline proposed.
-Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations.
-For this experiment, we report results using pixels intensities (INT) for both models.
+Our dAAMs were built as described in Step~\ref{sec:step4}.
+In both cases we build the appearance models using pixel intensities.
+The results are reported on the 224 images of the LFPW testset.
 
-For ear experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear.
-To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper.
+In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions.
+The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper.
 Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
-We randomly split the previous database into two disjoint sets of training (500) and testing (105) images.
-Both models were built using the 500 images training set and their fitting accuracy evaluated on the 105 images of the testing set.
-Note here that we used the same procedures to build the models as for faces and same error metric for evaluation.
+We randomly split the database into two disjoint sets of training (500) and testing (105) images.
+The training of the two models was done in the same way as in the face's case.
 
@@
 
-\paragraph{Experiments} CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
+\paragraph{Results} Cumulative Error Distribution (CED) curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
 We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models.

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

--- 2015-11-06 contents/evaluation.tex
@@
 The results are reported on the 224 images of the LFPW testset.
+The fitting error is evaluated as the point-to-point distance normalised by the face's size.
 
@@
 We randomly split the database into two disjoint sets of training (500) and testing (105) images.
-The training of the two models was done in the same way as in the face's case.
+The training and evaluation of the two models is done in the same way as in the face's case.
 
@@
 
-\paragraph{Results} Cumulative Error Distribution (CED) curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
-We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models.
-This result is expected due to the more complex structure of the ear shape.
-Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
+\paragraph{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.
+
+Through visual inspection we determined that fitting errors below 0.1 typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
 Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.

### 2015-11-09 contents/evaluation.tex

--- 2015-11-06 contents/evaluation.tex
@@
 \end{figure}
+
+\paragraph{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.
+
+Through visual inspection we determined that fitting errors below 0.1 typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
+Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.
+In fact, classic AAM fail to improve the accuracy of the original initialisation on ears.
+Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
 

### 2015-11-09 contents/conclusion.tex
Final

Learning and fitting statistical deformable models (SDM) is one of the most important areas in computer vision. Generally, in order to train a SDM a set of pre-defined correspondences are required. In some objects, such as human face, semantically meaningful correspondences can be found, but require laborious human manual annotations, on other objects it is very difficult, or even impossible, to find semantically meaningful correspondences. In this paper, we propose one the first comprehensive procedures for establishing correspondences (that do not necessarily correspond to semantically meaningfull object landmarks) in arbitrary objects with minimal ammount of human annotation. We apply the proposed approach for the construction of the first, to the best of our knowledge, highly descriptive SDM for the human arm.

### 2015-11-09 contents/evaluation.tex
Final

--- 2015-11-06 contents/evaluation.tex
@@
 
-\subsection{Non-rigid Object Alignment In-the-wild}
-\label{exp:daam_benchmark}
-Herein, we compare the fitting accuracy of the dAAMs that are trained with our proposed framework with holistic sparse AAMs~\cite{Cootes2001,Matthews2004}.
-We consider two object classes that demonstrate rich texture: face and ear.
-
-\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}.
-Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}.
-Our dAAMs were built as described in Step~\ref{sec:step4}.
-In both cases we build the appearance models using pixel intensities.
-The results are reported on the 224 images of the LFPW testset.
-The fitting error is evaluated as the point-to-point distance normalised by the face's size.
-
-In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions.
-The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper.
-Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
-We randomly split the database into two disjoint sets of training (500) and testing (105) images.
-The training and evaluation of the two models is done in the same way as in the face's case.
-
-\begin{figure}[b!]
-    \centering
-    \includegraphics[width=0.6\columnwidth]{resources/DAAMBenchmark/legend}
-    \\
-    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/face}
-    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
-    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
-    \label{fig:daam_benchmark}
-\end{figure}
-
-\paragraph{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.
-
-Through visual inspection we determined that fitting errors below 0.1 typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
-Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.
-In fact, classic AAM fail to improve the accuracy of the original initialisation on ears.
-Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
-
-\subsection{Arm Pose Estimation}
-\label{exp:benchmark}
-
-This experiment evaluates the localisation of arm joints using our skeleton prediction from outline fitting and compares it to state-of-the-art human pose estimation algorithms in-the-wild. 
-% We show here that training a patch-based AAM from our automatic outline annotations provides remarkable joints estimation.
-In addition, the experiment investigates the impact of annotating outlines of human poses instead of annotating skeletons.
-Note that all results reported in this section were obtained by fitting patch-based AAM using the fast version of the Simultaneous Inverse Compositional algorithm (Fast-SIC) originally proposed by the authors of \cite{Papandreou2008}.
-
-\paragraph{Dataset \& Error Metric} There exist several datasets for human pose estimation, with FLIC \cite{sapp2013modec}, BBC Pose \cite{pfister2015flowing}, Fashion Pose \cite{dantone2013human} and MPII \cite{andriluka14cvpr} being some of the most commonly-used ones.
-In this work, we report quantitative evaluation on BBC Pose, which contains the most consistent skeleton annotations among the relevant datasets.
-
-The training of patch-based AAM for arms involves manual outline annotation from a combination of datasets, including H3D \cite{PoseletsICCV09}, Microsoft COCO \cite{lin2014microsoft}, MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
-The training set contains 891 training images from where 500 are annotated with outline manually.
-A dAAMs is built from 500 training images thereby produces dense correspondences for generating sparse outline annotation (29 landmarks).
-A patch-based AAM is build from sparse annotations before fitting to 391 images.
-Manual minor correction are required for putting those fitted image to training set.
-The final patch-based AAM is built from 891 images and validated on validation set given by BBC Pose.
-
-In order to compare with current state-of-the-art human pose estimation on BBC Pose, we uses same error metric as BBC Poses does, which normalises testing images to have height of 256 pixels.
-Performance measure of experiments in this paper are plot with Cumulative Error Distribution (CED) curve, where graph shows accuracy against distance from ground truth in pixels on normalised images.
-
-\begin{figure}[b!]
-    \centering
-    \includegraphics[width=\columnwidth]{resources/HandBenchmark/legend}
-    \\
-    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/wrist}
-    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
-    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
-    \label{fig:hand_benchmark}
-\end{figure}
-
-\paragraph{Experiments} Two experiments are undertaken in this section: 1) presenting training classic patch-based AAM from outline annotation provides remarkable joints estimation; 2) supporting outline annotation by comparing with training classic patch-based AAM from joint annotation.
-
-First experiment presented the accuracy of predicting joints positions from establishing dense correspondences with outline fitting.
-We build patch-based AAM using 891 training hand images from a combination of datasets, where each image has 29 landmarks annotated alone its boundary.
-SIFT \cite{PoseletsICCV09} feature is used from image representation for our model.
-Model fitting is initialised based on current state-of-the-art human pose estimation algorithms (including Buehler \cite{buehler2011upper}, Charles14 \cite{charles2014upper}, Charles13 \cite{charles2013domain}, Pfister14 \cite{pfister2015deep}, Ramanan \cite{yang2013articulated} and Pfister15 \cite{pfister2015flowing}) on BBC Pose \cite{pfister2015flowing} dataset.
-Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton.
-For our model, joints are projected from the dense correspondence generated from our proposed method.
-
-Second experiment investigates the disadvantages of using skeleton annotation.
-We build patch-based AAM on joints with same training data and with SIFT representation.
-Both models are fine-tuned on BBC Pose validation set.
-The fitting procedure is performed under exactly same condition, e.g.
-same testing set and initialisation position.
-
-CED Curves for both experiments are shown in Figure \ref{fig:hand_benchmark} while fitting statistics are shown in supplementary material.
-Results show that, for first experiment, the fitting accuracy achieved by our method outperformed current state-of-the-art algorithms.
-In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
-While for second experiment, patch-based AAM trained with outline significantly outperforms path AAM trained with joints as we expected.
-Note that path AMM trained with Joints still comparable even marginally better than recent algorithms.
-
-% \begin{table}[b!]
-%     \small
-%     \centering
-%     \begin{tabular}{|l|c|c|c||c|c|c|}
-%         \hline
-%                             & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
-%         \hline
-%         \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
-%         \hline\hline
-%         Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
-%         Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
-%         Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
-%         Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
-%         Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
-%         Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
-%         \hline\hline
-%         Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
-%         \hline
-%     \end{tabular}
-%     \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
-%     \label{tab:hand_benchmark}
-% \end{table}
-
 \begin{figure*}[!t]
@@
     \includegraphics[height=\fh]{resources/Fixing/fix_1}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_2}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_3}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_5}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_6}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_7}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_8}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_9}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_10}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_20}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_12}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_13}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_14}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_15}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_17}
+    \hfill
     \includegraphics[height=\fh]{resources/Fixing/fix_18}
-    % \includegraphics[height=\fh]{resources/Fixing/fix_19}
     \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}.
@@
     \label{fig:outline_fitting}
+    \vspace{-10pt}
 \end{figure*}
+
+\subsection{Non-rigid Object Alignment In-the-wild}
+\label{exp:daam_benchmark}
+Herein, we compare the fitting accuracy of the dAAMs that are trained with our proposed framework with holistic sparse AAMs~\cite{Cootes2001,Matthews2004}.
+We consider two object classes that demonstrate rich texture: face and ear.
+
+\noindent\textbf{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}.
+Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}.
+Our dAAMs were built as described in Step~\ref{sec:step4}.
+In both cases we build the appearance models using pixel intensities.
+The results are reported on the 224 images of the LFPW testset.
+The fitting error is evaluated as the point-to-point distance normalised by the face's size.
+
+In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions.
+The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper.
+Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
+We randomly split the database into two disjoint sets of training (500) and testing (105) images.
+The training and evaluation of the two models is done in the same way as in the face's case.
+
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=0.6\columnwidth]{resources/DAAMBenchmark/legend}
+    \\
+    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/face}
+    \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
+    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
+    \label{fig:daam_benchmark}
+\end{figure}
+
+\noindent\textbf{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.
+By visually inspecting the results, we determined that the fitting is becomes inaccurate for errors greater than 0.1 and 0.06 for the ear and face, respectively.
+By inspecting the error curves, it can be observed that dAAMs marginally outperform sparse AAMs using pixels intensities as features.
+Therefore, the proposed pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass the commonly-used sparse AAMs.
+
+\subsection{Arm Pose Estimation}
+\label{exp:benchmark}
+
+In this experiment, we aim to compare the performance of a deformable model for the outline of the arm that is built on our proposed outline sparse annotation scheme, against the standard skeleton joints scheme that is commonly employed in literature.
+For this purpose, we employ the patch-based AAM as described in Step~\ref{sec:step4} and train two different models, one that corresponds to the outline of the arm and one on the skeleton of the hand.
+Additionally, we compare are methodology with the current state-of-the-art techniques on human arm pose estimation in-the-wild.
+
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=\columnwidth]{resources/HandBenchmark/legend}
+    \\
+    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/wrist}
+    \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
+    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
+    \label{fig:hand_benchmark}
+\end{figure}
+
+\noindent\textbf{Dataset \& Error Metric} We opted to report quantitative results on the BBC Pose\cite{pfister2015flowing} database, which contains the most consistent skeleton annotations among all the existing ones.
+The training of the outline patch-based AAM was performed after obtaining the outline annotations using our proposed framework.
+To train the part-based AAM (29 landmarks in the boundary) we used 891 training images from a combination of datasets, including H3D \cite{PoseletsICCV09}, Microsoft COCO \cite{lin2014microsoft}, MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
+SIFT \cite{PoseletsICCV09} feature is used from image representation for our model.
+Model fitting on BBC Pose is initialised based on an in house deep convolutional neural network.
+
+In order to compare with current state-of-the-art human pose estimation on BBC Pose, we used the same error metric as BBC Pose, which normalises testing images to have height of 256 pixels.
+Performance measure of experiments in this paper are plot with Cumulative Error Distribution (CED) curve, where graph shows accuracy against distance from ground truth in pixels on normalised images.
+Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton.
+For our model, joints are projected from the dense correspondence generated from our proposed method.
+Results (Figure \ref{fig:hand_benchmark}, our method is the outline PAAM) are reported comparing with the state-of-the-art which includes Buehler \cite{buehler2011upper}, Charles14 \cite{charles2014upper}, Charles13 \cite{charles2013domain}, Pfister14 \cite{pfister2015deep}, Ramanan \cite{yang2013articulated} and Pfister15 \cite{pfister2015flowing}.
+As can seen our outline part-based AAM model, even though not trained for locating the wrist and elbow, outperforms the state-of-the-art for this task.
+In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
+
+In the same experiment we investigated the disadvantages of using skeleton annotation.
+We build patch-based AAM on the skeleton of the arm with same training data.
+As it can be seen from the  CED curves of \ref{fig:hand_benchmark} the skeleton based deformable model (called joint PAAM) has significant lower performance than the our outline model (Outline PAAM),
+
+% \begin{figure*}[!t]
+%     \newcommand{\fh}{0.24\columnwidth}
+%     \centering
+%     \includegraphics[height=\fh]{resources/Fixing/fix_1}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_2}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_3}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_5}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_6}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_7}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_8}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_9}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_10}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_20}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_12}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_13}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_14}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_15}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_17}
+%     \includegraphics[height=\fh]{resources/Fixing/fix_18}
+%     \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}.
+\emph{Red} dots refer to officially provided landmarks, and \emph{green} dots are corrected position.}
+%     \label{fig:qualitative}
+% \end{figure*}
+
+% \begin{figure*}[!t]
+%     \newcommand{\ofh}{0.24\columnwidth}
+%     \centering
+%     \includegraphics[height=\ofh]{resources/Fittings/20.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/3.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/19.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/4.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/6.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/15.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/7.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/8.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/13.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/17.eps}
+%     \\
+%     \includegraphics[height=\ofh]{resources/Fittings/21.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/23.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/25.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/27.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/29.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/31.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/33.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/35.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/36.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/37.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/38.eps}
+%     \includegraphics[height=\ofh]{resources/Fittings/39.eps}
+%     \caption{Demonstration of outline fitting of patch-based AAM on arms.}
+%     \label{fig:outline_fitting}
+% \end{figure*}
 
@@
 
-This experiment demonstrates inconsistency of joints annotation among MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human} and FLIC \cite{sapp2013modec}, as well as investigate the inevitable variance of manual annotation.
+The final experiment demonstrates that is feasible to use the proposed arm model in order to correct the annotations provided by the current datasets.
+As mentioned above there are inconsistencies in the joint annotations of MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human} and FLIC \cite{sapp2013modec}.
 Three well trained annotators are used to annotate left arm using 120 test images from Fashion Pose \cite{dantone2013human} dataset.
@@
 
-Figure \ref{exp:qualitative} presents corrections of joint annotations using patch-based SDM trained as experiment \ref{exp:benchmark}.
-\emph{Red} dots shows ``ground truth" points while \emph{green} dots shows landmarks after correction using our methodology.
+Figure \ref{exp:qualitative} presents corrections of joint annotations using the proposed patch-based SDM.
+\emph{Red} dots shows ``ground truth" annotations while \emph{green} dots shows landmarks after correction using our methodology.
 There is no doubt that points after correction show more consistency among images.
 Images are cropped to hand only for better visualisation.
+Upon acceptance we will provide the corrected annotations in all the aforementioned databases.
+
+% \begin{table}[b!]
+%     \small
+%     \centering
+%     \begin{tabular}{|l|c|c|c||c|c|c|}
+%         \hline
+%                             & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
+%         \hline
+%         \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
+%         \hline\hline
+%         Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
+%         Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
+%         Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
+%         Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
+%         Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
+%         Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
+%         \hline\hline
+%         Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
+%         \hline
+%     \end{tabular}
+%     \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
+%     \label{tab:hand_benchmark}
+% \end{table}

### 2015-11-09 contents/evaluation.tex

@@
 Therefore, the proposed pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass the commonly-used sparse AAMs.
+
+\paragraph{Results} Cumulative Error Distribution (CED) curves for this experiment are shown in Figure \ref{fig:daam_benchmark}.
+We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models.
+This result is expected due to the more complex structure of the ear shape.
+Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces.
+Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations.
+In fact, classic AAM fail to improve the accuracy of the original initialisation on ears.
+Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
 
@@
 %     \label{tab:hand_benchmark}
-% \end{table}

### 2015-11-10 supplementary.tex
Updates from ShareLaTeX

\input{contents/header}

% \iccvfinalcopy % *** Uncomment this line for the final submission

\input{cvpr_setting}

\begin{document}

%%%%%%%%% TITLE
\title{Supplementary Material: Constructing Statistical Deformable Models with Shape Flow}

\author{Yuxiang Zhou, Joan Alabort-i-Medina, Anastasios Roussos, Stefanos Zafeiriou\\
Imperial College London\\
180 Queen’s Gate, SW7 2AZ, London, U.K.\\
{\tt\small \{yuxiang.zhou10, ja310, troussos, s.zafeiriou\}@imperial.ac.uk}}
\maketitle
\thispagestyle{empty}

%%%%%%%%% Appendix
\section*{Introduction}
In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing dense AAMs without consistent set of landmarks. 
We present four different sets of experiments. 
In Section \ref{sec:fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs. In Section \ref{sec:modelanalysis}, we provide evaluations and comparisons of dAAMs, in terms of model compactness, warping quality and reconstruction accuracy. 
Moreover, Section \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can be used to effectively generate novel modified instances of an object, such as caricatures, from simple hand drawn sketches.
Finally, in Section \ref{sec:segmentation}, we evaluate the application of the proposed methodology on the problem of segmenting objects that are difficult to annotate with a consistent set of landmarks, such as bottles and human bodies.

\appendix
\section{Fitting Results}
\label{sec:fittingresults}

This section provides additional visualisations for the experiments of Section 3.3 of the main submission (Non-rigid object alignment in-the-wild). We visualise pixel-wise dense fitting results for both faces and ears. Results for this experiment of faces are reported over the 224 testing images of the LFPW database using 68 point ground truth landmark annotations
\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}. 
For ears, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in the paper. Results for fitting ears are reported over 105 testing images.

Figure \ref{fig:fr} shows dense fitting results using a grid visualisation, thus dense points are visible without affecting the visibility of appearance.

\begin{figure}[!t]
\centering
\includegraphics[width=0.5\textwidth]{supports/Fittings/fittings}
\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
\label{fig:fr}
\end{figure}

\section{Shape Model Analysis}
\label{sec:modelanalysis}

\begin{figure}[!b]
    \centering
    % \vspace*{-0.1in}
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_ear}
        %\caption{dAAMs dense shape reconstruction}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_face}
        %\caption{AAMs dense shape reconstruction}
    \end{subfigure}
    \caption{Dense shape reconstruction errors for ears and faces. Top: results of reconstruction on ears, bottom: results of reconstruction on faces. The normalised point-to-point error is used an evaluation measure.}
    \label{fig:rc_face}
\end{figure}

We first investigate the reconstruction accuracy of AAMs and dAAMs in the shape space. In particular, given a ground-truth shape, we use the shape models from both AAMs and dAAMs to reconstruct the given shape densely. Since AAMs contain a sparse shape model, we densify it using a piecewise affine transformation, which is typically used in warping textures on to shape model too. Figure \ref{fig:rc_face} shows plots of dense shape reconstruction errors for ears and faces, for varying number of principal components kept. We observe that dAAMs significantly outperform classic AAMs on shape reconstruction.

Furthermore, we explore the compactness of the built AAMs and dAAMs models. 
Figure \ref{fig:compact} demonstrates the variance explained as a function of the number of principal components. One can infer that dAAMs have a more compact shape model than AAMs, which leads to better reconstruction especially with few shape components.

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
        %\caption{dAAMs vs AAMs Variance Ratio}
    \end{subfigure}
    \begin{subfigure}[b]{0.43\textwidth}
            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
    \end{subfigure}
    \caption{Variance explained by each principal component, for both dAAM and AAM models. Top: variance explained by each principal component. Bottom: cumulative plot of the variance explained as a function of the principal components.}
    \label{fig:compact}
\end{figure}

Finally, Figure \ref{fig:pcamodel} visualises the principal components of dAAMs for ears and faces. We observe that the variation of both shape and appearance captured by the model seem plausible.

\begin{figure*}[!t]
\centering
\includegraphics[width=\textwidth]{supports/Models/models}
\caption{Principal components of dAAMs built on ears (top) and faces (bottom). The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right). $\pm 3$ times the variance of the corresponding component is used in each case.}
\label{fig:pcamodel}
\end{figure*}

\section{Appearance Reconstruction}
\label{sec:reconstruct}

\begin{figure}[!b]
    \centering
    %\vspace*{-0.2in}
    \includegraphics[width=0.5\textwidth]{resources/Fig_Draw/draw}
    \caption{Synthesizing face images from caricature sketches. First column: caricature sketches. Second column: arbitrary chosen face images. Third and last column: sketch-based warping of images based on AAMs (third column) and dAAMs (last column).}
    \label{fig:draw}
\end{figure}

In this qualitative experiment, we show how the proposed pipeline can be used to generate novel modified instances of an object, e.g. caricatures. To be specific, firstly we manually craft a set of hand-drawn cartoon-like shape sketches. We then apply shape flow to align them with the reference frame. In this way, we establish dense correspondences of landmarks. Afterwards, we perform shape reconstruction using both AAMs and dAAMs. Finally, we warp the appearance from arbitrarily chosen faces on the reconstructed shape using either piecewise affine warp (in the case of AAMs) or shape flow (in the case of dAAMs). The corresponding results are shown in figure \ref{fig:draw}. We see that AAMs introduce more severe artifacts, especially on the areas of mouth and eyes, where nuanced information is missing or models are overly deformed. In contrast, dAAMs yield a significantly more plausible result.

\section{Segmentation using Dense AAM}
\label{sec:segmentation}

In this section, we present experiments of utilising our dense AAM for object segmentation. Two object classes, bottles and human bodies, are considered. For human bodies, we use images along with ground truth segmentation from Space-Time Actions dataset \footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}, which includes sequences with several human actions. We use ``jumping'' and ``sliding'' actions. As far as bottles are concerned, we use 500 high-resolution images that we collected and annotated using a newly-defined 50 point annotation scheme, as well as the curve annotations proposed in this paper. We randomly split these images into two disjoint sets of training (400) and testing (100) images. Bottle models were built using 400 training images while body models are built in terms of human actions (e.g. jumping), each having approximately 200 training images and 50 test images.

\begin{figure}[!t]
    \centering
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/ear}
        %\caption{Ear Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/bottle}
        %\caption{Bottle Initial Bounding Box}
    \end{subfigure}
    \begin{subfigure}[b]{0.15\textwidth}
            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/body}
        %\caption{Body Initial Bounding Box}
    \end{subfigure}
    \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
    \label{fig:seg_init}
\end{figure}

Fitting dAAMs on test images yields dense landmarks that can be used to perform segmentation. In a real-world scenario, a simple object detector would be required to be applied prior to our pipeline to initialise the fitting. However, as a simple evaluation, we initialise the fitting by randomly perturbing the ground-truth bounding box with certain variance to simulate an object detector with implicit detection, see e.g.~Figure \ref{fig:seg_init}. Table  \ref{tab:seg_result} reports the segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline.

\begin{table}[!h]
\small
\centering
\begin{tabular}{|l|c|c|c|}
\hline
\emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
\hline\hline
Bottles         & 0.8125      & 0.1460     & 0.8414\\
Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
\hline
\end{tabular}
\caption{Segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline. The mean, standard deviation and median of the precision error are provided.}
\label{tab:seg_result}
\end{table}

% {\small
% \bibliographystyle{ieee}
% \bibliography{bib}
% }

\end{document}

### 2015-11-10 supplementary.tex
Updates from ShareLaTeX

@@
 \centering
-\includegraphics[width=0.5\textwidth]{supports/Fittings/fittings}
+\includegraphics[width=0.5\textwidth]{Supplementory_Meterial/Fittings/fittings}
 \caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_ear}
+            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/sr_ear}
         %\caption{dAAMs dense shape reconstruction}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_face}
+            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/sr_face}
         %\caption{AAMs dense shape reconstruction}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
+            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/var_ratio}
         %\caption{dAAMs vs AAMs Variance Ratio}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
+            \includegraphics[width=\textwidth]{Supplementory_Meterial/Model_Analysis/cumu_var_ratio}
         %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
@@
 \centering
-\includegraphics[width=\textwidth]{supports/Models/models}
+\includegraphics[width=\textwidth]{Supplementory_Meterial/Models/models}
 \caption{Principal components of dAAMs built on ears (top) and faces (bottom).
@@
     %\vspace*{-0.2in}
-    \includegraphics[width=0.5\textwidth]{resources/Fig_Draw/draw}
+    \includegraphics[width=0.5\textwidth]{Supplementory_Meterial/Fig_Draw/draw}
     \caption{Synthesizing face images from caricature sketches.
@@
     \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/ear}
+            \includegraphics[height=\textwidth]{Supplementory_Meterial/Segmentation_Measure/ear}
         %\caption{Ear Initial Bounding Box}
@@
     \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/bottle}
+            \includegraphics[height=\textwidth]{Supplementory_Meterial/Segmentation_Measure/bottle}
         %\caption{Bottle Initial Bounding Box}
@@
     \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/body}
+            \includegraphics[height=\textwidth]{Supplementory_Meterial/Segmentation_Measure/body}
         %\caption{Body Initial Bounding Box}

### 2015-11-10 supplementary.tex
Figure Fix

--- 2015-11-10 supplementary.tex
@@
 \centering
-\includegraphics[width=0.5\textwidth]{supports/Fittings/fittings}
+\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
 \caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_ear}
+            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/sr_ear}
         %\caption{dAAMs dense shape reconstruction}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/sr_face}
+            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/sr_face}
         %\caption{AAMs dense shape reconstruction}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/var_ratio}
+            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/var_ratio}
         %\caption{dAAMs vs AAMs Variance Ratio}
@@
     \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{supports/Model_Analysis/cumu_var_ratio}
+            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/cumu_var_ratio}
         %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
@@
 \centering
-\includegraphics[width=\textwidth]{supports/Models/models}
+\includegraphics[width=\textwidth]{Suplementory_Meterial/Models/models}
 \caption{Principal components of dAAMs built on ears (top) and faces (bottom).
@@
     %\vspace*{-0.2in}
-    \includegraphics[width=0.5\textwidth]{resources/Fig_Draw/draw}
+    \includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fig_Draw/draw}
     \caption{Synthesizing face images from caricature sketches.
@@
     \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/ear}
+            \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/ear}
         %\caption{Ear Initial Bounding Box}
@@
     \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/bottle}
+            \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/bottle}
         %\caption{Bottle Initial Bounding Box}
@@
     \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{supports/Segmentation_Measure/body}
+            \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/body}
         %\caption{Body Initial Bounding Box}

### 2015-11-11 supplementary.tex
Updates from ShareLaTeX

@@
 %%%%%%%%% TITLE
-\title{Supplementary Material: Constructing Statistical Deformable Models with Shape Flow}
-
-\author{Yuxiang Zhou, Joan Alabort-i-Medina, Anastasios Roussos, Stefanos Zafeiriou\\
-Imperial College London\\
-180 Queen’s Gate, SW7 2AZ, London, U.K.\\
-{\tt\small \{yuxiang.zhou10, ja310, troussos, s.zafeiriou\}@imperial.ac.uk}}
+\title{Supplementary Material \\ Estimating Correspondences of Deformable Objects ``In-the-wild"}
+\input{contents/authors}
 \maketitle
@@
 \section*{Introduction}
-In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing dense AAMs without consistent set of landmarks.
-We present four different sets of experiments.
-In Section \ref{sec:fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs.
+In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing both Dense AAMs and Patch-based AAMs. 
+For \textbf{Dense AAM}, We present more detailed algorithms explanation and intrinsic property analysis of Dense AAMs.
+In section~\ref{sec:cost_function},  minimisation of the energy function are described in more details.
+In Section \ref{sec:daam_fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs.
 In Section \ref{sec:modelanalysis}, we provide evaluations and comparisons of dAAMs, in terms of model compactness, warping quality and reconstruction accuracy.
-Moreover, Section \ref{sec:reconstruct} serves as a qualitative demonstration of how the proposed pipeline can be used to effectively generate novel modified instances of an object, such as caricatures, from simple hand drawn sketches.
-Finally, in Section \ref{sec:segmentation}, we evaluate the application of the proposed methodology on the problem of segmenting objects that are difficult to annotate with a consistent set of landmarks, such as bottles and human bodies.
+For \textbf{Patch-based AAM}, we described how sparse landmark points are sparsely sampled from dense reference shape and mapped to rest shapes according to dense correspondences in section~\ref{sec:sparsesample}.
+A visualisation for Patch-based AAM shape model is presented in section~\ref{sec:paam_sm}.
+Also more visualisation of fitting results are shown in section~\ref{sec:paam_fittingresults}.
 
 \appendix
-\section{Fitting Results}
-\label{sec:fittingresults}
+\section{Dense Active Appearance Model}
+\label{sec:daam}
 
+\subsection{Detailed Cost Function Description}
+\label{sec:cost_function}
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
+\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
+\label{fig:fr}
+\end{figure}
+
+\begin{figure*}[!t]
+\centering
+\includegraphics[width=\textwidth]{Suplementory_Meterial/Models/models}
+\caption{Principal components of dAAMs built on ears (top) and faces (bottom).
+The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right).
+$\pm 3$ times the variance of the corresponding component is used in each case.}
+\label{fig:pcamodel}
+\end{figure*}
+
+Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
+We propose to perform this estimation simultaneously for all training data, by using the correspondence basis.
+
+In order to learn the such a subspace, we first transform the original annotation to point clouds.
+Then, we use NICP to align the previous point clouds with respect to a reference point cloud template.
+NICP iteratively deforms each point cloud until its points match the ones on the shape template and correspondences are established.
+However, because optical flow is a pixel-wise frame registration technique, we need to establish correspondences for all pixels on the reference frame rather than for sparse point clouds.
+To achieve this, we apply Thin Plate Spline (TPS) \cite{Bookstein1989} to find correspondences for all pixels in the reference frame given the point cloud correspondences provided by the previous NICP stage.
+Once dense correspondences have been established among all pixels, the so-called correspondence subspace is obtained by performing PCA the trajectory of all pixels.
+Note that incorporating the previous subspace as a low rank constrained in optical flow is consistent with its assumption of smooth motion.
+
+In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with a Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Sec.~\ref{sec:step2}.
+We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization.
+After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
+The minimization w.r.t.~
+$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+The minimization w.r.t.~
+$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+
+To register all decision functions to temp`late shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.
+The objective cost function we would like to minimise is:
+\begin{align}
+    \operatorname*{arg\,min}_{\bm{u}_n(\bm{x}), \bm{v}}&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u}_n(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
+    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
+    &+ \sum[\bm{TV}(Qv)]
+\end{align}
+where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$.
+$TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
+
+Term~\eqref{eq:costfunc} state the shape constancy where points having similar classification probability are from same object.
+Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
+The objective cost function has two free parameters $u$ and $v$, so we perform alternating minimisation.
+The equation can be solved using a thresholding scheme after linearisation of image functions.
+The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in \{1,...F\}$ independently.
+
+After solving the equation, $\bm{u}_n(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g.
+$\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame.
+Figure~\ref{fig:deformationfield} demonstrates deformation fields that warps from reference frame where there is no deformation.
+
+Applying PCA on deformations trains dense deformable shape model:
+\begin{equation*}
+    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
+\end{equation*}
+where $\bm{s_p}$ is deformed shape instance. $\bm{\bar{s}}$ is mean shape and $\bm{U}_s\bm{p}$ are eigenvectors with corresponding parameters $p$.
+
+\subsection{Fitting Results}
+\label{sec:daam_fittingresults}
 This section provides additional visualisations for the experiments of Section 3.3 of the main submission (Non-rigid object alignment in-the-wild).
@@
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
-\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
-\label{fig:fr}
-\end{figure}
-
-\section{Shape Model Analysis}
+\subsection{Shape Model Analysis}
 \label{sec:modelanalysis}
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
     \centering
@@
 
-\begin{figure*}[!t]
+\section{Patch-based Active Appearance Model}
+\label{sec:paam}
+
+\subsection{Subsampling Sparse Outline from Dense Correspondent Shapes}
+\label{sec:sparsesample}
+
+\begin{figure}[!t]
 \centering
-\includegraphics[width=\textwidth]{Suplementory_Meterial/Models/models}
-\caption{Principal components of dAAMs built on ears (top) and faces (bottom).
-The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right).
-$\pm 3$ times the variance of the corresponding component is used in each case.}
-\label{fig:pcamodel}
-\end{figure*}
+\includegraphics[width=\columnwidth]{Suplementory_Meterial/dense_sample_grid}
+\caption{Demonstration of sparse sampling from dense shape.}
+\label{fig:sparsesample}
+\end{figure}
 
-\section{Appearance Reconstruction}
-\label{sec:reconstruct}
+\subsection{Patch-based AAM Shape Model}
+\label{sec:paam_sm}
 
-\begin{figure}[!b]
-    \centering
-    %\vspace*{-0.2in}
-    \includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fig_Draw/draw}
-    \caption{Synthesizing face images from caricature sketches.
+\subsection{Fitting Results}
+\label{sec:paam_fittingresults}
+
+\end{document}
+
+% \subsection{Appearance Reconstruction}
+% \label{sec:reconstruct}
+
+% \begin{figure}[!b]
+%     \centering
+%     %\vspace*{-0.2in}
+%     \includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fig_Draw/draw}
+%     \caption{Synthesizing face images from caricature sketches.
 First column: caricature sketches.
@@
 Third and last column: sketch-based warping of images based on AAMs (third column) and dAAMs (last column).}
-    \label{fig:draw}
-\end{figure}
+%     \label{fig:draw}
+% \end{figure}
 
-In this qualitative experiment, we show how the proposed pipeline can be used to generate novel modified instances of an object, e.g.
+% In this qualitative experiment, we show how the proposed pipeline can be used to generate novel modified instances of an object, e.g.
 caricatures.
@@
 
-\section{Segmentation using Dense AAM}
-\label{sec:segmentation}
+% \section{Segmentation using Dense AAM}
+% \label{sec:segmentation}
 
-In this section, we present experiments of utilising our dense AAM for object segmentation.
+% In this section, we present experiments of utilising our dense AAM for object segmentation.
 Two object classes, bottles and human bodies, are considered.
@@
 
-\begin{figure}[!t]
-    \centering
-    \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/ear}
-        %\caption{Ear Initial Bounding Box}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/bottle}
-        %\caption{Bottle Initial Bounding Box}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.15\textwidth}
-            \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/body}
-        %\caption{Body Initial Bounding Box}
-    \end{subfigure}
-    \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
-    \label{fig:seg_init}
-\end{figure}
+% \begin{figure}[!t]
+%     \centering
+%     \begin{subfigure}[b]{0.15\textwidth}
+%             \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/ear}
+%         %\caption{Ear Initial Bounding Box}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.15\textwidth}
+%             \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/bottle}
+%         %\caption{Bottle Initial Bounding Box}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.15\textwidth}
+%             \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/body}
+%         %\caption{Body Initial Bounding Box}
+%     \end{subfigure}
+%     \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
+%     \label{fig:seg_init}
+% \end{figure}
 
-Fitting dAAMs on test images yields dense landmarks that can be used to perform segmentation.
+% Fitting dAAMs on test images yields dense landmarks that can be used to perform segmentation.
 In a real-world scenario, a simple object detector would be required to be applied prior to our pipeline to initialise the fitting.
@@
 
-\begin{table}[!h]
-\small
-\centering
-\begin{tabular}{|l|c|c|c|}
-\hline
-\emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
-\hline\hline
-Bottles         & 0.8125      & 0.1460     & 0.8414\\
-Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
-Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
-\hline
-\end{tabular}
-\caption{Segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline. The mean, standard deviation and median of the precision error are provided.}
-\label{tab:seg_result}
-\end{table}
+% \begin{table}[!h]
+% \small
+% \centering
+% \begin{tabular}{|l|c|c|c|}
+% \hline
+% \emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
+% \hline\hline
+% Bottles         & 0.8125      & 0.1460     & 0.8414\\
+% Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
+% Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
+% \hline
+% \end{tabular}
+% \caption{Segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline. The mean, standard deviation and median of the precision error are provided.}
+% \label{tab:seg_result}
+% \end{table}
 
@@
 % }
-
-\end{document}

### 2015-11-12 supplementary.tex
Updates from ShareLaTeX

@@
 \label{sec:daam}
+This section presents 1) detailed description of minimising cost function, 2) intrinsic property analysis of dense AAM and 3) visualisation of fitting dense AAMs on faces and ears.
 
@@
 \label{sec:paam}
+This section shows spares annotation of densely corespondent shapes are generated, since patch-based AMM support consistent parse annotation only in section~\ref{sec:sparsesample}.
+Also, shape model visualisation of build patch-based AMM are shown in section~\ref{sec:paam_sm}, as well as corresponding fitting result visualisation are shown in section~\ref{sec:paam_fittingresults}.
 
@@
 \centering
-\includegraphics[width=\columnwidth]{Suplementory_Meterial/dense_sample_grid}
+\includegraphics[width=0.3\columnwidth]{Suplementory_Meterial/dsg}
 \caption{Demonstration of sparse sampling from dense shape.}
@@
 
+As \emph{step 4} in main paper refers, patch-based AAM are suitable for fitting objects that interior appearance having no structure, in this case e.g.
+arms.
+But patch-based AAM require consistent sparse annotation.
+So a sub-sampling step is need to meet such criteria.
+As we built dense correspondence between shapes, we only sparsely annotation one shape then rest shapes are sub-sampled automatically since sparse samples are preserved in all shapes by dense correspondent.
+Figure~\ref{fig:fig:sparsesample} shows sparse annotation (blue dots) on dense mean shape (grid visualisation used for visibility) and exemplar projected samples on other shapes.
+
 \subsection{Patch-based AAM Shape Model}
@@
 
+Figure~\ref{fig:paam_sm} shows mean shape and corresponding \pm 3 variation on first 4 principle components.
+
 \subsection{Fitting Results}
 \label{sec:paam_fittingresults}
+
+Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII, FLIC, Fashion Pose and BBC Pose.
 

### 2015-11-12 supplementary.tex
Updates from ShareLaTeX

@@
 
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\columnwidth]{Suplementory_Meterial/HandSMPAAM/handsmpaam}
+\caption{Demonstration of shape model of patch-based AAM.}
+\label{fig:paam_sm}
+\end{figure}
+
 Figure~\ref{fig:paam_sm} shows mean shape and corresponding \pm 3 variation on first 4 principle components.
@@
 
-Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII, FLIC, Fashion Pose and BBC Pose.
+\begin{table}[b!]
+    \small
+    \centering
+    \begin{tabular}{|l|c|c|c||c|c|c|}
+        \hline
+                            & \multicolumn{3}{c||}{Wrist} & \multicolumn{3}{c|}{Elbow}\\
+        \hline
+        \emph{Method}       & \emph{mean} & \emph{std} & $\leq 6pt$ & \emph{mean} & \emph{std} & $\leq 6pt$\\
+        \hline\hline
+        Buehler             & 12.08    & 19.94        & 44.5\%       & 12.94    & 14.65        & 34.4\%\\
+        Charles14           & 11.81    & 20.89        & 54.2\%       &  8.30    & 11.00        & \textbf{55.2\%}\\
+        Charles13           & 13.78    & 22.39        & 43.3\%       & 13.17    & 18.74        & 46.3\%\\
+        Pfister14           & 14.69    & 17.89        & 29.7\%       & 14.60    & 10.59        & 14.0\%\\
+        Ramanan             & 15.59    & 19.04        & 22.6\%       & 15.53    & 10.82        & 15.8\%\\
+        Pfister15           & 7.62     & 11.04        & 54.1\%       &  8.84    & 11.44        & 54.9\%\\
+        \hline\hline
+        Ours                & \textbf{6.71}& \textbf{10.90}   & \textbf{63.1\%}       & \textbf{8.20}     &  \textbf{10.54}        & 52.1\%\\
+        \hline
+    \end{tabular}
+    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
+    \label{tab:hand_benchmark}
+\end{table}
+
+Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII, FLIC, Fashion Pose and BBC Pose. And table~\ref{}
 

### 2015-11-12 supplementary.tex

@@
 \label{sec:paam}
+
+\begin{figure*}[!t]
+    \newcommand{\ofh}{0.24\columnwidth}
+    \centering
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0001.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0002.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0003.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0004.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0005.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0006.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0007.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0008.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0009.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0010.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0011.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0012.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0013.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0014.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0015.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0017.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0018.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0019.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0020.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0021.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0022.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0023.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0024.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0025.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0026.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0027.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0028.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0029.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0030.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0031.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0032.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0033.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0034.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0035.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0036.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0037.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0038.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0039.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0040.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0041.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0042.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0043.eps}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0044.eps}
+
+    \caption{Demonstration of outline fitting of patch-based AAM on arms.}
+    \label{fig:outline_fitting}
+\end{figure*}
+
 This section shows spares annotation of densely corespondent shapes are generated, since patch-based AMM support consistent parse annotation only in section~\ref{sec:sparsesample}.
@@
 
-Figure~\ref{fig:paam_sm} shows mean shape and corresponding \pm 3 variation on first 4 principle components.
+Figure~\ref{fig:paam_sm} shows mean shape and corresponding $\pm 3$ variation on first 4 principle components.
 
@@
 
-Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII, FLIC, Fashion Pose and BBC Pose. And table~\ref{}
+Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
+In addition table~\ref{tab:hand_benchmark} presents statistics results that refers to experiment 4.2 in main paper for additional information.
 
@@
 
-% {\small
-% \bibliographystyle{ieee}
-% \bibliography{bib}
-% }
+{\small
+\bibliographystyle{ieee}
+\bibliography{bib}
+}

### 2015-11-13 supplementary.tex
Updates from ShareLaTeX

@@
     \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0044.eps}
-
-    \caption{Demonstration of outline fitting of patch-based AAM on arms.}
-    \label{fig:outline_fitting}
+    \caption{Demonstration of outline fitting of patch-based AAM on arms. Images are cropped to arms only for better visualisation.}
+    \label{fig:paam_fittingresults}
 \end{figure*}
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
 \centering
-\includegraphics[width=0.3\columnwidth]{Suplementory_Meterial/dsg}
-\caption{Demonstration of sparse sampling from dense shape.}
+\newcommand{\ofh}{0.24\columnwidth}
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-0.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-1.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-2.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-3.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-4.png}
+\caption{Demonstration of sparse sampling from dense shapes.
+Left most image shows sparse sample on the reference shape while other 5 images shows projection from sampled reference shape to arbitrary shapes with dense correspondence.}
 \label{fig:sparsesample}
@@
 But patch-based AAM require consistent sparse annotation.
-So a sub-sampling step is need to meet such criteria.
-As we built dense correspondence between shapes, we only sparsely annotation one shape then rest shapes are sub-sampled automatically since sparse samples are preserved in all shapes by dense correspondent.
-Figure~\ref{fig:fig:sparsesample} shows sparse annotation (blue dots) on dense mean shape (grid visualisation used for visibility) and exemplar projected samples on other shapes.
+So a sub-sampling step is needed to meet such criteria.
+As we built dense correspondence between shapes, we only sparsely annotate one shape so rest shapes are sub-sampled automatically since sparse samples are preserved in all shapes by dense correspondence generated with shape flow.
+Figure~\ref{fig:sparsesample} shows sparse annotation (red dots) on dense mean shape (grid visualisation used for visibility) and exemplar projected samples on other shapes.
 
@@
 
-\begin{figure}[!t]
+\begin{figure}[!b]
 \centering
 \includegraphics[width=\columnwidth]{Suplementory_Meterial/HandSMPAAM/handsmpaam}
-\caption{Demonstration of shape model of patch-based AAM.}
+\caption{Principal components of patch-based AAM built on arms.
+The mean (left most column) as well asthe first four principal components are visualised with three times the variance of the corresponding component it used in each case.}
 \label{fig:paam_sm}
@@
 
-Figure~\ref{fig:paam_sm} shows mean shape and corresponding $\pm 3$ variation on first 4 principle components.
+Figure~\ref{fig:paam_sm} shows mean shape and corresponding $\pm 3$ variation on first four principle components.
+As the appearance model are built with SIFT feature, the 36-channel feature give no meaningful visualisation to human so we have not shown it.
+From arms shape model, we observe that the variation of shape captured by the model are reasonable.
 
@@
 
-\begin{table}[b!]
+\begin{table}[t!]
     \small
@@
     \end{tabular}
-    \caption{Fitting statistics on BBC Pose database for experiment \ref{exp:benchmark}}
+    \caption{Fitting statistics on BBC Pose database for experiment 4.2 in main paper.}
     \label{tab:hand_benchmark}
@@
 Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
+All fittings are initialised using same method as mention in experiment 4.2 in main paper.
+
 In addition table~\ref{tab:hand_benchmark} presents statistics results that refers to experiment 4.2 in main paper for additional information.
+Column $\leq 6pt$ reports the percentage of fittings that having errors, point-to-point distance on normalised images, less than 6 pixels (same measurement used in \cite{pfister2015flowing}).
+This shows we have notable improvement on estimating wrists and comparable results on estimating elbow.
+
+{\small
+\bibliographystyle{ieee}
+\bibliography{bib}
+}
 
@@
 % \end{table}
-
-{\small
-\bibliographystyle{ieee}
-\bibliography{bib}
-}

### 2015-11-13 supplementary.tex
updated supplementary

@@
 \section*{Introduction}
-In this supplementary material, we provide additional experimental results and comparisons for the proposed pipeline of constructing both Dense AAMs and Patch-based AAMs. 
-For \textbf{Dense AAM}, We present more detailed algorithms explanation and intrinsic property analysis of Dense AAMs.
+In this supplementary material, we provide additional algorithmic details for our shape flow estimation, as well as additional visualizations and evaluations for the dense and patch-based AAMs that were constructed using the proposed framework.
+
+%experimental evaluations for constructing both Dense AAMs and Patch-based AAMs using the proposed pipeline.
+%For \textbf{Dense AAM}, We present more detailed algorithms explanation and intrinsic property analysis of Dense AAMs.
 In section~\ref{sec:cost_function},  minimisation of the energy function are described in more details.
@@
 In Section \ref{sec:modelanalysis}, we provide evaluations and comparisons of dAAMs, in terms of model compactness, warping quality and reconstruction accuracy.
-For \textbf{Patch-based AAM}, we described how sparse landmark points are sparsely sampled from dense reference shape and mapped to rest shapes according to dense correspondences in section~\ref{sec:sparsesample}.
+%For \textbf{Patch-based AAM}, we described how sparse landmark points are sparsely sampled from dense reference shape and mapped to rest shapes according to dense correspondences in section~\ref{sec:sparsesample}.
 A visualisation for Patch-based AAM shape model is presented in section~\ref{sec:paam_sm}.
@@
 \appendix
-\section{Dense Active Appearance Model}
-\label{sec:daam}
-This section presents 1) detailed description of minimising cost function, 2) intrinsic property analysis of dense AAM and 3) visualisation of fitting dense AAMs on faces and ears.
-
-\subsection{Detailed Cost Function Description}
+\section{Implementation of Shape Flow Estimation}
 \label{sec:cost_function}
 
-\begin{figure}[!t]
-\centering
-\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
-\caption{Result of fitting dAAMs on ears (first two rows) and faces (last two rows). A dense grid visualisation is used.}
-\label{fig:fr}
-\end{figure}
+As mentioned in the main submission (Section 3, Step 3), we propose to estimate the shape flow by minimizing the following energy:
+\vspace{-5pt}
+\begin{align}
+E_{sf} & =\alpha
+\int_{\Omega}\sum_{n=1}^{N_t} \|\bm{d}(\bx+\bm{u}_n(x);n)-\bm{d}(x;0)\| \ud \bx \label{eq:costfunc}\\
+    &+ \beta \int_{\Omega}\sum_{n=1}^{N_t}\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
+    &+
+\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
+\vspace{-5pt}
+\end{align}
+We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$, which correspond to the
+two sets of unknown shape flows.
+We implement this minimization based on the optimization algorithm described in \cite{Garg:2013hu} and the relevant publicly available code \footnote{https://bitbucket.org/troussos/mfsf/downloads}.
+However, we modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Section 3, Step 2 of the main submission.
+This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed.
+
+Regarding more details on the optimization algorithm, 
+in every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration.
+We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images $\bm{d}(\bx;n)$ around the initialization.
+After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
+The minimization w.r.t.~$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+The minimization w.r.t.~$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$.
+This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+
+\section{Dense Active Appearance Modeling}
+\label{sec:daam}
+
+In this section, we report additional qualitative and quantitative evaluations and comparisons for the dAAMs of faces and ears that were constructed using the proposed framework.
+
+\subsection{Principal Components and Compactness}
+
+Figure \ref{fig:pcamodel} visualizes some of the shape and appearance principal components of the built dAAMs for ears and faces.
+We observe that in both ears and faces, the variation of both shape and appearance captured by the model seem plausible.
 
@@
 
-Using the SVS functions built from training data, one of the main steps of our pipeline is to estimate dense correspondences between all these functions.
-We propose to perform this estimation simultaneously for all training data, by using the correspondence basis.
+Figure \ref{fig:compact} shows the compactness plot for our dAAM for faces and compares it with the corresponding plot for a standard sparse AAM built on the same data.
+Note that these are the two shape models that are compared in Figure 9-left of the main submission.
+We observe that our dAAM is significantly more compact than the sparse AAM, since for any given number of components, it manages to explain a larger portion of the corresponding total variance of the training set.
 
-In order to learn the such a subspace, we first transform the original annotation to point clouds.
-Then, we use NICP to align the previous point clouds with respect to a reference point cloud template.
-NICP iteratively deforms each point cloud until its points match the ones on the shape template and correspondences are established.
-However, because optical flow is a pixel-wise frame registration technique, we need to establish correspondences for all pixels on the reference frame rather than for sparse point clouds.
-To achieve this, we apply Thin Plate Spline (TPS) \cite{Bookstein1989} to find correspondences for all pixels in the reference frame given the point cloud correspondences provided by the previous NICP stage.
-Once dense correspondences have been established among all pixels, the so-called correspondence subspace is obtained by performing PCA the trajectory of all pixels.
-Note that incorporating the previous subspace as a low rank constrained in optical flow is consistent with its assumption of smooth motion.
+\begin{figure}[!b]
+    \centering
+%    \begin{subfigure}[b]{0.43\textwidth}
+%            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/var_ratio}
+%        %\caption{dAAMs vs AAMs Variance Ratio}
+%    \end{subfigure}
+    \begin{subfigure}[b]{0.43\textwidth}
+            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/cumu_var_ratio}
+        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
+    \end{subfigure}
+    \caption{Compactness plots of dAAM (green) and sparse AAM (blue) models for faces.
+Portion of the corresponding total variance explained as a function of the number of retained principal components.}
+    \label{fig:compact}
+\end{figure}
 
-In every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration and for the very beginning, we initialize with a Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Sec.~\ref{sec:step2}.
-We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization.
-After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
-The minimization w.r.t.~
-$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
-The minimization w.r.t.~
-$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$. This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+\subsection{Dense Shape Reconstruction Ability}
 
-To register all decision functions to temp`late shape, decision function $d_i(\bm{x}), i \in {1,...,F}$ are grouped into one sequence before applying flow algorithm.
-The objective cost function we would like to minimise is:
-\begin{align}
-    \operatorname*{arg\,min}_{\bm{u}_n(\bm{x}), \bm{v}}&=\alpha \int_{\Omega}\sum_{n=1}^F|\bm{d_n}(x+\bm{u}_n(x))-\bm{d_0}(x)\| dx  \label{eq:costfunc}\\
-    &+ \beta \int_{\Omega}\sum_{n=1}^F\|\bm{u}_n(x)-\sum_{i=1}^R\bm{q_i}(n)\bm{v_i}(x)\|^2 dx \label{eq:lowrank}\\
-    &+ \sum[\bm{TV}(Qv)]
-\end{align}
-where $d_n(x)$ is the decision function from~\eqref{eq:decisionfunc}, which returns possibilities of given coordinate classified as shape component where coordinates are from set $\Omega \in \Re^2$.
-$TV(Qv)$ is total variation as regularization on low rank subspace, $Q$ is trajectory basis and $v^T.L.v$ is low rank spacial constrains.
-
-Term~\eqref{eq:costfunc} state the shape constancy where points having similar classification probability are from same object.
-Part~\eqref{eq:lowrank} applies constrain on low rank trajectory basis states in section~\ref{sec:trabasis}.
-The objective cost function has two free parameters $u$ and $v$, so we perform alternating minimisation.
-The equation can be solved using a thresholding scheme after linearisation of image functions.
-The minimisation can be speed up by paralleling the minimisation for every spatial-temporal point $(x;n), x \in \Omega, n \in \{1,...F\}$ independently.
-
-After solving the equation, $\bm{u}_n(\bm{x}), x \in \Omega$ gives a group of deformation fields that registering every decision functions in the shape sequence to reference frame e.g.
-$\bm{u_1}(\bm{x})$ registers decision function $\bm{d_1}(\bm{x})$ to the reference frame.
-Figure~\ref{fig:deformationfield} demonstrates deformation fields that warps from reference frame where there is no deformation.
-
-Applying PCA on deformations trains dense deformable shape model:
-\begin{equation*}
-    \bm{s_p}=\bm{\bar{s}} + \bm{U}_s\bm{p}
-\end{equation*}
-where $\bm{s_p}$ is deformed shape instance. $\bm{\bar{s}}$ is mean shape and $\bm{U}_s\bm{p}$ are eigenvectors with corresponding parameters $p$.
-
-\subsection{Fitting Results}
-\label{sec:daam_fittingresults}
-This section provides additional visualisations for the experiments of Section 3.3 of the main submission (Non-rigid object alignment in-the-wild).
-We visualise pixel-wise dense fitting results for both faces and ears.
-Results for this experiment of faces are reported over the 224 testing images of the LFPW database using 68 point ground truth landmark annotations
-\footnote{\label{ibug_300} \url{http://ibug.doc.ic.ac.uk/resources/300-W/}}.
-For ears, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in the paper.
-Results for fitting ears are reported over 105 testing images.
-
-Figure \ref{fig:fr} shows dense fitting results using a grid visualisation, thus dense points are visible without affecting the visibility of appearance.
-
-\subsection{Shape Model Analysis}
-\label{sec:modelanalysis}
+Figure \ref{fig:rc_face} evaluates the dense shape reconstruction ability of the proposed dAAMs and compares it with that of standard sparse AAMs. In more detail, we use shapes with dense 
+ground-truth annotations and we use both AAMs and dAAMs to reconstruct them, by projecting on the corresponding model subspace.
+In the case of AAMs, which only contain a sparse shape model, we densify it using a piecewise affine transformation, which is typically used in texture warping textures using this type of models.
+We observe that dAAMs significantly outperform classic AAMs, in terms of dense shape reconstruction accuracy.
 
@@
     \end{subfigure}
-    \caption{Dense shape reconstruction errors for ears and faces.
-Top: results of reconstruction on ears, bottom: results of reconstruction on faces.
-The normalised point-to-point error is used an evaluation measure.}
+    \caption{Dense shape reconstruction errors for ears (top) and faces (bottom), using AAMs (red) and dAAMs (blue).
+The average normalized dense point-to-point distance error is plotted as a function of the number of principal components of the model.}
     \label{fig:rc_face}
@@
 
-We first investigate the reconstruction accuracy of AAMs and dAAMs in the shape space.
-In particular, given a ground-truth shape, we use the shape models from both AAMs and dAAMs to reconstruct the given shape densely.
-Since AAMs contain a sparse shape model, we densify it using a piecewise affine transformation, which is typically used in warping textures on to shape model too.
-Figure \ref{fig:rc_face} shows plots of dense shape reconstruction errors for ears and faces, for varying number of principal components kept.
-We observe that dAAMs significantly outperform classic AAMs on shape reconstruction.
+\subsection{Dense Fitting Visualizations}
+\label{sec:daam_fittingresults}
 
-Furthermore, we explore the compactness of the built AAMs and dAAMs models.
-Figure \ref{fig:compact} demonstrates the variance explained as a function of the number of principal components.
-One can infer that dAAMs have a more compact shape model than AAMs, which leads to better reconstruction especially with few shape components.
+In this section,
+we visualize some characteristic examples of fitting
+dense Active Appearance Models that were built using the proposed framework.
+These results are characteristic examples that come from the quantitative evaluations and comparisons reported in Section 4.1 (``Non-rigid object alignment in-the-wild'') of the main submission.
+Figure \ref{fig:fr} shows dAAM fitting results using a grid visualisation, for both faces and ears.
+We observe that the proposed method successfully captures the shape deformations of these object classes and provides a detailed shape estimation for a variety of input images.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
+\caption{Examples of fitting
+dAAMs that are constructed with the proposed pipeline. Results of dense fitting on images of
+ ears (first two rows) and faces (last two rows). A grid visualisation is used.}
+\label{fig:fr}
+\end{figure}
+
+\section{Patch-based Active Appearance Modeling}
+\label{sec:paam}
+
+In this section, we present additional visualizations and evaluations for the patch-based Active Appearance Model (PAAM) of arms that was constructed using the proposed framework.
+
+\subsection{Subsampling of the Outline from Dense Correspondences}
+\label{sec:sparsesample}
 
@@
 \centering
-    \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/var_ratio}
-        %\caption{dAAMs vs AAMs Variance Ratio}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/cumu_var_ratio}
-        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
-    \end{subfigure}
-    \caption{Variance explained by each principal component, for both dAAM and AAM models.
-Top: variance explained by each principal component.
-Bottom: cumulative plot of the variance explained as a function of the principal components.}
-    \label{fig:compact}
+\newcommand{\ofh}{0.24\columnwidth}
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-0.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-1.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-2.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-3.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-4.png}
+\caption{Examples of sparse subsampling from dense shapes of arms.
+The dense correspondences (visualized via a deforming grid) are established using our shape flow estimation.
+The sparse landmarks (red dots) on the object outline are manually annotated only on the reference shape (left most image).
+In all other 5 example shapes, these landmarks have been automatically ``propagated'' using the established dense correspondences.}
+\label{fig:sparsesample}
 \end{figure}
 
-Finally, Figure \ref{fig:pcamodel} visualises the principal components of dAAMs for ears and faces. We observe that the variation of both shape and appearance captured by the model seem plausible.
+As mentioned in the main submission (Section 3 - Step 4), in order to train a PAAM, we subsample the  densified training shapes to only consider points on the object outline. 
+Some examples of this procedure are depicted in Figure~\ref{fig:sparsesample}. 
+We manually annotate sparse outline points only on the reference shape.
+Then all other training shapes are subsampled automatically exploiting the dense correspondences that are established with our shape flow estimation.
+We observe that the automatic sub-sampling seems plausible, which is attributed to the accurate estimations of dense correspondences.
 
-\section{Patch-based Active Appearance Model}
-\label{sec:paam}
+\subsection{Principal Components}
+\label{sec:paam_sm}
+
+Figure~\ref{fig:paam_sm} shows the mean shape and the first 4 principal components of shape variation of our PAAM for arms \footnote{Note that we do not visualize the appearance variation, since this is built using SIFT features and the corresponding 36-channel feature space cannot be visualized in an intuitive way.}.
+We observe that the shape variations captured by the model are plausible and seem to produce valid shapes of human arms.
+
+\begin{figure}[!b]
+\centering
+\includegraphics[width=\columnwidth]{Suplementory_Meterial/HandSMPAAM/handsmpaam}
+\caption{Principal components of our patch-based AAM for human arms.
+The mean (left most column) as well as the first four principal components are visualised.
+$\pm 3$ times the variance of the corresponding component is used in each case.}
+\label{fig:paam_sm}
+\end{figure}
+
+\subsection{Fitting Results}
+\label{sec:paam_fittingresults}
+
+Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
+All fittings are initialised using same method as mention in experiment 4.2 in main paper.
 
@@
 
-This section shows spares annotation of densely corespondent shapes are generated, since patch-based AMM support consistent parse annotation only in section~\ref{sec:sparsesample}.
-Also, shape model visualisation of build patch-based AMM are shown in section~\ref{sec:paam_sm}, as well as corresponding fitting result visualisation are shown in section~\ref{sec:paam_fittingresults}.
-
-\subsection{Subsampling Sparse Outline from Dense Correspondent Shapes}
-\label{sec:sparsesample}
-
-\begin{figure}[!b]
-\centering
-\newcommand{\ofh}{0.24\columnwidth}
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-0.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-1.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-2.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-3.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-4.png}
-\caption{Demonstration of sparse sampling from dense shapes.
-Left most image shows sparse sample on the reference shape while other 5 images shows projection from sampled reference shape to arbitrary shapes with dense correspondence.}
-\label{fig:sparsesample}
-\end{figure}
-
-As \emph{step 4} in main paper refers, patch-based AAM are suitable for fitting objects that interior appearance having no structure, in this case e.g.
-arms.
-But patch-based AAM require consistent sparse annotation.
-So a sub-sampling step is needed to meet such criteria.
-As we built dense correspondence between shapes, we only sparsely annotate one shape so rest shapes are sub-sampled automatically since sparse samples are preserved in all shapes by dense correspondence generated with shape flow.
-Figure~\ref{fig:sparsesample} shows sparse annotation (red dots) on dense mean shape (grid visualisation used for visibility) and exemplar projected samples on other shapes.
-
-\subsection{Patch-based AAM Shape Model}
-\label{sec:paam_sm}
-
-\begin{figure}[!b]
-\centering
-\includegraphics[width=\columnwidth]{Suplementory_Meterial/HandSMPAAM/handsmpaam}
-\caption{Principal components of patch-based AAM built on arms.
-The mean (left most column) as well asthe first four principal components are visualised with three times the variance of the corresponding component it used in each case.}
-\label{fig:paam_sm}
-\end{figure}
-
-Figure~\ref{fig:paam_sm} shows mean shape and corresponding $\pm 3$ variation on first four principle components.
-As the appearance model are built with SIFT feature, the 36-channel feature give no meaningful visualisation to human so we have not shown it.
-From arms shape model, we observe that the variation of shape captured by the model are reasonable.
-
-\subsection{Fitting Results}
-\label{sec:paam_fittingresults}
+In addition table~\ref{tab:hand_benchmark} presents statistics results that refers to experiment 4.2 in main paper for additional information.
+Column $\leq 6pt$ reports the percentage of fittings that having errors, point-to-point distance on normalised images, less than 6 pixels (same measurement used in \cite{pfister2015flowing}).
+This shows we have notable improvement on estimating wrists and comparable results on estimating elbow.
 
@@
 \end{table}
-
-Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
-All fittings are initialised using same method as mention in experiment 4.2 in main paper.
-
-In addition table~\ref{tab:hand_benchmark} presents statistics results that refers to experiment 4.2 in main paper for additional information.
-Column $\leq 6pt$ reports the percentage of fittings that having errors, point-to-point distance on normalised images, less than 6 pixels (same measurement used in \cite{pfister2015flowing}).
-This shows we have notable improvement on estimating wrists and comparable results on estimating elbow.
 

### 2015-11-18 supplementary.tex
Updates from ShareLaTeX

@@
 
+\begin{figure*}[!b]
+\centering
+\includegraphics[width=\textwidth]{Suplementory_Meterial/Models/models}
+\caption{Principal components of dAAMs built on ears (top) and faces (bottom).
+The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right).
+$\pm 3$ times the variance of the corresponding component is used in each case.}
+\label{fig:pcamodel}
+\end{figure*}
+
 %%%%%%%%% Appendix
 \section*{Introduction}
-In this supplementary material, we provide additional algorithmic details for our shape flow estimation, as well as additional visualizations and evaluations for the dense and patch-based AAMs that were constructed using the proposed framework.
+In this supplementary material, we provide additional algorithmic details for our shape flow estimation, as well as additional visualisations and evaluations for the dense and patch-based AAMs that were constructed using the proposed framework.
 
@@
 
-As mentioned in the main submission (Section 3, Step 3), we propose to estimate the shape flow by minimizing the following energy:
+As mentioned in the main submission (Section 3, Step 3), we propose to estimate the shape flow by minimising the following energy:
 \vspace{-5pt}
@@
 \end{align}
-We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$, which correspond to the
+We minimise this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$, which correspond to the
 two sets of unknown shape flows.
-We implement this minimization based on the optimization algorithm described in \cite{Garg:2013hu} and the relevant publicly available code \footnote{https://bitbucket.org/troussos/mfsf/downloads}.
+We implement this minimisation based on the optimisation algorithm described in \cite{Garg:2013hu} and the relevant publicly available code \footnote{https://bitbucket.org/troussos/mfsf/downloads}.
 However, we modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Section 3, Step 2 of the main submission.
@@
 
-Regarding more details on the optimization algorithm, 
-in every coarse-to-fine and warping iteration, we use an initialization that comes from the previous iteration.
-We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images $\bm{d}(\bx;n)$ around the initialization.
-After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
-The minimization w.r.t.~$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
-The minimization w.r.t.~$\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$.
-This minimization is also implemented by applying the efficient primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+Note that in every coarse-to-fine and warping iteration, we use an initialisation that comes from the previous iteration.
+We approximate the data term \eqref{eq:costfunc} by linearising the SVS images $\bm{d}(\bx;n)$ around the initialisation.
+After that, the energy becomes convex and we optimise it by employing alternating optimisation with respect to $\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
+The minimisation with respect to $\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising~\cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of~\cite{Chambolle:Pock:JMIV2011}.
+The minimisation with respect to $\bm{u}_n(x)$ is decoupled for every pixel $\bx$ and every shape index $i$.
+This minimisation is also implemented by applying the efficient primal-dual algorithm of~\cite{Chambolle:Pock:JMIV2011}.
 
-\section{Dense Active Appearance Modeling}
+\section{Dense Active Appearance Models}
 \label{sec:daam}
 
-In this section, we report additional qualitative and quantitative evaluations and comparisons for the dAAMs of faces and ears that were constructed using the proposed framework.
+In this section, we report additional qualitative and quantitative evaluations for the Dense Active Appearance Models (dAAMs) of faces and ears that were constructed using the proposed framework.
 
@@
 
-Figure \ref{fig:pcamodel} visualizes some of the shape and appearance principal components of the built dAAMs for ears and faces.
-We observe that in both ears and faces, the variation of both shape and appearance captured by the model seem plausible.
+Figure~\ref{fig:pcamodel} visualises the first five shape and appearance principal components of ear and face dAAMs.
+We observe that in both ear and face cases, the variation of both shape and appearance captured by the model seem plausible.
 
-\begin{figure*}[!t]
-\centering
-\includegraphics[width=\textwidth]{Suplementory_Meterial/Models/models}
-\caption{Principal components of dAAMs built on ears (top) and faces (bottom).
-The mean (middle columns) as well as the first five principal components are visualised for both shape (left) and appearance (right).
-$\pm 3$ times the variance of the corresponding component is used in each case.}
-\label{fig:pcamodel}
-\end{figure*}
-
-Figure \ref{fig:compact} shows the compactness plot for our dAAM for faces and compares it with the corresponding plot for a standard sparse AAM built on the same data.
-Note that these are the two shape models that are compared in Figure 9-left of the main submission.
+Figure~\ref{fig:compact} pliots the variance ration of the face dAAM, which provides an indication of the compactness of the model.
+The compactness is compared with the one of a standard sparse AAM built on the same data.
+Note that these are the two shape models that are compared in Figure 9-left of the main paper.
 We observe that our dAAM is significantly more compact than the sparse AAM, since for any given number of components, it manages to explain a larger portion of the corresponding total variance of the training set.
 
-\begin{figure}[!b]
+\begin{figure}[!t]
     \centering
-%    \begin{subfigure}[b]{0.43\textwidth}
-%            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/var_ratio}
-%        %\caption{dAAMs vs AAMs Variance Ratio}
-%    \end{subfigure}
-    \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/cumu_var_ratio}
-        %\caption{dAAMs vs AAMs Cumulative Variance Ratio}
-    \end{subfigure}
+    \includegraphics[width=\columnwidth]{Suplementory_Meterial/Model_Analysis/cumu_var_ratio}
     \caption{Compactness plots of dAAM (green) and sparse AAM (blue) models for faces.
@@
 
-Figure \ref{fig:rc_face} evaluates the dense shape reconstruction ability of the proposed dAAMs and compares it with that of standard sparse AAMs. In more detail, we use shapes with dense 
-ground-truth annotations and we use both AAMs and dAAMs to reconstruct them, by projecting on the corresponding model subspace.
-In the case of AAMs, which only contain a sparse shape model, we densify it using a piecewise affine transformation, which is typically used in texture warping textures using this type of models.
-We observe that dAAMs significantly outperform classic AAMs, in terms of dense shape reconstruction accuracy.
-
-\begin{figure}[!b]
+\begin{figure}[!t]
     \centering
     % \vspace*{-0.1in}
-    \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/sr_ear}
+    \begin{subfigure}[b]{\columnwidth}
+            \includegraphics[width=\textwidth,trim={0 0 0 25pt},clip]{Suplementory_Meterial/Model_Analysis/sr_ear}
         %\caption{dAAMs dense shape reconstruction}
@@
     \\
-    \begin{subfigure}[b]{0.43\textwidth}
-            \includegraphics[width=\textwidth]{Suplementory_Meterial/Model_Analysis/sr_face}
+    \begin{subfigure}[b]{\columnwidth}
+            \includegraphics[width=\textwidth,trim={0 0 0 25pt},clip]{Suplementory_Meterial/Model_Analysis/sr_face}
         %\caption{AAMs dense shape reconstruction}
@@
 
-\subsection{Dense Fitting Visualizations}
-\label{sec:daam_fittingresults}
-
-In this section,
-we visualize some characteristic examples of fitting
-dense Active Appearance Models that were built using the proposed framework.
-These results are characteristic examples that come from the quantitative evaluations and comparisons reported in Section 4.1 (``Non-rigid object alignment in-the-wild'') of the main submission.
-Figure \ref{fig:fr} shows dAAM fitting results using a grid visualisation, for both faces and ears.
-We observe that the proposed method successfully captures the shape deformations of these object classes and provides a detailed shape estimation for a variety of input images.
-
-\begin{figure}[!t]
-\centering
-\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
-\caption{Examples of fitting
-dAAMs that are constructed with the proposed pipeline. Results of dense fitting on images of
- ears (first two rows) and faces (last two rows). A grid visualisation is used.}
-\label{fig:fr}
-\end{figure}
-
-\section{Patch-based Active Appearance Modeling}
-\label{sec:paam}
-
-In this section, we present additional visualizations and evaluations for the patch-based Active Appearance Model (PAAM) of arms that was constructed using the proposed framework.
-
-\subsection{Subsampling of the Outline from Dense Correspondences}
-\label{sec:sparsesample}
-
-\begin{figure}[!b]
-\centering
-\newcommand{\ofh}{0.24\columnwidth}
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-0.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-1.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-2.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-3.png}
-    \hfill
-    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-4.png}
-\caption{Examples of sparse subsampling from dense shapes of arms.
-The dense correspondences (visualized via a deforming grid) are established using our shape flow estimation.
-The sparse landmarks (red dots) on the object outline are manually annotated only on the reference shape (left most image).
-In all other 5 example shapes, these landmarks have been automatically ``propagated'' using the established dense correspondences.}
-\label{fig:sparsesample}
-\end{figure}
-
-As mentioned in the main submission (Section 3 - Step 4), in order to train a PAAM, we subsample the  densified training shapes to only consider points on the object outline. 
-Some examples of this procedure are depicted in Figure~\ref{fig:sparsesample}. 
-We manually annotate sparse outline points only on the reference shape.
-Then all other training shapes are subsampled automatically exploiting the dense correspondences that are established with our shape flow estimation.
-We observe that the automatic sub-sampling seems plausible, which is attributed to the accurate estimations of dense correspondences.
-
-\subsection{Principal Components}
-\label{sec:paam_sm}
-
-Figure~\ref{fig:paam_sm} shows the mean shape and the first 4 principal components of shape variation of our PAAM for arms \footnote{Note that we do not visualize the appearance variation, since this is built using SIFT features and the corresponding 36-channel feature space cannot be visualized in an intuitive way.}.
-We observe that the shape variations captured by the model are plausible and seem to produce valid shapes of human arms.
-
-\begin{figure}[!b]
-\centering
-\includegraphics[width=\columnwidth]{Suplementory_Meterial/HandSMPAAM/handsmpaam}
-\caption{Principal components of our patch-based AAM for human arms.
-The mean (left most column) as well as the first four principal components are visualised.
-$\pm 3$ times the variance of the corresponding component is used in each case.}
-\label{fig:paam_sm}
-\end{figure}
-
-\subsection{Fitting Results}
-\label{sec:paam_fittingresults}
-
-Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms datasets including MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
-All fittings are initialised using same method as mention in experiment 4.2 in main paper.
+Figure \ref{fig:rc_face} evaluates the dense shape reconstruction ability of the proposed dAAMs and compares it with that of standard sparse AAMs.
+Specifically, we use shapes with dense ground-truth annotations and reconstruct them with both AAMs and dAAMs, by projecting on the corresponding model subspace.
+In the case of AAMs, which only contain a sparse shape model, we densify it using a piecewise affine transformation, which is typically for texture warping of these models.
+We observe that dAAMs significantly outperform classic AAMs, in terms of dense shape reconstruction accuracy.
 
@@
 
-In addition table~\ref{tab:hand_benchmark} presents statistics results that refers to experiment 4.2 in main paper for additional information.
-Column $\leq 6pt$ reports the percentage of fittings that having errors, point-to-point distance on normalised images, less than 6 pixels (same measurement used in \cite{pfister2015flowing}).
-This shows we have notable improvement on estimating wrists and comparable results on estimating elbow.
+\subsection{Dense Fitting Visualizations}
+\label{sec:daam_fittingresults}
 
-\begin{table}[t!]
-    \small
+In this section, we visualise some characteristic examples of fitting
+dAAMs that were built using the proposed framework.
+These results are characteristic examples that come from the quantitative evaluations reported in Section 4.1 (``Non-rigid object alignment in-the-wild'') of the main paper.
+Figure \ref{fig:fr} shows dAAM fitting results using a grid visualisation, for both faces and ears.
+We observe that the proposed method successfully captures the shape deformations of these object classes and provides a detailed shape estimation for a variety of input images.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fittings/fittings}
+\caption{Examples of fitting
+dAAMs that are constructed with the proposed pipeline. Results of dense fitting on images of
+ ears (first two rows) and faces (last two rows). A grid visualisation is used.}
+\label{fig:fr}
+\end{figure}
+
+\section{Patch-based Active Appearance Models}
+\label{sec:paam}
+
+In this section, we present additional visualisations and evaluations for the patch-based Active Appearance Model (PAAM) of arms that was constructed using the proposed framework.
+
+\subsection{Subsampling of the Outline from Dense Correspondences}
+\label{sec:sparsesample}
+
+\begin{figure}[!t]
+\centering
+\newcommand{\ofh}{0.24\columnwidth}
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-0.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-1.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-2.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-3.png}
+    \hfill
+    \includegraphics[height=\ofh]{Suplementory_Meterial/SparseSamples/mean-4.png}
+\caption{Examples of sparse subsampling from dense shapes of arms.
+The dense correspondences (visualized via a deforming grid) are established using our shape flow estimation.
+The sparse landmarks (red dots) on the object outline are manually annotated only on the reference shape (left most image).
+In all other 5 example shapes, these landmarks have been automatically ``propagated'' using the established dense correspondences.}
+\label{fig:sparsesample}
+\end{figure}
+
+\begin{table*}[t!]
     \centering
@@
     \label{tab:hand_benchmark}
-\end{table}
+\end{table*}
+
+As mentioned in the main paper (Section 3 - Step 4), in order to train a PAAM, we subsample the densified training shapes to only consider points on the object's outline.
+Some examples of this procedure are depicted in Figure~\ref{fig:sparsesample}.
+We manually annotate sparse outline points only on the reference shape.
+Then all other training shapes are subsampled automatically exploiting the dense correspondences that are established with our shape flow estimation.
+We observe that the automatic subsampling seems plausible, which is attributed to the accurate estimations of dense correspondences.
+
+\subsection{Principal Components}
+\label{sec:paam_sm}
+
+Figure~\ref{fig:paam_sm} shows the mean shape and the first 4 principal shape components of our PAAM for arms\footnote{Note that we do not visualise the appearance variation, since this is built using SIFT features and the corresponding 36-channel feature space cannot be visualised in an intuitive way.}.
+We observe that the shape variations captured by the model are plausible and seem to produce valid shapes of human arms.
+
+\begin{figure}[!t]
+\centering
+\includegraphics[width=\columnwidth]{Suplementory_Meterial/HandSMPAAM/handsmpaam}
+\caption{Principal components of our patch-based AAM for human arms.
+The mean (left most column) as well as the first four principal components are visualised.
+$\pm 3$ times the variance of the corresponding component is used in each case.}
+\label{fig:paam_sm}
+\end{figure}
+
+\subsection{Fitting Results}
+\label{sec:paam_fittingresults}
+
+Figure~\ref{fig:paam_fittingresults} demonstrates more fitting results produced by fitting patch-base AAM on arms using MPII~\cite{andriluka14cvpr}, Fashion Pose~\cite{dantone2013human}, FLIC~\cite{sapp2013modec} and BBC Pose~\cite{pfister2015flowing} databases.
+All fittings are initialised using the same method as mentioned in section 4.2 of the main paper.
+
+In addition table~\ref{tab:hand_benchmark} reports statistical measures that provide additional information to section 4.2 of the main paper.
+Column $\leq 6pt$ reports the percentage of fittings that achieved a point-to-point normalised error less than 6 pixels (same measure used in \cite{pfister2015flowing}).
+This shows that we have notable improvement on estimating wrists and comparable results on estimating the elbow.
 

### 2016-01-27 rebuttal/egrebuttal.tex
Rebuttal Final

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr_rebuttal}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{0008} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\setlength{\parindent}{0pt}

\usepackage{caption}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Estimating Correspondences of Deformable Objects ``In-the-wild"}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We thank all Reviewers for their valuable feedback. Both Reviewers 24 and 25 (R24, R25) accept the paper (R24 strongly accepts it by acknowledging its potential impact). However, Reviewer 23 (R23) is reserved, but in the same time thinks it is ``interesting and quite novel''. It goes without saying that all minor comments will be implemented in the revised manuscript (including suggested references).  %Note that in what follows, all citations correspond to references of the original paper submission.

% EFFECT OF CORRECTED FOREARM ANNOTATIONS
\textbf{[R23] Are our annotations better? How the annotations affect the final performance?}
The only way to show that our annotations are more accurate than existing ones is by providing qualitative results and visual inspection (c.f.~Fig.7). In general, it is impossible to quantitatively compare the quality between different annotation sets, because there are no annotations that could be considered as ground truth.  Furthermore, in supervised learning better and more consistent annotations always lead to better models. An example of that is demonstrated in Fig.~A1, where the same algorithm, a cascade regression method, is learnt from noisy annotations (from crowd-sourcing) and from consistent annotations by our method. The quantitative experiments are performed on the widely used BBC Pose database because it has by far the most accurate annotations compared to the rest databases (FLIC, MPII etc.). As mentioned in the paper, we will provide all  corrected landmarks to the community upon acceptance.

% HUMAN EFFORT COMPARED TO HUMAN ANNOTATION
\textbf{[R23, R24] Human annotation effort.}
From our experience, the manual annotation of the body parts requires about 2 minutes per image. Thus, the manual annotation of FLIC database that includes about 20k images would require about 667 human working hours. On the contrary, our system requires the annotation of a few hundred images. The manual annotation of 700 such images took about 23 hours of human effort. Then these annotations were used by our pipeline to generate landmarks for all the FLIC images (and many other images). Additionally, according to an experiment we conducted, annotating images of faces and ears in terms of landmarks requires about 8.5 and 6.8 minutes respectively, while only 42 and 38 seconds are required to annotate them w.r.t.~curves. It becomes evident that the human effort required by our system is much smaller.

% building dense AAMs of patch-based AAMs with our pipeline cost 30 minutes for training with 600 images and fitting models cost the same time as normal AAM does. In our cases 5s for each fitting. Also, curve annotation requires much less effort, according to our experiment, putting landmarks on faces and ears requires 511s and 408s for each image including quality control, while only 42s and 38s need for annotating with curves.

% Manually annotating MPII (40K candidates), FLIC (20K+ candidates) require approximately 40K, 20K minutes correspondingly, while annotating using base line requires 700 minutes manually annotation + 40 minutes building time + 5s fitting time for each image. So 4K minutes and 2.3K minutes required for annotating entire MPII and FLIC dataset.

% FOCUS ON WRIST AND ELBOW
\textbf{[R23, R25] Body parts considered.} 
We  focus on the wrist and elbow because they are the most challenging body parts. R23 mentions that the hip and head are the most inconsistent body parts, but we disagree: Both LSP and MPII datasets report lower detection rates on wrist (MPII: 77\%, LSP: 79\%) and elbow (MPII: 84\%, LSP: 84\%), compared to hip (MPII: 83\%, LSP: 93\%) and head (MPII, LSP: 96\%)~[5]. In addition, the recently published system by Google (DeepPose) focuses on the elbow and wrist, which further demonstrates the challenges of these body parts and the interest they have attracted by the current state of the art. Also, Fig.6 demonstrates that elbow and wrist are the most noisily annotated points. Especially for the head, we believe it is very easy to accurately detect it, given the advances in head detection. In any case, our plan is to extend this work to include more parts (torso etc.), as well as a full body model, as suggested by R25.

% ARE OUR LANDMARKS CONSIDERED GROUNDTRUTH
%\textbf{[R23] Can our landmarks be considered as groundtruth?} As shown in our %qualitative results (figure 7), our landmarks are, in most cases, much more %accurate than the existing landmarks. Figure~\ref{fig:noise_fitting} shows some %indicative results of fitting a model trained on our landmarks and on noisy %landmarks (crow. The results are very indicative of the impact that more accurate 5annotations could have to the effectiveness of an SDM.

% INITIALISATION OF FOREARM FITTING
\textbf{[R23, R25] Initialisation of forearm fitting.}
It is initialised with our in-house implementation of a 
CNN pose estimation system, similar to~[41]. We remark that for a point-to-point error of 10, we get an improvement of about 10-15\% (in absolute terms, i.e. our method has 88\% at 10, while initilisation is at 73\%) for both wrist and elbow. In the final version of the paper, the initialisation CED curves will be included in Fig.10 (they are close to the yellow lines).
%Figure~\ref{fig:hand_benchmark} shows the results along with the initialisation curve, as requested.
%%
\begin{figure}[t!]
    \newcommand{\ofh}{0.24\columnwidth}
    \centering
    \includegraphics[height=\ofh]{face_all}
    \includegraphics[height=\ofh]{face2_all}
    \includegraphics[height=\ofh]{arm_all}
    \includegraphics[height=\ofh]{arm2_all}
    \caption*{Figure A1. Visualisation of fitting models (faces and forearms) trained with noisy annotation (blue dots) and trained with consistent annotation (green dots).}
    \label{fig:noise_fitting}
    \vspace{-14pt}
\end{figure

% LFPW EXPERIMENT
\textbf{[R23] Facial experiment on LFPW dataset.}
Unfortunately, LFPW database does not provide the actual images but only the original hyperlinks (from news-cites etc.) to them and currently most of them are inactive. We got the 224 from the authors of [24] who managed to download them 3 years ago. To keep it simple we have used state-of-the art AAMs such as [1,52] but on pixel intensities. State of the art includes the same methods but with image features such as HoGs [1,52] (in the revised paper, in Fig. 9, we will include AAMs on features).

% PERFORMANCE ANALYSIS OF PROPOSED METHOD'S COMPONENTS
\textbf{[R23, R24, R25] Performance analysis of each component is missing. Difficult to implement.} 
Unfortunately, due to limited space we could not show the effect of all parameters involved in the pipeline. We plan to make such an analysis on a journal extension of this work. Nevertheless, we are committed to make the whole pipeline publicly available. 
% , as done with all software developed in our group,

\textbf{[R25] Full body model.} Currently, our aim, starting with arms, is to create contour models for each body part. Then, we are thinking of creating an articulated model that connects each of them, but this is future work on the topic.

\textbf{[R25] Dimension of the $\mathbf{q}_i$ vector.} 
Every $\mathbf{q}_i$ is a sequence of 2D displacement vectors. It maps the image index $n$ ($n=1,..,N_t$ ) to a 2D vector 
$\mathbf{q}_i(n)$.  
Equivalently, $\mathbf{q}_i$ can be seen as a $2 N_t$ - dimensional vector, containing the displacements for all training images. 
%that correspond to the $i$-th basis element.

 %We plan to make such an analysis on a journal extension of this work. We refer the %Reviewer to the relevant bibliography of each component (SVS [39], NICP [3], Flow %[27], dAAM [2], patch AAM [52]).

%\begin{figure}[t!]
%    \centering
%    \includegraphics[width=0.48\columnwidth]{noise2}
%    \caption{Benchmark between AAM trained with consistant and noisy data}
%    \label{fig:noise}
%\end{figure}

% \textbf{[R23, R25] Effort of complete contour annotation of the forearm}. In the case of forearm, taking only two points into account actually requires slightly more effort. But for usecase that requires more points, our pipeline will be much faster. Moreover, contour annotation can work with semantic segmentation which can make the pipeline fully automatic (boundary of semantic segmentation gives contours needed).

% \textbf{[R23, R25] Manual effort spent on obtaining richer annotation worth ... SDM can be built with less effort does not seem to apply to the lower arm model ... }

%{\small
%\bibliographystyle{ieee}
%\bibliography{bib}
%}

\end{document}

### 2016-01-27 rebuttal/other_rebuttal.tex
Rebuttal Final

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr_rebuttal}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{89} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\setlength{\parindent}{0pt}

\usepackage{caption}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Dynamic Probabilistic Linear Discriminant Analysis}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We thank Reviewers (R) 10 and 22 for their valuable feedback. R10 ("A good paper") and R22 ("The proposed methods are clearly derived from sound mathematical principles") are positive regarding the paper. R13 strongly rejects the paper (being very confident), even though it is evident that he/she is not knowledgeable at all regarding the field (probabilistic machine learning). We kindly request the assistance of the Area Chair on that.    %Note that in what follows, all citations correspond to references of the original paper submission.

\textbf{[R10] Regarding Typos. }. Since, submission we have thoroughly edited the text to spot and correct all typos. An extended supplementary material will also accompany the paper (may it be accepted).

\textbf{[R10] The authors should provide some experiments regarding the training time of the model}. Since, the methods scale linearly with regards to number of videos, frames, people etc. it is quite fast to train and test them. For example for the largest training set it takes few minutes to train (not more than 10 mins using un-optimised Matlab code). Testing, if carefully implemented, can be performed real-time. Detailed complexity evaluations will be included for each individual experimental setup.

\textbf{[R10] The authors should consider comparisons of the proposed model with some other previous works like [20], [21].}. [20] is a CCA model that cannot be used for classification but for identifying shared structures. [21] proposes a unified view on probabilistic techniques. The only technique form [21] that is relevant is an alternative static PLDA which will include in the revised manuscript (performance very close to the tested static PLDA).

% EFFECT OF CORRECTED FOREARM ANNOTATIONS
\textbf{[R13] How correlation are found if $\mathbf{A}=0.98\mathbf{I}$? If $A_{ij}$ very close to 1, how to differentiate $W_{ij}^t$ and $W_{ij}^{t+1}$? In Eq.(19), how to define the value of $A_{ij}$?}
First we would like to explain that $\mathbf{A}=0.98\mathbf{I}$ is used ONLY to PRODUCE artificial data in section 4.1 (a legitimate choice though, since it corresponds to a Slow feature dynamical system \cite{turner2007maximum}). In all experiments $\mathbf{A}_{ij}$ is found from the data through the application of the EM algorithm (standard practise, see 444-454). We refer the reviewer to standard textbooks \cite{bishop2006pattern} and tutorial papers \cite{roweis1999unifying} for further details on Linear Dynamical Systems (LDS).

% HUMAN EFFORT COMPARED TO HUMAN ANNOTATION
\textbf{[R13] In Eq.(1), what the meaning of $\mathbf{y}_i$? There is no explanation in Section 2.1.. In Eq.(7), what is $Dy$ means? There is also no explanation in this section. etc.}
There is a clear explanation in 181-184 of the original paper. Unfortunately, we do not have space to describe in full detail standard models such as PPCA. Again we refer R13 to  \cite{bishop2006pattern,roweis1999unifying}. Equation (7) is a condensed form of equation (6) (it is easy to make the association between variables).

% building dense AAMs of patch-based AAMs with our pipeline cost 30 minutes for training with 600 images and fitting models cost the same time as normal AAM does. In our cases 5s for each fitting. Also, curve annotation requires much less effort, according to our experiment, putting landmarks on faces and ears requires 511s and 408s for each image including quality control, while only 42s and 38s need for annotating with curves.

% Manually annotating MPII (40K candidates), FLIC (20K+ candidates) require approximately 40K, 20K minutes correspondingly, while annotating using base line requires 700 minutes manually annotation + 40 minutes building time + 5s fitting time for each image. So 4K minutes and 2.3K minutes required for annotating entire MPII and FLIC dataset.

% FOCUS ON WRIST AND ELBOW
\textbf{[R13] Some state-of-the-art methods for YouTube face database, FERA database should also be compared in this section.} 
Comparisons exist in the original paper (please see 691-701 and 782-786). We will summarise them in a Table.

% ARE OUR LANDMARKS CONSIDERED GROUNDTRUTH
%\textbf{[R23] Can our landmarks be considered as groundtruth?} As shown in our %qualitative results (figure 7), our landmarks are, in most cases, much more %accurate than the existing landmarks. Figure~\ref{fig:noise_fitting} shows some %indicative results of fitting a model trained on our landmarks and on noisy %landmarks (crow. The results are very indicative of the impact that more accurate 5annotations could have to the effectiveness of an SDM.

% INITIALISATION OF FOREARM FITTING
\textbf{[R22]  The authors do not compare their techniques to any of the competing techniques that could be trained on the same data sets such as LBP, Convolutional Neural Networks or Support Vector Machines using Gabor filters or Gaussian Derivatives.}
The aim of the experiments were to show that our general machine learning methodology performs close to state-of-the-art even though combined with very simple features (IGO features).  Nevertheless, we compare with state-of-the-art techniques in 691-701 that use elaborate features.
Since, our method is a generic machine learning tool it can be used on top of arbitrary features (e.g. LBP and Gabor filters). For example we have now performed experiments using HoG and LBP features and the results have improved a lot.

% LFPW EXPERIMENT
\textbf{[R23] Deep learning versus probabilistic methods.}
We agree with R23 that when a lot of data are available deep learning techniques can provide a good alternative. This is true for face recognition. But for facial expression recognition (FERA experiments) to the best of our knowledge there is no competing deep network proposed yet. We would like to note that DCNNs provide mainly good features which can be combined with any classification technique (including ours).

% PERFORMANCE ANALYSIS OF PROPOSED METHOD'S COMPONENTS
\textbf{[R22] There are very large data sets , such as the CASIA Webface data set (10,575 subjects and 494,414 images), that are available for deep learning techniques.} 
We agree that CASIA database is a valuable source of data (we will cite CASIA in the revised version). Nevertheless, it does not provide the amount of data necessary to match the performance of FaceNet by Google (200 Million) or DeepFace by FaceBook.

% , as done with all software developed in our group,

\textbf{[R10-R25] Description of state-of-the-art (R25) and a table (R10).} We will include a table in the revised paper summarising all the state-of-the-art techniques, as well as further description in the text.

Finally, it goes without saying that all minor comments will be addressed. Also, we have already made steps towards making the code publicly available.

 %We plan to make such an analysis on a journal extension of this work. We refer the %Reviewer to the relevant bibliography of each component (SVS [39], NICP [3], Flow %[27], dAAM [2], patch AAM [52]).

%\begin{figure}[t!]
%    \centering
%    \includegraphics[width=0.48\columnwidth]{noise2}
%    \caption{Benchmark between AAM trained with consistant and noisy data}
%    \label{fig:noise}
%\end{figure}

% \textbf{[R23, R25] Effort of complete contour annotation of the forearm}. In the case of forearm, taking only two points into account actually requires slightly more effort. But for usecase that requires more points, our pipeline will be much faster. Moreover, contour annotation can work with semantic segmentation which can make the pipeline fully automatic (boundary of semantic segmentation gives contours needed).

% \textbf{[R23, R25] Manual effort spent on obtaining richer annotation worth ... SDM can be built with less effort does not seem to apply to the lower arm model ... }

{\small
\bibliographystyle{ieee}
\bibliography{egbib}
}

\end{document}

### 2016-04-06 contents/introduction.tex
Updates from ShareLaTeX
Rebuttal Final

@@
 We employ the proposed method in order to construct SDMs based on the outline of human body parts (i.e., arms and legs).
-To the best of our knowledge, this is the first time that an SDM is proposed to be trained on the outline of human body parts and not on their skeleton joints.
+While majority of proposed SDMs for human poses are trained on skeleton joints, training SDMs based on outline of human body parts have shown remarkable advantages~\cite{zuffi2012pictorial} (?).
 The proposed SDM can also be used to provide accurate and consistent annotations for several of the body joints (such as wrist, elbow etc.).
-
 To this end, we argue and empirically demonstrate that it is better to annotate an object with regards to a set of continuous lines that describe its shape.
@@
 It becomes evident that the curve annotations avoid the inherent ambiguity of placing sparse landmarks and offer a richer description of the object's shape.
-%
-%where the shape of the human arm is annotated with continuous lines instead of a number of discrete landmarks.
-Similarly, the shape annotations for an ear and a face are shown in the same figure.
-Annotating images by following this procedure takes 42, 38 and 43 secs per image for arm, faces, ears correspondingly.
+
 Furthermore, these curves can be automatically generated by recently proposed methods that perform discriminative segmentation of objects \cite{luo2013pedestrian,liu2015matching}.
@@
 Therefore, we introduce appropriate modifications based on the consistency of image-based shape representation, as well as low rank priors.
-%
-%On the other hand,  while shapes having no motion smoothness completely as all training data are independent. Low rank constrain plays important role to simulate motion smoothness assumption.
 
@@
 
-%To the best of our knowledge this is the first methodology which can %create a dense statistical model for AAM which can operate in %"in-the-wild".
-
-%[..]. There are methods such as [..] and [..] but ...
-
-In summary, the contributions of this paper are the following:
+In summary, the contributions of this paper are:
 \begin{itemize}
@@
   \item We report state-of-the-art quantitative and qualitative results on the task of human body parts localisation by employing a patch-based SDM trained on the outline landmarks that are sampled by the dense correspondences.
-Our proposed model outperforms all current state-of-the-art techniques that are trained on skeleton joints
+Our proposed model outperforms all current state-of-the-art techniques that are trained on skeleton joints.
 

### 2016-04-06 contents/introduction.tex
repo cleanup

@@
 Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
-Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014}.
+Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014, kazemi2014one, zhu2015face, antonakos2015feature, antonakos2015active, Joan_cvpr2015, tzimiropoulos2015project}.
 This is attributed to:
@@
 
-\item The manual annotation of such databases that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,charles2013domain,dantone2014body,andriluka14cvpr}.
+\item The manual annotation of such databases that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,sagonas2016faces,charles2013domain,dantone2014body,andriluka14cvpr}.
 

### 2016-04-06 contents/introduction.tex
adds more citations

@@
 
-Statistical Deformable Models (SDMs) of various object classes is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
-Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014, kazemi2014one, zhu2015face, antonakos2015feature, antonakos2015active, Joan_cvpr2015, tzimiropoulos2015project}.
+Statistical Deformable Models (SDMs) of various objects is a well-studied and popular area in the intersection of computer vision and machine learning \cite{Cootes1995, Cootes2001, Matthews2004, Saragih2011, Belhumeur2011, Zhu2012, Xiong2013}.
+Recently, we have witnessed tremendous developments on SDMs of human faces and bodies trained with images that are captured under unconstrained conditions, usually referred to as ``in-the-wild" \cite{Belhumeur2011, Cao2012, Zhu2012, Xiong2013, Asthana2013, Tzimiropoulos2014, Asthana2014, kazemi2014one, Alabort2014, zhu2015face, antonakos2015feature, antonakos2015active, Joan_cvpr2015, tzimiropoulos2015project}.
 This is attributed to:

### 2016-04-07 contents/implementation.tex
Updates from ShareLaTeX
Final
minor changes and acknowledgments

@@
 
+\vspace{0.2cm}
 %\subsection{Correspondence Basis for Shape Flow Estimation}
@@
 Using the constructed correspondence basis, the shape flow can be approximated as:
+\vspace{-5pt}
 \begin{equation}\label{eq:LinTrajModel}
@@
     \textstyle \, \sum_{i=1}^R \, \bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
+\vspace{-5pt}
 \end{equation}
@@
     \centering
-    \includegraphics[width=0.4\textwidth]{resources/models}
-    \caption{Exemplar dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
+    \includegraphics[width=0.9\columnwidth]{resources/models}
+    \caption{Dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
     \label{fig:dense_models}
@@
 
-\begin{figure*}[t!]
-\begin{center}
- \begin{tabular}{ccc}
-\subfigure[]{
-    \newcommand{\flowh}{0.12\columnwidth}
-    \includegraphics[height=\flowh]{resources/Fig_Flows/1}
-    \includegraphics[height=\flowh]{resources/Fig_Flows/2}
-    \includegraphics[height=\flowh]{resources/Fig_Flows/3}
-    \includegraphics[height=\flowh]{resources/Fig_Flows/4}
-    \includegraphics[height=\flowh]{resources/Fig_Flows/5}
-    \includegraphics[height=\flowh]{resources/Fig_Flows/6}
-} &
-\subfigure[]{
-    \includegraphics[width=0.2\textwidth]{resources/models}
-}
- \end{tabular}
-\end{center}
-\caption{(a) . (b) }
-\label{REC}
-\end{figure*}
-
 % ---------------------------------------------------------------------------------------------------------------------------------------------------
-
+\vspace{0.3cm}
 {\refstepcounter{steps}\label{sec:step3}\subsection*{Step 3: Shape Flow Estimation}}
@@
 Following \cite{Garg:2013hu}, we propose to estimate the shape flow over all training images by minimizing the following energy:
+\vspace{-5pt}
 \begin{align}
@@
 \int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
+\vspace{-5pt}
 \end{align}
@@
 %We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$.
-The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
+%The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
 
@@
 
+\vspace{0.3cm}
 {\refstepcounter{steps}\label{sec:step4}\subsection*{Step 4: Dense and Patch-Based Deformable Models}}

### 2016-04-07 contents/introduction.tex
minor changes and acknowledgments

@@
 
-\item The manual annotation of such databases that has been undertaken by several research teams \cite{sagonas_iccv_300w_2013,sagonas2016faces,charles2013domain,dantone2014body,andriluka14cvpr}.
+\item The manual annotation of such databases that has been undertaken by several research teams \cite{sagonas2016faces,charles2013domain,dantone2014body,andriluka14cvpr}.
 
@@
 Another such example is the human body, which is generally annotated with regards to a number of landmarks that intuitively correspond to a set of body joints.
-For most body pose databases, annotation task was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
-Unfortunately, this resulted in acquiring inconsistent and inaccurate annotations, in many cases\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot, by any means, be compared with the ones provided by the recent 300W competition \cite{sagonas_iccv_300w_2013}.} (please see Figure \ref{fig:wrong_anno}).
+For most body pose databases, the annotation task was undertaken by a crowd-sourcing Internet marketplace, so-called Amazon Mechanical Turk (AMT).
+Unfortunately, this resulted in acquiring inconsistent and inaccurate annotations, in many cases\footnote{In the case of faces, the quality of annotations produced from AMT are extremely inaccurate and cannot, by any means, be compared with the ones provided by the recent 300W competition \cite{sagonas_iccv_300w_2013,sagonas2016faces}.} (please see Figure \ref{fig:wrong_anno}).
 As it was also recently pointed out \cite{tompson2015efficient}, the inconsistencies in body joint annotations may also render the comparison between different human pose estimation methodologies irrelevant.
@@
 This means that the annotation of 1000 images requires a total of about 67 hours.
-Furthermore, the quality of training as well as fatigue largely influence the annotation accuracy.
+Furthermore, the quality of training as well as fatigue greatly influence the annotation accuracy.
 Hence, a second pass on the annotated data is, in many cases, necessary.
@@
 We employ the proposed method in order to construct SDMs based on the outline of human body parts (i.e., arms and legs).
-While majority of proposed SDMs for human poses are trained on skeleton joints, training SDMs based on outline of human body parts have shown remarkable advantages~\cite{zuffi2012pictorial} (?).
 The proposed SDM can also be used to provide accurate and consistent annotations for several of the body joints (such as wrist, elbow etc.).
@@
 It becomes evident that the curve annotations avoid the inherent ambiguity of placing sparse landmarks and offer a richer description of the object's shape.
-
+%
 Furthermore, these curves can be automatically generated by recently proposed methods that perform discriminative segmentation of objects \cite{luo2013pedestrian,liu2015matching}.
+%
+Note that the work in~\cite{zuffi2012pictorial} is the only one that shows that training SDMs based on the outline contours of the human body parts has considerable advantages compared to using the sparse skeleton joints, as done by the majority of existing SDMs for human pose.
 
@@
 Specifically, we explain how to build powerful dense SDMs that are suitable for objects that have rich interior texture but lack landmarks consistency.
-Furthermore, we show how to build a powerful patch-based SDMs on the sparse outline landmarks of objects that do not have semantically meaningful interior textures.
+Furthermore, we show how to build a powerful patch-based SDM on the sparse outline landmarks of objects that do not have semantically meaningful interior textures.
 Using the resulting outline patch-based SDM, we report state-of-the-art performance on the task of human body parts localisation on challenging databases.
@@
 
-  \item We report state-of-the-art quantitative and qualitative results on the task of human body parts localisation by employing a patch-based SDM trained on the outline landmarks that are sampled by the dense correspondences.
+  \item We report state-of-the-art quantitative and qualitative results on human body parts localisation by employing a patch-based SDM trained on the outline landmarks that are sampled by the dense correspondences.
 Our proposed model outperforms all current state-of-the-art techniques that are trained on skeleton joints.

### 2016-04-09 contents/conclusion.tex
cam ready final draft

@@
-Learning and fitting statistical deformable models (SDM) is one of the most important areas in computer vision.
-Generally, in order to train a SDM a set of pre-defined correspondences are required.
-In some objects, such as human face, semantically meaningful correspondences can be found, but require laborious human manual annotations, on other objects it is very difficult, or even impossible, to find semantically meaningful correspondences.
-In this paper, we propose one the first comprehensive procedures for establishing correspondences (that do not necessarily correspond to semantically meaningfull object landmarks) in arbitrary objects with minimal ammount of human annotation.
-We apply the proposed approach for the construction of the first, to the best of our knowledge, highly descriptive SDM for the human arm.
+Learning and fitting statistical deformable models (SDMs) is one of the most important areas in computer vision.
+Generally, in order to train a SDM, a set of predefined correspondences are required.
+In some objects, such as human face, semantically meaningful correspondences can be found, but require laborious manual annotations; on other objects it is very difficult, or even impossible.
+In this paper, we propose one of the first comprehensive procedures for establishing correspondences (that do not necessarily correspond to semantically meaningful object landmarks) in arbitrary objects with minimal amount of human annotation.
+We apply the proposed approach for the construction of the first, to the best of our knowledge, highly-descriptive SDM for the human arm.

### 2016-04-09 contents/evaluation.tex
Updates from ShareLaTeX
cam ready final draft

--- 2015-11-09 contents/evaluation.tex
@@
 For further experimental results, please refer to the supplementary material.
+Note that all steps of the proposed pipeline were implemented using the Menpo Project~\cite{menpo14}.
 
@@
     \includegraphics[width=\columnwidth]{resources/Fig_Variance/final}
-    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
-    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
-    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
-    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
-    % \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
-    \caption{Example of human pose annotation for left arm among 4 annotators. The large variance shows the difficulties of having consistent landmarks. Figure best viewed by zooming in.}
+    \caption{Example of human pose annotation for left arm among 4 annotators. The large variance highlights the difficulty of obtaining consistent landmarks.}
     \label{fig:variance}
@@
     \includegraphics[height=\fh]{resources/Fixing/fix_18}
-    \caption{Demonstration of annotation correction using our method for experiment \ref{exp:qualitative}.
+    \caption{Demonstration of annotation correction using our method for the experiment of Section \ref{exp:qualitative}.
 \emph{Red} dots refer to officially provided landmarks, and \emph{green} dots are corrected position.}
@@
     \includegraphics[height=\ofh]{resources/Fittings/20.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/3.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/19.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/4.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/6.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/15.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/7.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/8.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/13.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/17.eps}
@@
     \includegraphics[height=\ofh]{resources/Fittings/21.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/23.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/25.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/27.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/29.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/31.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/33.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/35.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/36.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/37.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/38.eps}
+    \hfill
     \includegraphics[height=\ofh]{resources/Fittings/39.eps}
@@
     \label{fig:outline_fitting}
-    \vspace{-10pt}
+    \vspace{-5pt}
 \end{figure*}
 
-\subsection{Non-rigid Object Alignment In-the-wild}
+\subsection{Non-rigid Object Alignment In-the-Wild}
 \label{exp:daam_benchmark}
-Herein, we compare the fitting accuracy of the dAAMs that are trained with our proposed framework with holistic sparse AAMs~\cite{Cootes2001,Matthews2004}.
+Herein, we compare the fitting accuracy of the dAAMs that are trained with our proposed framework with holistic sparse AAMs~\cite{Cootes2001,Matthews2004,antonakos2015feature}.
 We consider two object classes that demonstrate rich texture: face and ear.
 
-\noindent\textbf{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}.
-Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}.
+\noindent\textbf{Databases \& Error Metrics} In the case of face, we trained both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW)~\cite{belhumeur2013localizing}.
+Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013,sagonas2016faces}.
 Our dAAMs were built as described in Step~\ref{sec:step4}.
-In both cases we build the appearance models using pixel intensities.
+In both cases, the appearance is represented using pixel intensities.
 The results are reported on the 224 images of the LFPW testset.
-The fitting error is evaluated as the point-to-point distance normalised by the face's size.
+The fitting error is evaluated as the point-to-point distance normalised by the face's size, as proposed in~\cite{Zhu2012}.
 
-In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions.
-The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper.
-Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}.
+In the case of human ear, given the lack of publicly available annotated databases, we collected 605 high resolution images captured under unconstrained conditions from online search engines.
+The images were manually annotated with respect to 55 sparse landmarks, as well as the curve annotations proposed in this paper.
+Examples of these two types of annotations are shown in Figure~\ref{fig:intro}.
 We randomly split the database into two disjoint sets of training (500) and testing (105) images.
-The training and evaluation of the two models is done in the same way as in the face's case.
+The training and evaluation of the two models is done in the same way as in the case of face.
 
 \begin{figure}[b!]
+    \vspace{-5pt}
     \centering
@@
     \includegraphics[width=0.48\columnwidth]{resources/DAAMBenchmark/ear}
-    \caption{CEDs of faces and ears fitting performance for experiment \ref{exp:daam_benchmark}}
+    \caption{CEDs of faces and ears fitting performance for the experiment of Section \ref{exp:daam_benchmark}.}
     \label{fig:daam_benchmark}
@@
 
-\noindent\textbf{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.
-By visually inspecting the results, we determined that the fitting is becomes inaccurate for errors greater than 0.1 and 0.06 for the ear and face, respectively.
-By inspecting the error curves, it can be observed that dAAMs marginally outperform sparse AAMs using pixels intensities as features.
-Therefore, the proposed pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass the commonly-used sparse AAMs.
+\noindent\textbf{Results} We report the results in Figure~\ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.
+By visual inspection of the results, we determined that the fitting is adequately accurate for errors less than 0.1 and 0.06 for the ear and face, respectively.
+The results indicate that dAAMs marginally outperform sparse AAMs.
+Therefore, the proposed pipeline is capable of dealing with the complex structure of non-rigid shapes and train dAAMs from simple curve line annotations which can compete and even outperform the commonly-used sparse AAMs trained on carefully annotated images.
 
@@
 \label{exp:benchmark}
-
-In this experiment, we aim to compare the performance of a deformable model for the outline of the arm that is built on our proposed outline sparse annotation scheme, against the standard skeleton joints scheme that is commonly employed in literature.
-For this purpose, we employ the patch-based AAM as described in Step~\ref{sec:step4} and train two different models, one that corresponds to the outline of the arm and one on the skeleton of the hand.
-Additionally, we compare are methodology with the current state-of-the-art techniques on human arm pose estimation in-the-wild.
+In this experiment, we aim to compare the effect of training a deformable model of human arm using: (i)~our proposed outline sparse landmarks, and (ii)~the standard skeleton joints annotations that are commonly employed in literature.
+For this purpose, we employ the patch-based AAM as described in Step~\ref{sec:step4}.
+Additionally, we compare our methodology with the current state-of-the-art.
 
 \begin{figure}[b!]
+    \vspace{-5pt}
     \centering
@@
     \includegraphics[width=0.48\columnwidth]{resources/HandBenchmark/elbow}
-    \caption{CEDs over skeleton landmarks on BBC Pose database for experiment \ref{exp:benchmark}}
+    \caption{CEDs over skeleton landmarks on BBC Pose database for the experiment of Section  \ref{exp:benchmark}.}
     \label{fig:hand_benchmark}
@@
 
-\noindent\textbf{Dataset \& Error Metric} We opted to report quantitative results on the BBC Pose\cite{pfister2015flowing} database, which contains the most consistent skeleton annotations among all the existing ones.
-The training of the outline patch-based AAM was performed after obtaining the outline annotations using our proposed framework.
-To train the part-based AAM (29 landmarks in the boundary) we used 891 training images from a combination of datasets, including H3D \cite{PoseletsICCV09}, Microsoft COCO \cite{lin2014microsoft}, MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human}, FLIC \cite{sapp2013modec} and BBC Poses \cite{pfister2015flowing}.
-SIFT \cite{PoseletsICCV09} feature is used from image representation for our model.
-Model fitting on BBC Pose is initialised based on an in house deep convolutional neural network.
+\noindent\textbf{Dataset \& Error Metric} We opted to report quantitative results on the BBC Pose database~\cite{pfister2015flowing}, which provides the most consistent and accurate joints annotations compared to the rest of existing databases.
+The training of the outline patch-based AAM was performed after obtaining 29 outline landmarks using our proposed framework.
+We used 891 training images from a combination of datasets, including H3D~\cite{PoseletsICCV09}, Microsoft COCO~\cite{lin2014microsoft}, MPII~\cite{andriluka14cvpr}, Fashion Pose~\cite{dantone2013human}, FLIC~\cite{sapp2013modec} and BBC Pose~\cite{pfister2015flowing}.
+SIFT features~\cite{PoseletsICCV09} are adopted for the image representation in our model.
+The fitting procedure on the BBC Pose database is initialised using a simplistic in-house deep convolutional neural network.
 
-In order to compare with current state-of-the-art human pose estimation on BBC Pose, we used the same error metric as BBC Pose, which normalises testing images to have height of 256 pixels.
-Performance measure of experiments in this paper are plot with Cumulative Error Distribution (CED) curve, where graph shows accuracy against distance from ground truth in pixels on normalised images.
-Results for this experiment are reported over 1000 testing images BBC Pose Provided, which human upper-body pose are landmark with 7 points on skeleton.
-For our model, joints are projected from the dense correspondence generated from our proposed method.
-Results (Figure \ref{fig:hand_benchmark}, our method is the outline PAAM) are reported comparing with the state-of-the-art which includes Buehler \cite{buehler2011upper}, Charles14 \cite{charles2014upper}, Charles13 \cite{charles2013domain}, Pfister14 \cite{pfister2015deep}, Ramanan \cite{yang2013articulated} and Pfister15 \cite{pfister2015flowing}.
-As can seen our outline part-based AAM model, even though not trained for locating the wrist and elbow, outperforms the state-of-the-art for this task.
-In particular, our method improves performance of current best method \cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
+In order to compare with current state-of-the-art on BBC Pose, we used the same error metric as the one in~\cite{pfister2015flowing}, which normalises testing images in order to have a height of 256 pixels.
+Once again, the performance is visualised using CED curves.
+The results for this experiment are reported on 1000 testing images from BBC Pose, which utilises 7 skeleton landmarks to annotate the human upper-body pose.
+Note that in the case of our model, the final joints locations required for evaluation are retrieved from the dense correspondence acquired with our proposed method.
+On the contrary, the rest of the methods are trained on this 7-points mark-up, thus directly return their estimated locations.
 
-In the same experiment we investigated the disadvantages of using skeleton annotation.
-We build patch-based AAM on the skeleton of the arm with same training data.
-As it can be seen from the  CED curves of \ref{fig:hand_benchmark} the skeleton based deformable model (called joint PAAM) has significant lower performance than the our outline model (Outline PAAM),
+\noindent\textbf{Results} Figure~\ref{fig:hand_benchmark} reports the results of our model trained on the outline landmarks (Outline PAAM), as well as the current state-of-the-art techniques which include: Buehler~\cite{buehler2011upper}, Charles14~\cite{charles2014upper}, Charles13~\cite{charles2013domain}, Pfister14~\cite{pfister2015deep}, Ramanan~\cite{yang2013articulated} and Pfister15~\cite{pfister2015flowing}.
+As can be seen, our outline part-based AAM model outperforms the state-of-the-art for this task, even though it is not trained directly on the wrist and elbow points, thus it is not tailored for locating them.
+In particular, our model outperforms the currently best method~\cite{pfister2015flowing} by a notable amount (9\% with error less than 6pt) on wrist, as well as marginal improvement on elbow estimation.
+Figure~\ref{fig:outline_fitting} shows some indicative qualitative fitting results.
+
+In the same experiment we prove that it is more advantageous to train a deformable model using the outline landmarks rather than the skeleton points.
+This is done by building a patch-based AAM on the same training data and with identical settings using both annotation schemes.
+As it can be seen from the  CED curves of Figure~\ref{fig:hand_benchmark}, our model trained on outline landmarks (Outline PAAM) notable outperforms the skeleton-based model for both wrist and elbow.
+We believe that this is a remarkable result, which indicates that out proposed outline mark-up can lead to a significant improvement of current state-of-the-art techniques.
 
@@
 \label{exp:qualitative}
+The final experiment demonstrates that it is feasible to use the proposed arm model in order to correct the annotations provided by current datasets.
+As mentioned above there are inconsistencies in the annotations of MPII~\cite{andriluka14cvpr}, Fashion Pose~\cite{dantone2013human} and FLIC~\cite{sapp2013modec}.
+Due to the large variance in arm pose, it is difficult even for trained annotators to obtain consistent annotations between them.
+As proof of concept, Figure~\ref{fig:variance} reports the standard deviation observed between the annotations of 4 trained humans that were requested to annotate 120 images of left arms from Fashion Pose~\cite{dantone2013human} with respect to the shoulder, elbow and wrist.
 
-The final experiment demonstrates that is feasible to use the proposed arm model in order to correct the annotations provided by the current datasets.
-As mentioned above there are inconsistencies in the joint annotations of MPII \cite{andriluka14cvpr}, Fashion Pose \cite{dantone2013human} and FLIC \cite{sapp2013modec}.
-Three well trained annotators are used to annotate left arm using 120 test images from Fashion Pose \cite{dantone2013human} dataset.
-Figure \ref{fig:variance} presents statistical results calculated using data annotated and officially provided with normalisation based on length of arms.
-Exemplar annotation visualisation also shows significant inconsistency of manual annotation on joints.
-
-Figure \ref{exp:qualitative} presents corrections of joint annotations using the proposed patch-based SDM.
-\emph{Red} dots shows ``ground truth" annotations while \emph{green} dots shows landmarks after correction using our methodology.
-There is no doubt that points after correction show more consistency among images.
-Images are cropped to hand only for better visualisation.
-Upon acceptance we will provide the corrected annotations in all the aforementioned databases.
+By applying our outline patch-based AAM on the aforementioned databases, we managed to greatly correct the currently available annotations of the arm.
+Figure~\ref{fig:qualitative} shows indicative examples of the corrected landmarks.
+There is no doubt that points after correction demonstrate more consistency among images.
+We make the corrected annotations publicly available\textsuperscript{\ref{foot:annotations}}.
 

### 2016-04-09 contents/implementation.tex
cam ready final draft

@@
 %
-%It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multi-channel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multi-image subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.
+%It combines the techniques of Non-rigid Iterative Closest Point (NICP) \cite{Amber2007}, multichannel Support Vector Shape (SVS) \cite{Nguyen2013} representation and multiimage subspace flow \cite{Garg:2013hu} in an effective framework that has significant descriptive power.
 %
@@
 \noindent\textbf{Step 2:} Construct a correspondence basis for the training SVS images.
-This is acquired by applying Non-rigid ICP on the densely sampled annotated curves, followed by Principal Component Analysis (PCA).
+This is acquired by applying the Non-rigid ICP (NICP) algorithm of \cite{Amber2007} on the densely sampled annotated curves, followed by Principal Component Analysis (PCA).
 
@@
 it can be applied to sparse landmark points, curves lines or a combination of the two, and~(b) it fuses inconsistent landmarks into consistent and directly comparable decision functions.
-Furthermore, this representations is also robust against noise, missing data and outliers \cite{Nguyen2013}.
+Furthermore, this representation is also robust against noise, missing data and outliers \cite{Nguyen2013}.
 
@@
 Even though not absolutely necessary in our framework, it can provide further guidance on the estimation of dense shape correspondences for various object classes.
-In more detail, we create a multi-channel SVS image $\bm{d}(\bm{x})=[d_1(\bm{x}) \cdots d_i(\bm{x}) \cdots d_{N_c}(\bm{x})]$, where $d_i(\bm{x})$ is the SVS image that corresponds to the curve annotation of the $i$-th structure and $N_c$ is the total number of structures (a single curve annotation is the special case where $N_c=1$).
+In more detail, we create a multichannel SVS image $\bm{d}(\bm{x})=[d_1(\bm{x}) \cdots d_i(\bm{x}) \cdots d_{N_c}(\bm{x})]$, where $d_i(\bm{x})$ is the SVS image that corresponds to the curve annotation of the $i$-th structure and $N_c$ is the total number of structures (a single curve annotation is the special case where $N_c=1$).
 Note that we do not necessarily require that all structures are annotated in all the object images: in the case that a structure is not annotated, the corresponding channel of the SVS image simply takes a zero value for all pixels.
-The shape flow estimation can deal with such missing information thanks to the spatial regularisation and the low-rank constraint that it adopts, c.f.~Step~\ref{sec:step3}.
+The shape flow estimation can deal with such missing information thanks to the spatial regularization and the low-rank constraint that it adopts, c.f.~Step~\ref{sec:step3}.
 
@@
 To form this vector, the training images are arranged in an arbitrary order.
-Similarly to the order of training samples when PCA is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
+Similarly to the order of the training samples when PCA is applied, this order does not affect the result of our method and any re-ordering would produce exactly the same results.
 
@@
     \bm{u}_n(\bx) \approx
-    \textstyle \, \sum_{i=1}^R \, \bm{q}_i(n)\bm{v}_i(\bx) \,\, ,
+    \textstyle \, \sum_{i=1}^R \, \bm{q}_i(n)v_i(\bx) \,\, ,
 \vspace{-5pt}
 \end{equation}
-where $\bm{v}_i(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$.
-In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $\bm{v}_i(\bm{x})$.
-The values of the $i$-th coefficient for all the points $\bm{v}_i(\bm{x})$ can be interpreted as an image defined on $\Omega$.
-Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $\bm{v}_i(\bm{x})$.
+where $v_i(\bx)$ is the weight that needs to be applied on the $i$-th correspondence basis element, in order to get the correspondence vector for the point location $\bm{x}$.
+In other words, the shape flow for every point $\bm{x}$ is described as a linear combination of basis elements that is controlled by the coefficients $v_i(\bm{x})$.
+The values of the $i$-th coefficient for all the points $v_i(\bm{x})$ can be interpreted as an image defined on $\Omega$.
+Using the correspondence basis, the determination of the shape flow boils down to the determination of the set of coefficients $v_i(\bm{x})$.
 The above representation of shape flow, constrains the correspondence vectors to lie on a subspace and, therefore, acts as a low-rank prior that enforces coherency of the shape registration result over the whole training dataset of shapes.
@@
 To effectively build the correspondence basis, we first transform the original annotations to sparse point clouds.
-Then, we apply Nonrigid Iterative Closest Point (NICP) \cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
+Then, we apply the NICP algorithm of \cite{Amber2007} between the point cloud of annotations in the reference shape and the one of every shape of the training set.
 NICP iteratively deforms the cloud of points of every shape to match the points of the reference shape.
@@
     \includegraphics[width=0.9\columnwidth]{resources/models}
-    \caption{Dense shape models build for faces and ears. Dense shapes are presented as grid for better visualisation.}
+    \caption{Dense shape models build for faces and ears. Dense shapes are presented as grid for better visualization.}
     \label{fig:dense_models}
@@
 \int_{\Omega}\sum_{n=1}^{N_t} \|\bm{d}(\bx+\bm{u}_n(x);n)-\bm{d}(x;0)\| \ud \bx \label{eq:costfunc}\\
-    &+ \beta \int_{\Omega}\sum_{n=1}^{N_t}\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)\bm{v}_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
+    &+ \beta \int_{\Omega}\sum_{n=1}^{N_t}\|\bm{u}_n(\bx)-\sum_{i=1}^R\bm{q}_i(n)v_i(\bx)\|^2 \ud \bx \label{eq:lowrank}\\
     &+
-\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla \bm{v}_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
+\int_\Omega  \sum_{i=1}^R \,\, \left \|    \nabla v_i(\bx)    \right \|  \,\ud \bx \label{eq:TVterm}
 \vspace{-5pt}
 \end{align}
-This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $\bm{v}_i(\bx)$ that are spatially regularised and enforce a low-rank prior.
-%We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $\bm{v}_i(\bx)$.
+This energy consists of two sets of unknown shape flows that are relatively close to each other: (i) $\bm{u}_n(x)$ which tries to explain the data from the input SVS images, and (ii) the shape flow determined by the correspondence basis coefficients $v_i(\bx)$ that are spatially regularised and enforce a low-rank prior.
+%We minimize this energy jointly with respect to $\bm{u}_n(\bx)$ and $v_i(\bx)$.
 %The positive parameters $\alpha$ and $\beta$ weigh the balance between the terms of the energy.
@@
 The \textbf{third term} of the energy \eqref{eq:TVterm} corresponds to the spatial Total Variation regularization \cite{rudin92} of
-the correspondence basis coefficients $\bm{v}_i(\bx)$.
+the correspondence basis coefficients $v_i(\bx)$.
 This term penalizes spatial oscillations of each coefficient caused by distortions of the SVS images but not strong discontinuities that are desirable in the borders of different object regions.
@@
 We approximate the data term \eqref{eq:costfunc} by linearizing the SVS images around the initialization.
-After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$\bm{v}_i(\bx)$ and $\bm{u}_n(\bx)$.
+After that, the energy becomes convex and we optimize it using alternating optimization w.r.t.~$v_i(\bx)$ and $\bm{u}_n(\bx)$.
 The minimization w.r.t.~
-%$\bm{v}_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
+%$v_i(\bx)$ is decoupled for every coefficient $i$ and corresponds to Rudin-Osher-Fatemi Total Variation denoising \cite{rudin92}, which we solve efficiently by applying the first order primal-dual algorithm of \cite{Chambolle:Pock:JMIV2011}.
 The minimization w.r.t.~
@@
 
-Given a test image $\mathbf{I}$, the fitting process involves the minimisation of the following cost function:
+Given a test image $\mathbf{I}$, the fitting process involves the minimization of the following cost function:
 \begin{equation}
@@
 \end{equation}
-This optimisation problem is typically solved using the inverse-compositional Gauss-Newton algorithm, for which different variations have been proposed \cite{Matthews2004, Papandreou2008, Amberg2009, Tzimiropoulos2013, Alabort2014}.
+This optimization problem is typically solved using the inverse-compositional Gauss-Newton algorithm, for which different variations have been proposed \cite{Matthews2004, Papandreou2008, Amberg2009, Tzimiropoulos2013, Alabort2014}.
 Note that the existence of the sampling function $\mathcal{W}()$ instead of a non-linear warping function has the advantage that all existing efficient gradient descent algorithms become exact.
 
-\paragraph{Outline Patch-Based Active Appearance Model} The object classes for which the interior appearance does not have specific structure are modeled using patch-based AAMs \cite{Tzimiropoulos2014} trained on a set of sparse landmarks.
+\paragraph{Outline Patch-Based Active Appearance Model (PAAM)} The object classes for which the interior appearance does not have specific structure are modeled using patch-based AAMs \cite{Tzimiropoulos2014} trained on a set of sparse landmarks.
 Especially for human body parts (arms, legs), we strongly believe that the points located to the outline of the object are more suitable compared to the internal ones that correspond to the skeleton joints, which are commonly used by current literature \cite{buehler2011upper,charles2013domain,pfister2015flowing,yang2013articulated}.
@@
 These patches are then vectorised and concatenated in a single texture vector.
-Note that the optimisation process remains exactly the same.
+Note that the optimization process remains exactly the same.

### 2016-04-09 contents/introduction.tex
cam ready final draft

@@
 
-\item Annotating with regards to consistent landmarks is an extremely time consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person.
+\item Annotating with regards to consistent landmarks is an extremely time-consuming, tedious and labour intensive work \cite{sagonas_iccv_300w_2013}, which is usually performed by a trained person.
 Furthermore, for various object classes, it requires a highly skilled person in order to identify and annotate landmarks in a consistent manner.
@@
 \item The nature of many deformable objects does not allow them to be annotated with regards to a consistent set of landmarks (e.g., bottles, fruits etc.).
-Additionally, it is very difficult to consistently annotate the boundary/outline of certain objects such as faces, ears, body, since these landmarks do not have any semantic meaning.
+Additionally, it is very difficult to consistently annotate the outline of certain objects such as faces, ears, body, since these landmarks do not have any semantic meaning.
 That is why many state-of-the-art methods opt to leave the boundary out when reporting results \cite{Tzimiropoulos2014, Asthana2014}.
@@
 
-To illustrate how time consuming careful annotation of a complex deformable object is, we lay down our own experience based on the human ear.
+To illustrate how time-consuming careful annotation of a complex deformable object is, we lay down our own experience based on the human ear.
 A trained annotator needs an average of 4 minutes per image for the manual annotation of 55 landmarks.
@@
 Due to the fact that manual annotation is a costly and labour-intensive procedure, unsupervised learning of deformable models for the task of object alignment has recently attracted some attention \cite{frey2003learning, baker2004automatic, cootes2004groupwise, jojic2006escaping, Huang2006, kokkinos2007unsupervised, jiang2009learning, liu2009simultaneous, Zhang2012}.
-However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed, the limited number of methods that have been proposed for the task cannot be directly applied to arbitrary collection of ``in-the-wild" images.
+However, because the problem of fully unsupervised discovery of the deformations of arbitrary objects is difficult and ill-posed, the limited number of methods that have been proposed for the task cannot be directly applied to arbitrary collections of ``in-the-wild" images.
 On the other hand, the method of \cite{antonakos2014automatic}, which can deal with ``in-the-wild" images, requires a set of consistently annotated sparse shapes to perform deformable face congealing.
@@
 However, these assumptions do not hold in our case, where we have a collection of shapes.
-Therefore, we introduce appropriate modifications based on the consistency of image-based shape representation, as well as low rank priors.
+Therefore, we introduce appropriate modifications based on the consistency of image-based shape representation, as well as low-rank priors.
 
@@
 
-  \item We show that the employed patch-based SDM corrects the annotations that are currently provided for most major human body pose databases.
-Upon acceptance of the paper, we will make the corrected annotations publicly available.
+  \item We show that the employed patch-based SDM corrects the annotations that are currently provided for most major human body pose databases \footnote{\label{foot:annotations}The corrected annotations are publicly available in \url{http://www.ibug.doc.ic.ac.uk/resources/bodypose-anno-correction}.}.
 

### 2016-04-10 supplementary.tex
repo cleanup
supplementary minor fix

@@
 
-% \iccvfinalcopy % *** Uncomment this line for the final submission
+\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
-%experimental evaluations for constructing both Dense AAMs and Patch-based AAMs using the proposed pipeline.
-%For \textbf{Dense AAM}, We present more detailed algorithms explanation and intrinsic property analysis of Dense AAMs.
-In section~\ref{sec:cost_function},  minimisation of the energy function are described in more details.
-In Section \ref{sec:daam_fittingresults}, we present visualisations of in-the-wild model fitting  for faces and ears, comparing classic AAMs and the proposed dense AAMs.
-In Section \ref{sec:modelanalysis}, we provide evaluations and comparisons of dAAMs, in terms of model compactness, warping quality and reconstruction accuracy.
-%For \textbf{Patch-based AAM}, we described how sparse landmark points are sparsely sampled from dense reference shape and mapped to rest shapes according to dense correspondences in section~\ref{sec:sparsesample}.
-A visualisation for Patch-based AAM shape model is presented in section~\ref{sec:paam_sm}.
-Also more visualisation of fitting results are shown in section~\ref{sec:paam_fittingresults}.
-
 \appendix
@@
 
-As mentioned in the main submission (Section 3, Step 3), we propose to estimate the shape flow by minimising the following energy:
+As mentioned in the main paper (Section 3, Step 3), we propose to estimate the shape flow by minimising the following energy:
 \vspace{-5pt}
@@
 We implement this minimisation based on the optimisation algorithm described in \cite{Garg:2013hu} and the relevant publicly available code \footnote{https://bitbucket.org/troussos/mfsf/downloads}.
-However, we modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Section 3, Step 2 of the main submission.
+However, we modify this algorithm so that, instead of initialising the coarse-to-fine and warping iterations with a zero flow, we use Thin Plate Splines (TPS) \cite{Bookstein1989} interpolation of the initial correspondence vectors described in Section 3, Step 2 of the main paper.
 This yields a significantly better initial location of the highly-nonconvex objective function and improves the computational efficiency, since much less coarse-to-fine pyramids are needed.
@@
 
-Figure~\ref{fig:compact} pliots the variance ration of the face dAAM, which provides an indication of the compactness of the model.
+Figure~\ref{fig:compact} plots the variance ration of the face dAAM, which provides an indication of the compactness of the model.
 The compactness is compared with the one of a standard sparse AAM built on the same data.
@@
     \includegraphics[width=\columnwidth]{Suplementory_Meterial/Model_Analysis/cumu_var_ratio}
-    \caption{Compactness plots of dAAM (green) and sparse AAM (blue) models for faces.
+    \caption{Compactness plots of dAAM (blue) and sparse AAM (red) models for faces.
 Portion of the corresponding total variance explained as a function of the number of retained principal components.}
@@
     \includegraphics[height=\ofh]{Suplementory_Meterial/ExFit/0044.eps}
-    \caption{Demonstration of outline fitting of patch-based AAM on arms. Images are cropped to arms only for better visualisation.}
+    \caption{Demonstration of outline fitting of patch-based AAM on arms. Images are cropped to arms only for better visualization.}
     \label{fig:paam_fittingresults}
@@
 
-In this section, we visualise some characteristic examples of fitting
+In this section, we visualize some characteristic examples of fitting
 dAAMs that were built using the proposed framework.
@@
 
-Figure~\ref{fig:paam_sm} shows the mean shape and the first 4 principal shape components of our PAAM for arms\footnote{Note that we do not visualise the appearance variation, since this is built using SIFT features and the corresponding 36-channel feature space cannot be visualised in an intuitive way.}.
+Figure~\ref{fig:paam_sm} shows the mean shape and the first four principal shape components of our PAAM for arms\footnote{Note that we do not visualise the appearance variation, since this is built using SIFT features and the corresponding 36-channel feature space cannot be visualized in an intuitive way.}.
 We observe that the shape variations captured by the model are plausible and seem to produce valid shapes of human arms.
@@
 \end{document}
-
-% \subsection{Appearance Reconstruction}
-% \label{sec:reconstruct}
-
-% \begin{figure}[!b]
-%     \centering
-%     %\vspace*{-0.2in}
-%     \includegraphics[width=0.5\textwidth]{Suplementory_Meterial/Fig_Draw/draw}
-%     \caption{Synthesizing face images from caricature sketches.
-First column: caricature sketches.
-Second column: arbitrary chosen face images.
-Third and last column: sketch-based warping of images based on AAMs (third column) and dAAMs (last column).}
-%     \label{fig:draw}
-% \end{figure}
-
-% In this qualitative experiment, we show how the proposed pipeline can be used to generate novel modified instances of an object, e.g.
-caricatures.
-To be specific, firstly we manually craft a set of hand-drawn cartoon-like shape sketches.
-We then apply shape flow to align them with the reference frame.
-In this way, we establish dense correspondences of landmarks.
-Afterwards, we perform shape reconstruction using both AAMs and dAAMs.
-Finally, we warp the appearance from arbitrarily chosen faces on the reconstructed shape using either piecewise affine warp (in the case of AAMs) or shape flow (in the case of dAAMs).
-The corresponding results are shown in figure \ref{fig:draw}.
-We see that AAMs introduce more severe artifacts, especially on the areas of mouth and eyes, where nuanced information is missing or models are overly deformed.
-In contrast, dAAMs yield a significantly more plausible result.
-
-% \section{Segmentation using Dense AAM}
-% \label{sec:segmentation}
-
-% In this section, we present experiments of utilising our dense AAM for object segmentation.
-Two object classes, bottles and human bodies, are considered.
-For human bodies, we use images along with ground truth segmentation from Space-Time Actions dataset \footnote{\label{sta} \url{http://www.wisdom.weizmann.ac.il/~vision/SpaceTimeActions.html}}, which includes sequences with several human actions.
-We use ``jumping'' and ``sliding'' actions.
-As far as bottles are concerned, we use 500 high-resolution images that we collected and annotated using a newly-defined 50 point annotation scheme, as well as the curve annotations proposed in this paper.
-We randomly split these images into two disjoint sets of training (400) and testing (100) images.
-Bottle models were built using 400 training images while body models are built in terms of human actions (e.g.
-jumping), each having approximately 200 training images and 50 test images.
-
-% \begin{figure}[!t]
-%     \centering
-%     \begin{subfigure}[b]{0.15\textwidth}
-%             \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/ear}
-%         %\caption{Ear Initial Bounding Box}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.15\textwidth}
-%             \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/bottle}
-%         %\caption{Bottle Initial Bounding Box}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.15\textwidth}
-%             \includegraphics[height=\textwidth]{Suplementory_Meterial/Segmentation_Measure/body}
-%         %\caption{Body Initial Bounding Box}
-%     \end{subfigure}
-%     \caption{Examples of fitting initialisations used for the segmentation experiment. These are created by random perturbation of the ground-truth bounding box.}
-%     \label{fig:seg_init}
-% \end{figure}
-
-% Fitting dAAMs on test images yields dense landmarks that can be used to perform segmentation.
-In a real-world scenario, a simple object detector would be required to be applied prior to our pipeline to initialise the fitting.
-However, as a simple evaluation, we initialise the fitting by randomly perturbing the ground-truth bounding box with certain variance to simulate an object detector with implicit detection, see e.g.~Figure \ref{fig:seg_init}.
-Table  \ref{tab:seg_result} reports the segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline.
-
-% \begin{table}[!h]
-% \small
-% \centering
-% \begin{tabular}{|l|c|c|c|}
-% \hline
-% \emph{Object}   & \emph{mean} & \emph{std} & \emph{median}\\
-% \hline\hline
-% Bottles         & 0.8125      & 0.1460     & 0.8414\\
-% Action - Jump   & 0.6102      & 0.0198     & 0.6099\\
-% Action - Slide  & 0.6444      & 0.0500     & 0.6501\\
-% \hline
-% \end{tabular}
-% \caption{Segmentation precision, in case of fitting bottles and human bodies by adopting the proposed dAAMs pipeline. The mean, standard deviation and median of the precision error are provided.}
-% \label{tab:seg_result}
-% \end{table}
